### 2017-02-07 writing/paper-Tian-gr-wetting.tex
First draft; added data

% Created 2017-01-17 Tue 11:30
% Intended LaTeX compiler: pdflatex
\documentclass[aps,prl,reprint,groupedaddress,amsmath,amssymb, showpacs]{revtex4-1}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{fontspec}
\date{}
\title{}
\begin{document}

\title{A Multiscale View of the Doping-Induced Tunable Wettability on Two-Dimensional Materials}
\author{Tian Tian} 
  \affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Elton J. G. Santos}
  \affiliation{School of Mathematics and Physics, Queen's University Belfast, United Kingdom}
  \affiliation{School of Chemistry and Chemical Engineering, Queen's University Belfast, United Kingdom}
\author{Shangchao Lin}
  \email{slin@eng.fsu.edu.}
  \affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Chih-Jen Shih}
  \email{chih-jen.shih@chem.ethz.ch}
  \affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}

\date{\today}

\begin{abstract}
  The emergence of 2D-material-based liquid-phase devices calls for
  the need for understanding the wetting property at the
  2D-material-liquid interface, and particularly the doping-induced
  tuning of wetting properties. In this letter, we propose a
  multiscale view of the doping-induced tunable wettability of 2D
  materials, by combining the reorientation effect of water molecules
  estimated by MD simulation, and the electrowetting effect calculated
  by continuum model. We reveal the electrostatic nature of the
  doping-induced wettability under both scale. We further evaluate the
  recent finding of doping-induced wettability tuning of graphene with
  the proposed model, by considering incomplete surface coverage of 2D
  materials. We find that minor surface incompleteness can cause great
  discrepancy in the measured value of interfacial wettability, requiring
  extreme care for interpreting the experimental results. In
  addition, we prove that a 2D material with higher density of states
  can essentially reduce the gating voltage in a 2D-material-based
  electrowetting device, and rank the tunability of the 2D materials
  as: MoTe$_{2}$ > MoS$_{2}$ > WTe$_{2}$ > WS$_{2}$ > germanene > silicene >
  graphene. Our multiscale analysis provides a comprehensive view of
  the wettability of 2D material interface, and we believe operational
  2D-material-based liquid manipulating devices will be facilitate by
  the principles presented in this letter.
\end{abstract}
\maketitle

The emergence of two-dimensional (2D) materials has attracted broad
interest in various research fields, inspired by their unique physical
and chemical properties. Recent progress of scalable 2D material
synthesis paves the way for their liquid phase 2D-material-based
applications, for instance functional coating
\cite{Prasai_2012,Rafiee_2010,Kim_2014}, nanotribology devices
\cite{Yin_2014,Tang_2016,Feng_2016}, nanoporous desalination apparatus
\cite{Surwade_2015,Rollings_2016,Jain_2015}, droplet manipulation
\cite{Hern_ndez_2013,Vijayarangamuthu_2015}, etc.  To fully exploit the
physics of the interface between 2D materials and liquid phase, a
comprehensive understanding of the 2D-material-liquid interaction, and in
particular, the wettability, is of great importance.

Wetting on atomically-thin 2D materials has long been a hot but highly
disputed topic
\cite{taherian2013what,Kozbial_2015,Parobek_2015,Govind_Rajan_2016}.
Accurate description of the intrinsic wettability of 2D materials is
known to be challenging. Recent studies show that the wettability on
graphene \cite{li_effect_2013,Xu_2013_withwhat,kozbial_study_2014} and
MoS\(_{\text{2}}\) \cite{Kozbial_2015,Chow_2015} is strongly affected by airborne
contaminants. Meanwhile, the contact angle measurement technique which
has been widely to determine the wettability on 2D materials, may also
suffer inaccuracy from contact angle hysteresis caused by local
defects \cite{raj_wettability_2013}.  On the other hand, unlike bulk
materials, the thickness of a 2D material falls within the effective
range of dispersion interactions.  As a result, the dispersion
interaction between the substrate underneath the 2D material and
liquid molecules is not fully screened by the 2D material, giving rise
to the fascinating property known as the ``wetting-translucency''
\cite{rafiee_wetting_2012,shih_breakdown_2012,shih_wetting_2013}.
Moreover, 2D semimetals (graphene, silecene, germanene, etc.) and 2D
semiconductors (e.g, transition metal dichalcogenides (TMDCs)) possess
significantly lower density of states (DOS) than bulk materials,
making them easier to be doped by the underlying substrates
\cite{Chen_2013,Varchon_2007,Giovannetti_2008} or electrostatic gating
\cite{Das_2008,Perera_2013}. Due to the ubiquity of doping in 2D
materials, it is worth investigating the relationship between the
doping level and wettability. Several recent reports have addressed
the issue of doping-induced tunability of graphene's wettability, from
both atomistic simulations
\cite{ostrowski_tunable_2014,ren_interfacial_2015,Taherian_2015,daub_electrowetting_2007}
and experimental demonstrations
\cite{hong_mechanism_2016,goniszewski_correlation_2016,ashraf_doping-induced_2016}.
However, discrepancies exist between individual reports, concerning
the origin and magnitude of the doping-induced wetting
tunability. Moreover, to get a full perspective of such phenomenon,
the gap between the nanoscale simulations and macroscopic experimental
results needs to be filled, and the aforementioned issues of intrinsic
wettability and wetting translucency should also be taken into account.

In this letter, we propose a multiscale approach to properly model the
doping-induced tuning of 2D materials' wettability. We model the
change of surface adhesion energy between water and 2D material as a
combined effect of (i) reorientation of water molecules, characterized
by molecular dynamic (MD) simulations and (ii) electrowetting due to
formation of electric double layer, calculated by a continuum model
based on modified Young-Lippman theory. By using graphene as an
example, we demonstrate that, the electrostatic interaction plays a
major role in both the reorientation and electrowetting effects. By
further considering the surface coverage of 2D materials, we evaluate
the previous reported result on the doping-induced wetting behavior of
graphene using the proposed multiscale model. We find that the
existence of minor defects can cause great discrepancy between the
observed wetting property and theoretical values, requesting attentive
interpretation of the experimental results. Moreover, we quantify the
tunability of interfacial tension in a gate-controlled
2D-material-based electrowetting device as a function of the DOS of
the 2D material, and rank several 2D materials according to their
tunability. We show that 2D materials with higher DOS such as
transition metal dichalcogenides (TMDCs), perform better than graphene
by means of wettability regulation. Our findings provide a
comprehensional view of the wettability of 2D materials, as well as
guidance for operational liquid-phase 2D material-based devices.

Due to the complex dynamic nature of wetting
\cite{Cassie_1944,Wenzel_1936,Gao_2007,Marmur_2009}, we only study the
static wettability of 2D materials. We only consider water as the
liquid phase, as most liquid-phase applications of 2D materials are
also in aqueous environment. The macroscopic feature of
wetting--contact angle \(\theta\), is connected to the interfacial
adhesion energy \(\Phi_{\mathrm{2D-w}}\) by the Young's equation:
\begin{equation}
\label{eqn:young's equation}
\Phi_{\mathrm{2D-w}} = -\gamma_{\mathrm{L}}(1+\cos\theta)
\end{equation}
where \(\Phi_{\mathrm{2D-w}}\) is defined as:
\begin{equation}
\label{eqn:def-adhesion}
\Phi_{\mathrm{2D-w}} = \gamma_{\mathrm{2D-w}} - \gamma_{\mathrm{2D}} - \gamma_{\mathrm{w}}
\end{equation}

where \(\gamma_{\mathrm{2D-w}}\) is the surface tension between the
interface of the 2D material and the aqueous phase,
\(\gamma_{\mathrm{2D}}\) and \(\gamma_{\mathrm{w}}\) are the surface
tensions of the 2D material and water in vacuum,
respectively. \(\Phi_{\mathrm{2D-w}}\) is contributed by both the
short-range dispersion interaction and long-range electrostatic
interaction between the 2D material and water. The existence of
additional charges in 2D materials gives rise to the reorientation of
adjacent water molecules \cite{ostrowski_tunable_2014}. On the other
hand, the formation of electric double layer (EDL) in an ionic
solution near the interface also alters the interfacial adhesion
properties, known as the electrowetting effect \cite{Lippmann_1908},
which has been widely used in microfluidic applications
\cite{Mugele_2005}.  Owing to the additive nature of dispersion and
electrostatic interactions, we propose that the change of interfacial
adhesion energy \(\Delta \Phi_{\mathrm{2D-w}}\) is a combined effect of
the reorientation effect \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{or}}\) and EDL
formation \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}\):
\begin{equation}
\label{eqn:contrib-adhesion-change}
\Delta \Phi_{\mathrm{2D-w}} = \Delta \Phi_{\mathrm{2D-w}}^{\mathrm{or}}
                              + \Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}
\end{equation}

A multiscale approach is needed to combine both effects as their
effective length scales are different. We use molecular dynamics (MD)
simulations for sampling the orientation effect adjacent to the 2D
material; in addition a continuum model is implemented to describe the
contribution of EDL formation, since state-of-art MD simulations fail to
handle diluted ionic solution systems where the Debye length can be as
long as 10\(^{\text{3}}\) nm. Our multiscale modeling approach is schematically illustrated in Fig. \ref{fig:scheme-method}.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.95\linewidth]{../img/scheme-methods.pdf}
\caption{\label{fig:scheme-method}
Scheme of the multiscale approach for modeling the doping-induced wettability tuning of 2D materials.}
\end{figure}

It is also noteworthy that our multiscale approach is compatible with
the issues of the intrinsic wettability and wetting translucency of 2D
materials. Since we are dealing with the change of interfacial
adhesion energy as a function of surface charge, the absolute value of
\(\Phi_{\mathrm{2D-w}}\) or \(\gamma_{\mathrm{2D-w}}\) (extracted from intrinsic wetting property and wetting translucency theory) can be treated as
independent variables.

We model the charged 2D materials as rigid sheets with uniform surface
charge density \(\sigma_{\mathrm{2D}}\), either by substrate or
electrostatic doping. We also assume that the 2D material has no
dissociable groups which can change the aqueous pH value
\cite{zuccaro_tuning_2015} and the 2D material is inert to
electrochemical reaction at the interface
\cite{bard_electrochemical_1980}.  First we use graphene as a model
system to show the effect of reorientation of water molecules on the
interfacial adhesion energy. Different from previous approaches which
used MD simulations to extract the contact angle of nanodroplets on
graphene
\cite{ostrowski_tunable_2014,daub_electrowetting_2007,ren_interfacial_2015,Taherian_2015},
where the interfacial adhesion energy cannot be accurately measured
due to changed contact area between water and graphene, here we
propose to use a continuous water monolith in the MD simulation with periodic boundary conditions in the x and y directions to
calculate the interfacial adhesion energy \(\Phi_{\mathrm{2D-w}}\).
\begin{center}
\fbox{
\begin{minipage}[c]{.8\linewidth}
\textbf{\textsf{\textsc{TODO}}} Description for MD simulation

\end{minipage}
}
\end{center}

The adhesion energy \(\Phi_{\mathrm{2D-w}}^{or}\) in the MD simulation is
defined as:
\begin{equation}
\label{eqn:Delta-Phi-or-definition}
\begin{aligned}
\Phi_{\mathrm{2D-w}}^{or} &= (\Psi_{\mathrm{2D-w}} - \Psi_{\mathrm{w}} - \Psi_{\mathrm{2D}})\frac{1}{S \cdot N_{\mathrm{A}}} \\
                     &= \Phi_{\mathrm{LJ}} + \Phi_{\mathrm{CL}}
\end{aligned}
\end{equation}
where \(S\) is the area of the graphene sheet (same as the contact area
 between water and graphene), \(N_{\mathrm{A}}\) is the Avogadro's
 number, \(\Psi_{\mathrm{2D-w}}\) is the total internal potential of the
 2D material-water system, and \(\Psi_{\mathrm{w}}\) and
 \(\Psi_{\mathrm{2D}}\) are the potentials of the separated water phase
 and 2D materials, respectively.  The adhesion energy can be further
 decomposed into the short-range Lenard-Jones potential term
 (\(\Phi_{\mathrm{LJ}}\)) and the long-range Coulombic interaction term
 (\(\Phi_{\mathrm{CL}}\)). Since \(\Psi_{\mathrm{w}}\) and
 \(\Psi_{\mathrm{2D}}\) are unalterable in the MD simulation, the change
 of interfacial adhesion energy \(\Delta \Phi_{\mathrm{2D-w}}^{or}\) as a
 result of surface doping, is calculated as:
\begin{equation}
\label{eqn:delta-Phi-2D-or}
\begin{aligned}
\Delta \Phi_{\mathrm{2D}}^{or} &= \frac{\Delta \Phi_{\mathrm{2D-w}}}{S \cdot N_{\mathrm{A}}} \\
                               &= \Delta \Phi_{\mathrm{LJ}} + \Delta \Phi_{\mathrm{CL}}
\end{aligned}
\end{equation}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.9\linewidth]{../img/fig-pot-dens.pdf}
\caption{\label{fig:pot-dens}
(a) Change of total adhesion energy \(\Delta\Phi_{\mathrm{2D}}^{or}\), contribution of Lenard-Jones interaction \(\Delta\Phi_{\mathrm{LJ}}\) and Coulombic interaction \(\Delta\Phi_{\mathrm{CL}}\), as a function of charge density on graphene. (b) Local density of water molecule (\(\rho_{\mathrm{w}}\))  as a function of distance \(z\) from graphene surface.}
\end{figure}

The changes of adhesion energy terms \(\Delta
\Phi_{\mathrm{2D-w}}^{or}\), \(\Delta \Phi_{\mathrm{LJ}}\) and \(\Delta
\Phi_{\mathrm{CL}}\), as functions of \(\sigma_{\mathrm{2D}}\) , are
shown in Fig. \ref{fig:pot-dens}(a). It can be seen that the
contribution from dispersion interaction \(\Delta \Phi_{\mathrm{LJ}}\)
has a very small magnitude of negative change (less than 2.5 mJ\(\cdot
\mathrm{m}^{-2}\)) when \(\sigma_{\mathrm{2D}}\) ranges from
-5\(\times10^{13}\) \textasciitilde{} 5\(\times10^{13}\) \(e\cdot \mathrm{cm}^{-2}\). On the
other hand, we find that \(\Delta \Phi_{\mathrm{CL}}\) contributes
majorly to \(\Delta \Phi_{\mathrm{2D-w}}^{or}\), indicating the
electrostatic nature of the doping-induced reorientation of water
molecules.
\begin{center}
\fbox{
\begin{minipage}[c]{.8\linewidth}
\textbf{\textsf{\textsc{TODO}}} Validate the statement above

\end{minipage}
}
\end{center}
It is also interesting to find that, unlike its counterpart from
dispersion interaction, \(\Delta \Phi_{\mathrm{CL}}\) has a asymmetric
response to \(\sigma_{\mathrm{2D}}\). We further plot the local density
of water molecules \(\rho_{\mathrm{w}}\), as a function of distance \(z\)
from the graphene plane, which can be seen in Fig. \ref{fig:pot-dens}(b). We consider
3 cases where the graphene layer is either charge-neutral, or
\(\sigma_{\mathrm{2D}}=\pm 0.012\ e/ \mathrm{atom}\), respectively. We
find that the \(\rho_{\mathrm{w}}\) at the first water layer adjacent to
graphene (\(z \approx 3.2\ \mathrm{\AA}\)) also responsed asymmetrically with
\(\sigma_{\mathrm{2D}}\).  When \(\sigma_{\mathrm{2D}}=-0.012\ e/
\mathrm{atom}\), \(\rho_{\mathrm{w}}\) drops to ca. 80\% of that in the
electroneutral system, while \(\rho_{\mathrm{w}}\) at
\(\sigma_{\mathrm{2D}}=0.012\ e/ \mathrm{atom}\) has a 8\% increase in the density compared with the electroneutral system. The change of interfacial water
density can be ascribed by the polarity of water molecules. When the
graphene layer is positively charged, the O atom is more favorably
facing the graphene surface, while H atom is more favorably facing the
negatively-charged surface.
\begin{center}
\fbox{
\begin{minipage}[c]{.8\linewidth}
\textbf{\textsf{\textsc{TODO}}} Describe the density change

\end{minipage}
}
\end{center}
\begin{center}
\fbox{
\begin{minipage}[c]{.8\linewidth}
\textbf{\textsf{\textsc{TODO}}} More in-depth discussion?

\end{minipage}
}
\end{center}

It is noteworthy that although the process for investigating the
magnitude of \(\Delta \Phi_{\mathrm{2D-w}}^{or}\) is similar for other 2D
materials other than graphene, the result obtained here cannot be
readily applied to other 2D materials, since the contribution of
dispersion interaction and electrostatic interaction can be completely
different \cite{Govind_Rajan_2016,Chow_2015}. Nevertheless, in
real-world measurements, due to the existence of the contamination
layer which has a typical thickness ca. 1\textasciitilde{}2 nm, the dispersion
interactions contributed by surface charge can be nearly completely
screened out; aqueous electrolytes can also greatly attenuate the
electric displacement field, compared with the dipole water model used
in the MD simulations. Therefore we propose that the effect of
reorientation may not be easily observable in current experimental
setups.

While the interfacial dispersion interaction vanishes several
molecules away from the surface, the long range electrostatic
interaction will cause the aqueous ions to rearrange at a much longer
length scale, forming an EDL at the interface and decrease the
interfacial surface tension by the phenomenon known as
electrowetting. To model the effect of electrowetting, we first
consider that a contamination layer with thickness \(d_{\mathrm{c}}\)
covers the 2D material surface. Since the airborne contaminants are
mostly hydrocarbon compounds, they can be treated as a dielectric
layer with permittivity \(\epsilon_{\mathrm{c}}\). We use the
Gouy-Chapman-Stern model to describe the EDL in the aqueous phase,
which consists a Helmholtz double layer with the same permittivity
\(\epsilon_{\mathrm{w}}\) as water, and thickness \(d_{\mathrm{H}}\),
together with a diffuse layer where ionic distribution is described by
the Gouy-Chapman equation.  The potentials at the surface of the 2D
material, the contamination layer surface and the outer Helmholtz
plane (the interface between the Helmholtz double layer and the
diffuse layer) are \(\psi_{\mathrm{2D}}^{*}\), \(\psi_{\mathrm{2D}}\) and
\(\psi_{\mathrm{L}}\), respectively. An illustration of the model for the
2D-material-water interface is shown in Fig. \ref{fig:scheme-EDL}.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.95\linewidth]{../img/scheme-EDL.pdf}
\caption{\label{fig:scheme-EDL}
Scheme of the interface between the 2D material and the aqueous phase. A electrostatic potential \(\psi_{\mathrm{2D}}\) is built at the interface, as a result of surface charge on 2D material \(\sigma_{\mathrm{2D}}\).}
\end{figure}

If we neglect specific adsorption of ions at the solid-liquid interface,
electroneutrality ensures that the charge density of the 2D material
\(\sigma_{\mathrm{2D}}\) balances the total charge density of the EDL
\(\sigma_{\mathrm{L}}\) \cite{bard_electrochemical_1980}:
\begin{equation}
\sigma_{\mathrm{2D}} + \sigma_{\mathrm{L}} = 0
\end{equation}
From the Gouy-Chapman model of symmetric electrolytes we know:
\begin{align}
\displaystyle
\label{eqn:psi-L}
\psi_{\mathrm{L}} &= -\frac{2k_{\mathrm{B}}T}{z_{0}e} 
                       \sinh^{-1}\left(
                         \frac{\sigma_{\mathrm{L}}}{\sqrt{8c_{0}N_{\mathrm{A}}\epsilon_{\mathrm{w}}k_{\mathrm{B}}T}}
                          \right) \\
\label{eqn:psi-2D}
\psi_{\mathrm{2D}} &= \psi_{\mathrm{L}} - \sigma_{\mathrm{L}}\frac{d_{\mathrm{H}}}{\epsilon_{\mathrm{w}}} \\
\psi_{\mathrm{2D}}^{*} &= \psi_{\mathrm{2D}} - \sigma_{\mathrm{L}}\frac{d_{\mathrm{c}}}{\epsilon_{\mathrm{c}}}
\end{align} 
where \(z_{0}\) is the valency of the electrolyte, \(c_{0}\) is the
concentration of the electrolyte, \(N_{\mathrm{A}}\) is the Avogadro
constant and \(k_{\mathrm{B}}\) is the Boltzmann constant. While the
contamination layer is responsible for a potential drop across the
solid phase, the solid-liquid interfacial potential
\(\psi_{\mathrm{2D}}\) which contributes to the \(\Delta \Phi_{\mathrm{2D-w}}^{el}\), is only governed by \(\sigma_{\mathrm{L}}\). Therefore
we conclude that the existence of a contamination layer does not affect
the magnitude of \(\Delta \Phi_{\mathrm{2D-w}}}^{el}\).

The change of interfacial adhesion energy is calculated using the
Gibbs adsorption isotherm equation:
\(\mathrm{d}\Phi_{\mathrm{2D-w}}^{el} = \mathrm{d}
\gamma_{\mathrm{2D-w}}^{el} = -z_{0}e\Gamma
\mathrm{d}\psi_{\mathrm{2D}}\), where \(\Gamma\) is the interfacial
adsorption number at the solid-liquid interface. Since the Debye
length is much smaller than the diameter of a macroscopic droplet,
\(\Gamma\) can be approximated by the total excessive charge density
\(\sigma_{\mathrm{L}}\) at the interface. Therefore \(\Delta
\Phi_{\mathrm{2D-2}}^{el}\) can be derived from Eqs (\ref{eqn:psi-2D})
and (\ref{eqn:psi-L}):
\begin{equation}
\label{eqn:Delta-Phi-exact}
\begin{aligned}
\Delta \Phi_{\mathrm{2D-w}}^{el}
&= -\int_{0}^{\psi_{\mathrm{2D}}} \sigma_{\mathrm{L}} \mathrm{d}\psi' \\
&= -\int_{0}^{\sigma_{\mathrm{L}}} \sigma'\left(
   \frac{1}{C_{\mathrm{H}}} + \frac{1}{C_{\mathrm{L}}}
                                          \right) \mathrm{d}\sigma' \\
&= -\frac{\sigma_{\mathrm{L}}^{2}}{2C_{\mathrm{H}}}
    -\sqrt{\frac{32k_{\mathrm{B}}^{3}T^{3} \epsilon_{\mathrm{w}} c_{0} N_{\mathrm{A}}}{z_{0}^{2}e^{2}}}
   \left[\cosh(\frac{z_{0}e\psi_{\mathrm{L}}}{2k_{\mathrm{B}}T}) - 1\right] \\
&= -\frac{\sigma_{\mathrm{L}}^{2}}{2C_{\mathrm{H}}} 
   - \frac{\sigma_{\mathrm{L}}^{2}}{C_{\mathrm{L}} 
   + \frac{\epsilon_{w}}{\lambda_{\mathrm{D}}}}
\end{aligned}
\end{equation}
where \(C_{\mathrm{H}}=\epsilon_{w}/d_{\mathrm{H}}\) is the geometric
capacitance of the Helmholtz double layer,
\(C_{\mathrm{L}}=\sqrt{\frac{2z_{0}^{2}e^{2}\epsilon_{\mathrm{w}}c_{0}N_{\mathrm{A}}}{k_{\mathrm{B}}T}}
\cosh (\frac{z_{0}e\psi_{\mathrm{L}}}{2k_{\mathrm{B}}T})\) is the
capacitance of diffuse layer derived from the Gouy-Chapman equation,
and
\(\lambda_{\mathrm{D}}=\sqrt{\frac{\epsilon_{\mathrm{w}}k_{\mathrm{B}}T}{2z^{2}e^{2}c_{0}N_{\mathrm{A}}}}\)
is the Debye length of the electrolyte. The quantity
\(\epsilon_{\mathrm{w}}/\lambda_{\mathrm{D}}\) is actually the
Debye-Hückel-style capacitance of the EDL.
Eq. (\ref{eqn:Delta-Phi-exact}) shows that \(\Delta
\Phi_{\mathrm{2D-w}}^{el}\) consists of the contributions from the
Helmholtz double layer and the diffuse layer, respectively.  Note that
at room temperature, when \(\sigma_{\mathrm{2D}}\) is large
(e.g. \(10^{13}\) \(e\cdot \mathrm{cm}^{-2}\)) and \(c_{0}\) is small
(e.g. \(10^{-7}\) mol\(\cdot \mathrm{L}^{-1}\)),
\(\psi_{\mathrm{L}}\)=347 mV
, which is much larger than \(k_{\mathrm{B}}T/e\), causing a significant
discrepancy between the Gouy-Chapman capacitance \(C_{\mathrm{L}}\) and
the Debye-Hückel capacitance
\(\epsilon_{\mathrm{w}}/\lambda_{\mathrm{D}}\). This effect is often
ignored in previous studies concerning the electrowetting on graphene
and other 2D materials
\cite{ostrowski_tunable_2014,daub_electrowetting_2007,goniszewski_correlation_2016,ashraf_doping-induced_2016},
and the classical Young-Lippman equation \(\Delta
\gamma=-\frac{1}{2}C\psi^{2}\) (or \(\Delta
\gamma=-\frac{\sigma^{2}}{2C}\)) is casually used instead, assuming the
capacitance to be constant. Since most of the reported samples deals with pure water with extremely low \(c_{0}\), the Debye-Hückel capacitance is much smaller than the Gouy-Chapman capacitance, leading to an overestimation of \(\Delta\cos\theta\). Therefore our
derivation in Eq. \ref{eqn:Delta-Phi-exact} provides a more accurate
approach to analyze \(\Delta \Phi_{\mathem{2D-w}}^{el}\) as a function of \(\sigma_{\mathrm{2D}}\).

\begin{figure}[htbp]
\centering
\includegraphics[width=0.85\linewidth]{../img/2d-ph-dependency.pdf}
\caption{\label{fig:Delta-cos-dependency}
(a) \(\Delta\cos\theta\) as a function of \(\sigma_{\mathrm{2D}}\).The concentration varies from \(10^{0}\) to \(10^{-7}\) mol\(\cdot\mathrm{L}^{-1}\) (b) \(\Delta\theta\) as a function of \(\sigma_{\mathrm{2D}}\) and the hypothetical contact angle on a charge-neutral 2D material layer \(\theta^{*}\). c\(_{\text{0}}\) is taken as \(10^{-7}\) mol\(\cdot\mathrm{L}^{-1}\).}
\end{figure}

Consider that the aqueous phase contains a 1:1 electrolyte with
concentration \(c_{0}\), the thickness of the Helmholtz plane
\(d_{\mathrm{H}}=3\ \mathrm{\AA}\) \cite{mcclendon_thickness_1927}, and
the surface tension of water \(\gamma_{\mathrm{w}}=72.8\) mJ\(\cdot
\mathrm{m}^{-2}\) at \(T=298\) K, we calculate the magnitude of
\(\Delta\Phi_{\mathrm{2D-w}}^{el}\) and \(\Delta\cos\theta\) as function
of \(\sigma_{\mathrm{2D}}\), as shown in
Fig. \ref{fig:Delta-cos-dependency}(a). We discover that both the
changes in the magnitude of interfacial adhesion energy and the
contact angle become more pronounced when the concentration of
electrolyte is lower. On the contrary, in conventional electrowetting
model, \(\Delta\theta\) is governed by the constant capacitance of the
dielectric layer and is almost irrelevant to the \(c_{0}\). The results indicate that the variation of \(c_{0}\) has a significant impact on \(\Delta
\Phi_{\mathrm{2D-w}}^{el}\) and \(\Delta \cos \theta\) in the
electrowetting on doped 2D materials. This is due to the fact that the
interfacial potential \(\psi_{\mathrm{2D}}\) is affected by both the
surface charge \(\sigma_{\mathrm{2D}}\) and \(c_{0}\), as indicated by
Eq. (\ref{eqn:psi-L}) and (\ref{eqn:psi-2D}). When \(c_{0}\) is lower, a
larger potential is required to be built upon the interface, giving
rise to a larger change in the interfacial wetting property.

Although the ``real'' contact angle of a 2D material can be tedious to
determine, it is still possible to estimate the magnitude of contact
angle change due to the electrowetting effect, by assuming that the
hypothetical contact angle \(\theta^{*}\) on a charge-neutral 2D
material layer. \(\theta^{*}\) consists of the effect of intrinsic
wettability, surface contamination as well the wetting translucency of
the 2D material-liquid interface. Fig. \ref{fig:Delta-cos-dependency}(b)
shows the magnitude of contact angle decrease as a function of both
\(\sigma_{\mathrm{2D}}\) and \(\theta^{*}\), when \(c_{0}=10^{-7}\)
mol\(\cdot \mathrm{L}^{-1}\) (e.g. ideally pure water). Within the range
of typical contact angles reported on graphene (ca. 40\(^{\circ}\) \textasciitilde{}
100\(^{\circ}\)), and a doping level of \(-5\times10^{13}\) \textasciitilde{}
\(5\times10^{13}\) \(e \cdot \mathrm{cm}^{-2}\), we find that the maximum
magnitude \(\Delta\theta\) is only ca. 7\(^{\circ}\) when doping level is
as high as \(\pm 5 \times 10^{13}\) \(e\cdot \mathrm{cm}^{-2}\),
essentially smaller than previously reported values which were
measured both under smaller doping levels
\cite{hong_mechanism_2016,ashraf_doping-induced_2016}.  Due to the
saturation of CO\(_{\text{2}}\) in water and soluble contaminants, the effect of
electrowetting may be even less prominent in real
situations. Therefore we believe that the electrowetting effect theory
on 2D materials alone, cannot explain the current findings of
doping-induced wettability change on graphene.

Practically in a contact angle measurement, the amount of water varies
from pL (using environmental scanning electron microscopy, ESEM) to
\(\mathrm{\mu L}\) (using goniometer). Unlike nanodroplet models used in
MD contact angle simulations, the droplets used experimentally are
large enough to be exposed to both pristine and defect 2D surface, and
can therefore be trapped in the local minimal state caused by nanoscale
defects \cite{raj_wettability_2013}, giving rise to uncertainty of the
measured contact angle. Meanwhile, it is widely observed that
nanopores and macroscopic cracks exist in the transferred 2D material,
increasing the adhesion interaction between the substrate and the
water droplet.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.95\linewidth]{../img/scheme-crack.pdf}
\caption{\label{fig:scheme-crack}
Schematic drawing of the incomplete surface coverage in (a) substrate doping and (b) electrostatic doping systems. In both cases the aqueous phase is exposed directly to the substrate, leading to a discrepancy of apparent wetting properties compared with theoretical values.}
\end{figure}

We further consider the cases where the 2D material does not
completely cover the substrate. In both the substrate-induced doping
(see Fig. \ref{fig:scheme-crack}(a)) and the electrostatic doping (see
Fig. \ref{fig:scheme-crack}(b)) systems, substrate surface charge still
exists in non-covered regions: in surface doping the charged dopants
(i.e. polyelectrolytes) will instantly build up a EDL near the
substrate surface, while in electrostatic doping the electric
displacement field still forms between the conducting 2D material and
the gate electrode via the non-covered region, also causing the ions
to accumulate at the substrate-water interface. The interfacial
adsorption density of ions can essentially be larger than the surface
charge density on 2D material, due to the partial screening of
electric displacement field of the 2D material
\cite{tian_multiscale_2016,Shih2015PartiallyScreened,Muruganathan_2015,Huttmann_2015}. Since
the electrowetting effect is amphipolar, the accumulation of cations
and anions at the 2D material surface or the non-covered region
both contribute to the decrease of the apparent surface tension
\(\hat{\gamma}_{\mathrm{2D-w}}\). We assume that the electrowetting at
the non-covered region is described by the classical Young-Lippman
\(\Delta
\gamma_{\mathrm{nc}}=-\frac{\sigma_{\mathrm{2D}}^{2}}{2C_{\mathrm{nc}}}\),
where \(C_{\mathrm{nc}}\) is the effective capacitance of the
non-covered region (taken as the EDL capacitance in substrate doping,
or the geometric capacitance of dielectric layer in electrostatic
doping). We therefore describe \(\Delta
\hat{\gamma}_{\mathrm{2D-w}}\) as a combined effect of the
electrowetting on both pristine 2D material surface and non-covered substrate surface,
characterized by the surface coverage index \(f\):
\begin{equation}
\label{eqn:apparent-gamma-combined}
\begin{aligned}
\Delta \hat{\gamma}_{\mathrm{2D-w}} &= f \Delta \gamma_{\mathrm{2D-w}} + (1-f)\Delta \gamma_{\mathrm{nc}} \\
&= f \Delta \gamma_{\mathrm{2D-w}}  -\frac{1}{2}(1-f)\frac{\sigma_{\mathrm{2D}}^{2}}{C_{\mathrm{nc}}}
\end{aligned}
\end{equation}

It should also be noted that in electrowetting experiments
where additional charge is doped to the 2D material via dielectric
layer \cite{hong_mechanism_2016}, the initial doping density
\(\sigma_{\mathrm{i}}\) should also be considered to explain the
asymmetric electrowetting behavior. In an electrowetting system where a
dielectric layer with geometric capacitance \(C_{\mathrm{d}}\) and external
voltage \(V_{\mathrm{2D}}\) is applied to the 2D material, the doping
density in the 2D material is calculated as \cite{tian_multiscale_2016}:
\begin{equation}
\label{eqn:doping-vm-2D}
V_{\mathrm{2D}} = \frac{\sigma_{\mathrm{2D}} - \sigma_{\mathrm{i}}} {C_{\mathrm{d}}} 
                 + \int_{\sigma_{\mathrm{i}}}^{\sigma_{\mathrm{2D}}} 
                   \frac{1}{C_{\mathrm{2D}}} \mathrm{d}\sigma'
\end{equation}
where \(C_{\mathrm{2D}}\) is the quantum capacitance of the 2D material, which is proportional to the density of states (DOS) \(g(E)\) at energy level \(E\): \(C_{\mathrm{2D}}=g(E)e^{2}\).

\begin{figure}[htbp]
\centering
\includegraphics[width=0.95\linewidth]{../img/plot-fitting.pdf}
\caption{\label{fig:f-nc-exp}
Theoretical and fitted experimental data of \(\Delta\cos\theta\) as a function of \(\sigma_{\mathrm{2D}}\). The electrowetting data are extracted from Ref. \cite{hong_mechanism_2016}; the ESEM data are extracted from Ref. \cite{ashraf_doping-induced_2016}.}
\end{figure}

To examine the effect of incomplete 2D material coverage, we select
two sets of reported experimental measurements of the wettability on
doped graphene sheet, namely the contact angles of substrate-doped
graphene measured by ESEM from Ref. \cite{ashraf_doping-induced_2016}
and the contact angles of electostatically-doped graphene via
goniometer from Ref. \cite{hong_mechanism_2016}. The contact angle at
experimentally ``charge-neutral'' condition (graphene attached to SiO\(_{\text{2}}\)
substrate for ESEM experiment or \(V_{\mathrm{2D}}=0\) V in
electrowetting experiment, however \(\sigma_{\mathrm{2D}}\) may not be 0
due to existence of \(\sigma_{\mathrm{i}}\)) is used as reference for
calculating \(\mathrm{d}\cos\theta\). We use
Eq. \ref{eqn:apparent-gamma-combined} to extract \(f\) and
\(\sigma_{\mathrm{i}}\) for both experiments, as seen in
Fig. \ref{fig:f-nc-exp}. We observe that in both experimental data sets,
the measured \(\Delta \cos \theta\) is essential larger than the
theoretical value derived from the Gouy-Chapman-Stern model described
here. Fitting results reveals both systems are lightly p-doped in the
``charge-neutral'' condition, which corresponds well with other
experimental reports
\cite{Shih2015PartiallyScreened,goniszewski_correlation_2016}.  The
fitted \(f\) values for both systems are as small as 3.7\%-3.8\%,
indicating the graphene layers are mostly complete. It is very
surprising to find out that due to large discrepancy of wetting
behavior on the 2D material and the underlying substrate, the measured
contact angle change can be greatly influenced by the existence of
minor defects in the 2D material. Our calculations show that extreme
care should be taken to interpret the true doping-tunable wetting
behavior of 2D materials.

The doping-induced tuning of wetting on 2D materials opens a novel
avenue for 2D-material-based liquid manipulating devices. Unlike
conventional electrowetting on dielectric (EWOD) setup, no counter
electrode is required in the liquid phase, ensuring simpler device
design. Although Eq. \ref{eqn:Delta-Phi-exact} shows that the
electrowetting effect of 2D material is only dependent on the surface
charge \(\sigma_{\mathrm{2D}}\), practically it is more favorable to
achieve the desired electrowetting by applying a smaller
\(V_{\mathrm{2D}}\). A usual setup for electrostatic doping of 2D
material involves the use of high-k dielectric or ionic gating
\cite{Das_2008,Radisavljevic_2011,Xu_2011,Newaz_2012}, where the
\(C_{\mathrm{d}}\) is comparable with \(C_{\mathrm{2D}}\). Therefore the
contribution of \(C_{\mathrm{2D}}\) in Eq. \ref{eqn:doping-vm-2D} cannot
be ignored. Combing Eqs. \ref{eqn:psi-L}, \ref{eqn:psi-2D} and
\ref{eqn:doping-vm-2D}, we get:

\begin{align}
\label{eqn:dV-sigma-2D}
\mathrm{d} V_{\mathrm{2D}} &= \left(\frac{1}{C_{\mathrm{d}}} +
\frac{1}{C_{\mathrm{2D}}}\right) \mathrm{d}\sigma_{\mathrm{2D}} \\
\label{eqn:dpsi-sigma-L}
\mathrm{d} \psi_{\mathrm{2D}} &= -\left( \frac{1}{C_{\mathrm{H}}}
+ \frac{1}{C_{\mathrm{L}}} \right) \mathrm{d}\sigma_{\mathrm{L}}
\end{align}
and by substituting \(\sigma_{\mathrm{2D}} = -\sigma_{\mathrm{L}}\), we derive the ratio between \(\psi_{\mathrm{2D}}\) and \(V_{\mathrm{2D}}\), named as \(\beta\):
\begin{equation}
\label{eqn:beta}
\beta = \frac{\mathrm{d} \psi_{\mathrm{2D}}}{\mathrm{d}
V_{\mathrm{2D}}} = \dfrac{\dfrac{1}{C_{\mathrm{L}}} +
\dfrac{1}{C_{\mathrm{H}}}}{\dfrac{1}{C_{\mathrm{d}}} + \dfrac{1}{C_{\mathrm{2D}}}}
\end{equation}
at a certain \(c_{0}\), the larger \(\beta\) is, the higher tunability in
wettability of the 2D material will be. On the device side, it can be
achieved if both \(C_{\mathrm{d}}\) and \(C_{\mathrm{2D}}\) are
larger. Increasing the value of \(C_{\mathrm{2D}}\) can be implemented
by replacing graphene--a 2D semimetal, with a 2D semiconductor, such
as TMDC \cite{tian_multiscale_2016}. Here we evaluate a
2D-material-based electrowetting device consists of a 2 nm thick HfO\(_{\text{2}}\)
dielectric layer with \(\epsilon_{\mathrm{d}}=24.0\), and an 2D material sheet
selected from graphene, silicene (2D allotrope of Si), germanene (2D
allotrope of Ge), MoS\(_{\text{2}}\), MoTe\(_{\text{2}}\), WS\(_{\text{2}}\) and WTe\(_{\text{2}}\) (see
Fig. \ref{fig:dcos-all-2D}(a)). The DOS and \(C_{\mathrm{2D}}\) are
calculated from first-principle simulations using HSE06 hydrid
functional (see Ref. \cite{tian_multiscale_2016}). The magnitude of \(\Delta \cos \theta\) as a function of \(V_{\mathrm{2D}}\) in devices based on different 2D materials is shown in Fig. \ref{fig:dcos-all-2D}(b).
\begin{figure}[htbp]
\centering
\includegraphics[width=0.95\linewidth]{../img/dcos-all-2D.pdf}
\caption{\label{fig:dcos-all-2D}
(a) Schematic illustration of the 2D-material-based electrowetting device. (b) \(\Delta\cos\theta\) as a function of \(V_{\mathrm{2D}}\) for selected 2D materials.}
\end{figure}

As expected in Eq. \ref{eqn:beta}, at the same \(V_{\mathrm{2D}}\) level,
the 2D TMDC semiconductors (MoS\(_{\text{2}}\), MoTe\(_{\text{2}}\), WS\(_{\text{2}}\), WTe\(_{\text{2}}\)) exhibit a much
higher response \(\Delta \cos \theta\) than 2D semimetals (silicene,
germanene and graphene). We can briefly rank the voltage tunability of
the selected 2D materials by their DOS: MoTe\(_{\text{2}}\) > MoS\(_{\text{2}}\) > WTe\(_{\text{2}}\) > WS\(_{\text{2}}\)
> germanene > silicene > graphene. Notably, TMDCs can achieve a
\(\Delta \Phi_{\mathrm{2D}}\) as high as 0.15 when
\(V_{\mathrm{2D}}=\pm1.5\) V is applied, corresponding a contact angle
decrease at the magnitude of 10\(^{\circ}\) when the intrinsic contact
angle is ca. 90\(^{\circ}\).  A high-DOS 2D material further suppresses
electrochemical reactions at the solid-liquid interface, as less
electrochemical potential (i.e. the Fermi level \(E_{\mathrm{F}}\)) is
required. We conclude that a 2D material with higher DOS can
essentially reduced the voltage needed for doping, pushing
liquid-phase 2D-material-based devices to a more operational regime.

In conclusion, we propose a multiscale approach for modeling the
doping-induced tunable wettability of 2D materials, by combining the
reorientation effect of water molecules estimated by MD simulations,
and the electrowetting effect calculated by a continuum model. Taking
graphene as an example, we find that electrostatic interaction plays a
major role at both scales for the graphene-water interface. We further
show that, by considering the incomplete coverage of 2D material on
the substrate, it is possible to evaluate the recent findings of
doping-induced tuning of graphene's wettability with the proposed
model. We find that minor surface incompleteness can cause great
discrepancy in the measured value of interfacial wettability, and
extreme care should be taken to interpret the observed
electrowetting phenomena. In addition, we prove that a 2D material
with higher density of states can essentially reduce the gating
voltage in a 2D-material-based electrowetting device, and rank the
tunability of the 2D materials as: MoTe\(_{\text{2}}\) > MoS\(_{\text{2}}\) > WTe\(_{\text{2}}\) > WS\(_{\text{2}}\) >
germanene > silicene > graphene. Our multiscale analysis provides a
comprehensive view of the wettability of 2D material interface, and we
believe operational 2D-material-based liquid manipulating devices will
be facilitated by the principles presented in this letter.
\bibliography{ref}
\end{document}

### 2017-02-07 writing/dcos_sigma.py

@@ -1,0 +1,123 @@
+import matplotlib
+from matplotlib import patches
+from pubfigure.FigureCollection import FigureCollection
+import numpy
+import scipy
+import scipy.constants as const
+import pycse.orgmode as org
+
+eps_w = 80*const.epsilon_0
+d_H = 0.3*10**-9                # Helmholtz plane
+n_L = numpy.linspace(-5, 5, 100)
+sigma_L = n_L*const.e*10**13*10**4
+T = 298
+C_H = eps_w/d_H
+gamma_w = 72.8e-3               # surface tension in SI
+
+def cal_2D(c0, sigma_, what="Delta_cos", z=1):
+    # c0 should use mol/m^3
+    sigma = -sigma_
+    psi_L = -2*const.k*T/z/const.e*scipy.arcsinh(
+            sigma/scipy.sqrt(8*c0*const.N_A*eps_w*const.k*T))
+    psi_2D = psi_L - sigma/C_H
+    A = scipy.sqrt(2*z**2*const.e**2*eps_w*c0*const.N_A/const.k/T)
+    B = z*const.e*psi_L/(2*const.k*T)
+    C_L = A*scipy.cosh(B)
+    l_D = scipy.sqrt(eps_w*const.k*T/(2*z**2*const.e**2*c0*const.N_A))
+    Delta_Phi_el = -sigma**2/(2*C_H) - sigma**2/(C_L+eps_w/l_D)
+    Delta_cos = -Delta_Phi_el/gamma_w
+
+    # Classical value
+    # C = scipy.sqrt(32*const.k**3*T**3*eps_w*c0*const.N_A/z**2/const.e**2)
+    # Delta_Phi_el = -sigma**2/(2*C_H) - C*(scipy.cosh(B)-1)
+    # Delta_cos = -Delta_Phi_el/gamma_w
+
+    # Classical value
+    sigma = scipy.sqrt(8*c0*const.N_A*eps_w*const.k*T)*scipy.sinh(z*const.e*psi_L/2/const.k/T)
+    C = scipy.sqrt(32*const.k**3*T**3*eps_w*c0*const.N_A/z**2/const.e**2)
+    Delta_Phi_el = -sigma**2/(2*C_H) - C*(scipy.cosh(B)-1)
+    Delta_cos = -Delta_Phi_el/gamma_w
+    if what is "Delta_Phi_el":
+        return Delta_Phi_el
+    elif what is "Delta_cos":
+        return Delta_cos
+
[…]

### 2017-02-07 writing/fun-read-xvg.py

@@ -1,0 +1,26 @@
+def read_xvg_energy(filename):
+    data = {}
+    with open(filename) as f:
+        s_tmp = ""
+        s = f.readline()
+        while s.startswith("-") is not True:
+            s_tmp = s
+            s = f.readline()
+        attrs = s_tmp.strip().split()  # Attributes of columns
+        s = f.readline()
+        while len(s) > 0:
+            # print(s)
+            name = ""
+            i = 0
+            s = s.split()
+            while not s[i][0].isdecimal() and not s[i][0] == "-":
+                name += s[i]
+                i += 1
+            d_dic = {}
+            for att in attrs[1:]:
+                d_dic[att] = float(s[i])
+                i += 1
+            d_dic["Unit"] = s[-1]
+            data[name] = d_dic
+            s = f.readline()
+    return data

### 2017-02-07 writing/plot_change_adhesion.py

@@ -1,0 +1,137 @@
+import numpy
+import scipy
+import scipy.constants as const
+import matplotlib
+matplotlib.use("Agg")
+import matplotlib.pyplot as plt
+from fun_read_xvg import read_xvg_energy
+import pycse.orgmode as org
+
+charge_per_atom = [0, 1, 2, 3, 4, 5, 6, 8, 10, 12, 15, 20, 30]
+charge_per_atom += [-1, -2, -3, -4, -5, -6, -8, -10, -12, -15, -20, -30]
+charge_per_atom.sort()
+
+c_atom_to_sigma = lambda x: x*2/(2.465e-8**2*scipy.sin(scipy.pi/3))
+
+
+# Convert the adhesion energy from
+
+A_c = 15.1e-18                  # area of the whole plane in m^2
+
+f_base = "../data/MD/E_int_%d.xvg"
+
+
+vdW_tot = []
+vdW_err = []
+coulomb_tot = []
+coulomb_err = []
+potential_tot = []
+potential_err = []
+coul_LR = []
+
+f_0 = f_base % 0
+data = read_xvg_energy(f_0)
+vdw0 = data["LJ(SR)"]["Average"] + data["Disper.corr."]["Average"]
+coul0 = data["Coulomb(SR)"]["Average"] + data["Coul.recip."]["Average"]
+potential0 = data["Potential"]["Average"]
+coul_LR_0 = data["Coul.recip."]["Average"]
+
+for e in charge_per_atom:
+    f_n = f_base % e
+    # print(f_n)
+    data = read_xvg_energy(f_n)
+    vdw = data["LJ(SR)"]["Average"] + data["Disper.corr."]["Average"]
+    vdw_err = data["LJ(SR)"]["RMSD"] + data["Disper.corr."]["RMSD"]
+    # coul = data["Coulomb(SR)"]["Average"]
+    coul = data["Coulomb(SR)"]["Average"] + data["Coul.recip."]["Average"]
+    coul_err = data["Coulomb(SR)"]["RMSD"] + data["Coul.recip."]["RMSD"]
+    _coul_LR = data["Coul.recip."]["Average"]
+    potential = data["Potential"]["Average"]
+    potential_err_ = data["Potential"]["RMSD"]
+    # print(vdw, coul)
+    vdW_tot.append(vdw-vdw0)
[…]

### 2017-02-07 writing/plot_density.py

@@ -1,0 +1,58 @@
+import numpy, matplotlib
+matplotlib.use("Agg")
+import matplotlib.pyplot as plt
+import scipy.constants as const
+import scipy
+import pycse.orgmode as org
+
+charge_per_atom = [-12, 0, 12]
+
+c_atom_to_sigma = lambda x: x*2/(2.465e-8**2*scipy.sin(scipy.pi/3))
+z_gr = 2.177
+
+f_charge_base = "../data/MD/charge_int_%d.xvg"
+f_charge_water = "../data/_MD/charge_water_surf.xvg"
+
+f_dens_base = "../data/MD/density_int_%d.xvg"
+f_dens_water = "../data/MD/density_water_surf.xvg"
+
+charge_per_atom.sort()
+
+c_water = numpy.genfromtxt(f_charge_water, delimiter=(12, 17), skip_header=19)
+d_water = numpy.genfromtxt(f_dens_water, delimiter=(12, 17), skip_header=19)
+
+# ax1.plot(c_water[:, 0] - z_gr, c_water[:, 1], label="Water Only")
+
+def plot_den(fig, what="mass"):
+    ax = fig.add_subplot(111)
+    if what is "mass":
+        for c in charge_per_atom:
+            d_sys = numpy.genfromtxt(f_dens_base % c,
+                                     delimiter=(12, 17), skip_header=19)
+            ax.plot(d_sys[:, 0] - z_gr,
+                    d_sys[:, 1], label=r"%d$\times10^{-3}$ $e$/atom" % (c))
+        ax.set_ylabel(r"$\rho_{\mathrm{w}}$ (kg$\cdot$m$^{-3}$)")
+        ax.set_xlabel(r"$z$ (nm)")
+        ax.set_xlim(0, 1.5)
+        ax.legend(loc=0)
+    elif what is "charge":
+        for c in charge_per_atom:
+            c_sys = numpy.genfromtxt(f_charge_base % c,
+                                     delimiter=(12, 17), skip_header=19)
+            ax.plot(c_sys[:, 0] - z_gr, c_sys[:, 1],
+                    label=r"%d$\times10^{-3}$ $e$/atom" % (c) )
+        ax.set_ylabel(r"$\delta_{\mathrm{w}}$ ($e\cdot$nm$^{-3}$)")
+        ax.set_xlabel(r"$z$ (nm)")
+        ax.set_xlim(0, 1.5)
+        ax.legend(loc=0)
+
[…]

### 2017-02-07 writing/paper-Tian-gr-wetting.tex
Added the part for charge-induced 2D surface tension change

@@
-% Created 2017-01-17 Tue 11:30
+% Created 2017-02-07 Tue 22:04
 % Intended LaTeX compiler: pdflatex
@@
 \(\gamma_{\mathrm{2D}}\) and \(\gamma_{\mathrm{w}}\) are the surface
-tensions of the 2D material and water in vacuum,
-respectively. \(\Phi_{\mathrm{2D-w}}\) is contributed by both the
+tensions of the 2D material and water in air,
+respectively.
+
+\(\Phi_{\mathrm{2D-w}}\) is contributed by both the
 short-range dispersion interaction and long-range electrostatic
@@
 length scale, forming an EDL at the interface and decrease the
-interfacial surface tension by the phenomenon known as
-electrowetting. To model the effect of electrowetting, we first
+interfacial surface tension by the phenomenon known as electrowetting.
+Revisiting Eq. (\ref{eqn:def-adhesion}), we know that the change of
+interfacial tension due to electrostatic interactions, \(\Delta
+\Phi_{\mathrm{2D-w}}^{\mathrm{el}}\), is given by:
+
+\begin{equation}
+\label{eqn:Delta-Phi-el-def}
+\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}} = \Delta \gamma_{\mathrm{2D-w}}^{\mathrm{el}}
+                                           -\Delta \gamma_{\mathrm{2D}}^{\mathrm{el}}
+                                           -\Delta \gamma_{\mathrm{w}}^{\mathrm{el}}
+\end{equation}
+where \(\Delta \gamma_{\mathrm{2D-w}}^{\mathrm{el}}\), \(\Delta
+\gamma_{\mathrm{2D}}^{\mathrm{el}}\) and \(\Delta
+\gamma_{\mathrm{w}}^{\mathrm{el}}\) denote the change of surface
+tension of 2D material-water interface, 2D material-air and
+water-air, respectively. In the continuum model, all the changes of
+surface tensions can be modeled by surface excesses. From the
+isothermal 2D Gibbs-Duhem equation we can calculate the change of surface
+energy \(\mathrm{d} \gamma\):
+
+\begin{equation}
+\label{eqn:iso-gibbs-duhem}
+\displaystyle
+\mathrm{d}\gamma = -\frac{\sum_{\mathrm{i}} n_{\mathrm{i}}^{\mathrm{ex}}}{A} \mathrm{d} \mu_{\mathrm{i}} 
+                 = -\sum_{\mathrm{i}} \Gamma_{i} \mathrm{d} \mu_{\mathrm{i}}
+\end{equation}
+where \(n_{\mathrm{i}}^{\mathrm{ex}}\) is the surface excess amount of
+specie i, \(A\) is the unit are of the surface, \(\Gamma_{\mathrm{i}}\) is
+the surface excess concentration of specie i, and \(\mu_{\mathrm{i}}\)
+is the chemical potential of specie i. Eq. (\ref{eqn:iso-gibbs-duhem})
+indicates that: both the charges accumulated on the 2D material
+surface and the formation of electric double layer will alter the
+interfacial tension of 2D materials. As far as we are concerned, the
+effect of charge-induced surface tension change of 2D materials has
+rarely been addressed previously. For a charged 2D material surface in
+air, the decrease of surface tension equals the work required to
+charge the isolated 2D material:
+
+\begin{equation}
+\label{eqn:dgamma-QC}
+\begin{aligned}
+\mathrm{d} \gamma_{\mathrm{2D}}^{\mathrm{el}} &= -\Gamma_{e} \mathrm{d} E_{\mathrm{F}} \\
+                                              &= -\frac{\sigma_{\mathrm{2D}}}{C_{\mathrm{2D}}} \mathrm{d}\sigma_{\mathrm{2D}}
+\end{aligned}
+\end{equation}
+where \(E_{\mathrm{F}}=\mu_{e}\) is the Fermi level of the 2D material
+(equals the chemical potential of electrons in the 2D materials) and
+\(C_{\mathrm{2D}}\) is the quantum capacitance of the 2D material, which
+is proportional to the density of states (DOS) \(g(E_{\mathrm{F}})\) at
+Fermi level \(E_{\mathrm{F}}\):
+\(C_{\mathrm{2D}}=g(E_{\mathrm{F}})e^{2}\). Due to the fact that most 2D
+materials possess quantum capacitances essentially smaller than those
+of bulk materials, one would expect that the charge-induced-decrease
+of surface tension of 2D materials is more prominent than bulk
+materials. Here we demonstrate the degree of charge-induced
+surface tension decrease of several typical 2D materials in
+air. The selected 2D materials are graphene, silicene (2D allotrope
+of Si), germanene (2D allotrope of Ge), MoS\(_{\text{2}}\), MoTe\(_{\text{2}}\), WS\(_{\text{2}}\) and
+WTe\(_{\text{2}}\), respectively. Their DOS as functions of \(E_{\mathrm{F}}\) have been previously
+reported by density functional theory (DFT) calculation, based on the
+HSE06 hybrid functional approach \cite{tian_multiscale_2016}. The
+charge-induced decrease of surface tension of the 2D materials
+\(\Delta \gamma_{\mathrm{2D}}^{\mathrm{el}}\), as a function of the
+surface charge density \(\sigma_{\mathrm{2D}}\), is shown in Fig. \ref{fig:dgamma-sigma}.
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.95\linewidth]{../img/dgamma-sigma.pdf}
+\caption{\label{fig:dgamma-sigma}
+\(\Delta \gamma_{\mathrm{2D}}^{\mathrm{el}}\) as a function of \(\sigma_{\mathrm{2D}}\) for several 2D materials: graphene, silicene, germanene, MoS\(_{2}\), MoTe\(_{2}\), WS\(_{2}\) and WTe\(_{2}\)}
+\end{figure}
+It can be observed from our calculations that graphene has the largest
+degree of surface tension decrease (ca. 22 mJ\(\cdot\mathrm{m}^{-2}\)
+when \(\sigma_{\mathrm{2D}}=\pm5\times10^{13}\ e\cdot
+\mathrm{cm}^{-2}\)), due to the fact that graphene has the lowest
+\(C_{\mathrm{2D}}\) among the selected 2D materials
+\cite{tian_multiscale_2016}. We can rationalize the \(\Delta
+\gamma_{\mathrm{2D}}^{\mathrm{el}}\) - \(\sigma_{\mathrm{2D}}\) relation
+of the 2D materials by their \(C_{\mathrm{2D}}\) values: the 2D
+semimetals (graphene, silicene and germanene) generally have larger
+decrease of surface tension, compared with the semiconducting 2D TMDCs
+at same doping level, due to the limited DOS dispersion in 2D
+semimetals. Notably, the results indicate that a significant decrease
+of surface tension of 2D materials (at the order of 10 mJ\(\cdot
+\mathrm{m}^{-2}\)) can be achieved with a doping at the order of
+\(10^{13}\ e\cdot \mathrm{cm}^{-2}\), and may eventually be experimentally
+observed.
+
+Similarly, \(\Delta \gamma_{\mathrm{2D-w}}^{\mathrm{el}}\) is
+contributed by both the 2D surface charge and the charge accumulation
+in the EDL:
+
+\begin{equation}
+\label{eqn:dgamma-2D-w}
+\mathrm{d}\gamma_{\mathrm{2D-w}}^{\mathrm{el}} = -\frac{\sigma_{\mathrm{2D}}}{e} \mathrm{d}E_{\mathrm{F}}
+-\sum_{\mathrm{i}} z_{\mathrm{i}}e\Gamma_{\mathrm{i}}^{\mathrm{s}} \mathrm{d}\psi_{\mathrm{2D}}
+\end{equation}
+where \(\Gamma_{\mathrm{i}}^{\mathrm{s}}\) and \(z_{\mathrm{i}}\) are the
+surface excess concentration and valency of ionic solute i,
+respectively; \(\psi_{\mathrm{2D}}\) is the electrostatic potential at the 2D
+material-water interface. On the other hand \(\gamma_{\mathrm{w}}\) is
+independent of the surface charge of the 2D material, since no surface
+excess is present at the water-air interface. We therefore derive
+the expression for \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}\) as
+follows:
+
+\begin{equation}
+\label{eqn:Delta-Phi-final}
+\begin{aligned}
+\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}} &= -\frac{\sigma_{\mathrm{2D}}}{e}dE_{\mathrm{F}} 
+                                             -\sum_{\mathrm{i}} z_{\mathrm{i}}e\Gamma_{\mathrm{i}}^{\mathrm{s}} \mathrm{d}\psi_{\mathrm{2D}}
+                                             +\frac{\sigma_{\mathrm{2D}}}{e}dE_{\mathrm{F}} \\
+                                          &= -\sigma_{\mathrm{L}} \mathrm{d}\psi_{\mathrm{2D}}
+\end{aligned}
+\end{equation}
+where \(\sigma_{\mathrm{L}}\) is the total charge density in the EDL. As
+the accumulation of charge on the 2D material surface occurs both on
+the 2D material-air and 2D material-water interfaces, their
+contributions to the surface tension is canceled out. As a result
+\(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}\) is governed by the ion
+accumulation in EDL alone, in consistent with the trivial
+electrowetting theory (constant solid surface tension). However, the
+absolute values of \(\gamma_{\mathrm{2D-w}}\) and \(\gamma_{\mathrm{2D}}\)
+do change due to the aforementioned phenomenon.
+
+To evaluate the effect of electrowetting, we first
 consider that a contamination layer with thickness \(d_{\mathrm{c}}\)
@@
 \end{equation}
-From the Gouy-Chapman model of symmetric electrolytes we know:
+From the Gouy-Chapman model of 1 symmetric electrolyte we know:
 \begin{align}
@@
 
-The change of interfacial adhesion energy is calculated using the
-Gibbs adsorption isotherm equation:
-\(\mathrm{d}\Phi_{\mathrm{2D-w}}^{el} = \mathrm{d}
-\gamma_{\mathrm{2D-w}}^{el} = -z_{0}e\Gamma
-\mathrm{d}\psi_{\mathrm{2D}}\), where \(\Gamma\) is the interfacial
-adsorption number at the solid-liquid interface. Since the Debye
-length is much smaller than the diameter of a macroscopic droplet,
-\(\Gamma\) can be approximated by the total excessive charge density
-\(\sigma_{\mathrm{L}}\) at the interface. Therefore \(\Delta
-\Phi_{\mathrm{2D-2}}^{el}\) can be derived from Eqs (\ref{eqn:psi-2D})
+The exact solution of \(\Delta
+\Phi_{\mathrm{2D-w}}^{el}\) can be derived from Eqs (\ref{eqn:psi-2D})
 and (\ref{eqn:psi-L}):
@@
 derivation in Eq. \ref{eqn:Delta-Phi-exact} provides a more accurate
-approach to analyze \(\Delta \Phi_{\mathem{2D-w}}^{el}\) as a function of \(\sigma_{\mathrm{2D}}\).
+approach to analyze \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}\) as a function of \(\sigma_{\mathrm{2D}}\).
 
@@
 \end{equation}
-where \(C_{\mathrm{2D}}\) is the quantum capacitance of the 2D material, which is proportional to the density of states (DOS) \(g(E)\) at energy level \(E\): \(C_{\mathrm{2D}}=g(E)e^{2}\).
 
@@
 2D-material-based electrowetting device consists of a 2 nm thick HfO\(_{\text{2}}\)
-dielectric layer with \(\epsilon_{\mathrm{d}}=24.0\), and an 2D material sheet
-selected from graphene, silicene (2D allotrope of Si), germanene (2D
-allotrope of Ge), MoS\(_{\text{2}}\), MoTe\(_{\text{2}}\), WS\(_{\text{2}}\) and WTe\(_{\text{2}}\) (see
-Fig. \ref{fig:dcos-all-2D}(a)). The DOS and \(C_{\mathrm{2D}}\) are
-calculated from first-principle simulations using HSE06 hydrid
-functional (see Ref.
-\cite{tian_multiscale_2016}).
-The magnitude of \(\Delta \cos \theta\) as a function of \(V_{\mathrm{2D}}\) in devices based on different 2D materials is shown in Fig.
-\ref{fig:dcos-all-2D}(b).
+dielectric layer with \(\epsilon_{\mathrm{d}}=24.0\), and an 2D material
+sheet selected from graphene, silicene, germanene, MoS\(_{\text{2}}\), MoTe\(_{\text{2}}\), WS\(_{\text{2}}\)
+and WTe\(_{\text{2}}\) (see Fig. \ref{fig:dcos-all-2D}(a)). The magnitude of \(\Delta
+\cos \theta\) as a function of \(V_{\mathrm{2D}}\) in devices based on
+different 2D materials is shown in Fig. \ref{fig:dcos-all-2D}(b).
 \begin{figure}[htbp]

### 2017-02-22 writing/paper-Tian-gr-wetting.tex
Change style to achemso (ACS Nano)

@@
-% Created 2017-02-07 Tue 22:04
+% Created 2017-02-22 Wed 13:07
 % Intended LaTeX compiler: pdflatex
-\documentclass[aps,prl,reprint,groupedaddress,amsmath,amssymb, showpacs]{revtex4-1}
+\documentclass[journal=ancac3,manuscript=article,email=true]{achemso}
  \usepackage{minted}
@@
 \usepackage{fontspec}
-\date{}
-\title{}
-\begin{document}
-
-\title{A Multiscale View of the Doping-Induced Tunable Wettability on Two-Dimensional Materials}
 \author{Tian Tian}
@@
 \affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
+\date{}
+\title{Wettability of Doped Two-Dimensional Materials}
+\begin{document}
 
-\date{\today}
-
+\newpage{}
 \begin{abstract}

### 2017-02-22 writing/paper-Tian-gr-wetting.tex
Change abstract

@@
-% Created 2017-02-22 Wed 13:07
+% Created 2017-02-22 Wed 14:18
 % Intended LaTeX compiler: pdflatex
@@
 \begin{abstract}
-  The emergence of 2D-material-based liquid-phase devices calls for
-  the need for understanding the wetting property at the
-  2D-material-liquid interface, and particularly the doping-induced
-  tuning of wetting properties. In this letter, we propose a
-  multiscale view of the doping-induced tunable wettability of 2D
-  materials, by combining the reorientation effect of water molecules
-  estimated by MD simulation, and the electrowetting effect calculated
-  by continuum model. We reveal the electrostatic nature of the
-  doping-induced wettability under both scale. We further evaluate the
-  recent finding of doping-induced wettability tuning of graphene with
-  the proposed model, by considering incomplete surface coverage of 2D
-  materials. We find that minor surface incompleteness can cause great
-  discrepancy in the measured value of interfacial wettability, requiring
-  extreme care for interpreting the experimental results. In
-  addition, we prove that a 2D material with higher density of states
-  can essentially reduce the gating voltage in a 2D-material-based
-  electrowetting device, and rank the tunability of the 2D materials
-  as: MoTe$_{2}$ > MoS$_{2}$ > WTe$_{2}$ > WS$_{2}$ > germanene > silicene >
-  graphene. Our multiscale analysis provides a comprehensive view of
-  the wettability of 2D material interface, and we believe operational
-  2D-material-based liquid manipulating devices will be facilitate by
-  the principles presented in this letter.
+  Understanding molecular interactions between liquid and the doped two-dimensional (2D) 
+  materials enables new technology opportunities in functional surfaces and ultrathin membranes. 
+  Here, we develop the first theoretical framework to model the wettability of the doped two-dimensional 
+  (2D) materials as a function of their doping level. Multiscale physical phenomena are considered, 
+  including: (i) the change of 2D materials surface energy, 
+  (ii) the molecular reorientation of liquid molecules adjacent to the interface, 
+  and (iii) the electrical double layer (EDL) formed in the liquid phase. 
+  \textcolor{cyan}{We propose that the EDL effect dominates the contact angle change }
+  and show that upon doping, the decrease of the equilibrium water contact angle on a sheet of defect-free, 
+  monolayer 2D material is typically less than 7 degrees. 
+  We then study the role of the surface defects and the influence of 2D material choice.
+  \textcolor{cyan}{Our analysis show that the defect density has a great impact on the water contact angle on the doped
+  2D materials, and is responsible for the discrepancy between the recent experimental observations and our proposed 
+  theory. Based on the quantum capacitances (QCs) of various 2D materials calculated by density functional theory (DFT),
+  we predict that when the the 2D materials is doped by electrostatic gating, 
+  the contact angle change on 2D semiconductors (e.g. transition metal dichalcogenides (TMDCs)) is more
+  sensitive to the gate voltage compared to that on 2D semimetals (e.g. graphene). 
+  Selecting a 2D material with a higher QC essentially reduces the gate voltage required to reach the same doping level,
+  and ensures a wider operational region in 2D-material-based liquid phase devices.}
+  \textcolor{magenta}{
+  FINAL CONCLUSIONS PLACE HOLDER.
+  }
+
 \end{abstract}

### 2017-02-22 writing/paper-Tian-gr-wetting.tex
Modify introduction part

@@
-% Created 2017-02-22 Wed 14:18
+% Created 2017-02-22 Wed 21:46
 % Intended LaTeX compiler: pdflatex
@@
   We then study the role of the surface defects and the influence of 2D material choice.
-  \textcolor{cyan}{Our analysis show that the defect density has a great impact on the water contact angle on the doped
+  \textcolor{cyan}{Our analysis show that the defect density plays a crucial role in the water contact angle on the doped
   2D materials, and is responsible for the discrepancy between the recent experimental observations and our proposed 
   theory. Based on the quantum capacitances (QCs) of various 2D materials calculated by density functional theory (DFT),
-  we predict that when the the 2D materials is doped by electrostatic gating, 
+  we predict that when the the 2D material is doped by electrostatic gating, 
   the contact angle change on 2D semiconductors (e.g. transition metal dichalcogenides (TMDCs)) is more
@@
 
-The emergence of two-dimensional (2D) materials has attracted broad
-interest in various research fields, inspired by their unique physical
-and chemical properties. Recent progress of scalable 2D material
-synthesis paves the way for their liquid phase 2D-material-based
-applications, for instance functional coating
-\cite{Prasai_2012,Rafiee_2010,Kim_2014}, nanotribology devices
-\cite{Yin_2014,Tang_2016,Feng_2016}, nanoporous desalination apparatus
-\cite{Surwade_2015,Rollings_2016,Jain_2015}, droplet manipulation
-\cite{Hern_ndez_2013,Vijayarangamuthu_2015}, etc.  To fully exploit the
-physics of the interface between 2D materials and liquid phase, a
-comprehensive understanding of the 2D-material-liquid interaction, and in
-particular, the wettability, is of great importance.
+\section{Introduction}
+\label{sec:org30908ab}
 
-Wetting on atomically-thin 2D materials has long been a hot but highly
-disputed topic
-\cite{taherian2013what,Kozbial_2015,Parobek_2015,Govind_Rajan_2016}.
-Accurate description of the intrinsic wettability of 2D materials is
-known to be challenging. Recent studies show that the wettability on
-graphene \cite{li_effect_2013,Xu_2013_withwhat,kozbial_study_2014} and
-MoS\(_{\text{2}}\) \cite{Kozbial_2015,Chow_2015} is strongly affected by airborne
-contaminants. Meanwhile, the contact angle measurement technique which
-has been widely to determine the wettability on 2D materials, may also
-suffer inaccuracy from contact angle hysteresis caused by local
-defects \cite{raj_wettability_2013}.  On the other hand, unlike bulk
-materials, the thickness of a 2D material falls within the effective
-range of dispersion interactions.  As a result, the dispersion
-interaction between the substrate underneath the 2D material and
-liquid molecules is not fully screened by the 2D material, giving rise
-to the fascinating property known as the ``wetting-translucency''
-\cite{rafiee_wetting_2012,shih_breakdown_2012,shih_wetting_2013}.
-Moreover, 2D semimetals (graphene, silecene, germanene, etc.) and 2D
-semiconductors (e.g, transition metal dichalcogenides (TMDCs)) possess
-significantly lower density of states (DOS) than bulk materials,
-making them easier to be doped by the underlying substrates
-\cite{Chen_2013,Varchon_2007,Giovannetti_2008} or electrostatic gating
-\cite{Das_2008,Perera_2013}. Due to the ubiquity of doping in 2D
-materials, it is worth investigating the relationship between the
-doping level and wettability. Several recent reports have addressed
-the issue of doping-induced tunability of graphene's wettability, from
-both atomistic simulations
-\cite{ostrowski_tunable_2014,ren_interfacial_2015,Taherian_2015,daub_electrowetting_2007}
-and experimental demonstrations
-\cite{hong_mechanism_2016,goniszewski_correlation_2016,ashraf_doping-induced_2016}.
-However, discrepancies exist between individual reports, concerning
-the origin and magnitude of the doping-induced wetting
-tunability. Moreover, to get a full perspective of such phenomenon,
-the gap between the nanoscale simulations and macroscopic experimental
-results needs to be filled, and the aforementioned issues of intrinsic
-wettability and wetting translucency should also be taken into account.
+Two-dimensional (2D) materials, the crystalline films with a thickness
+of one atom or one molecule, combine optical transparency and the
+quantum-confined properties.
+\begin{center}
+\fbox{
+\begin{minipage}[c]{.8\linewidth}
+\textbf{\textsf{\textsc{TODO}}} [cite some review papers].
+
+\end{minipage}
+}
+\end{center}
+Recent progress in the scalable production of large-area 2D materials
+\begin{center}
+\fbox{
+\begin{minipage}[c]{.8\linewidth}
+\textbf{\textsf{\textsc{TODO}}} cite review papers
+
+\end{minipage}
+}
+\end{center}
+has paved the way for the applications of functional surfaces and
+ultrathin membranes.
+\begin{center}
+\fbox{
+\begin{minipage}[c]{.8\linewidth}
+\textbf{\textsf{\textsc{TODO}}} cite review papers
+
+\end{minipage}
+}
+\end{center}
+
+The realization of these technologies essentially requires precise
+control over the interactions between liquid and the ultrathin
+materials, which motivates fundamental research of their
+wettability. An accurate determination of the interfacial tension,
+nevertheless, remains highly disputed
+\cite{taherian2013what,Kozbial_2015,Parobek_2015,Govind_Rajan_2016}. Early
+literature on understanding the surface science of 2D materials has
+highlighted the effects of the airborne contaminants
+\cite{li_effect_2013,Xu_2013_withwhat,kozbial_study_2014,Kozbial_2015,Chow_2015}
+and the underlying substrate
+\cite{raj_wettability_2013,rafiee_wetting_2012,shih_breakdown_2012,shih_wetting_2013},
+since the length scale for the van der Waals (vdW) interactions is
+comparable to the thickness of a monolayer. On the other hand, a
+subtle but important fact is that the 2D semimetals (e.g, graphene and
+silicene) and 2D semiconductors (e.g., transition metal
+dichalcogenides (TMDCs)) possess low density of states (DOSs) around
+the intrinsic Fermi level (\(E_{\mathrm{F}}\)), such that the effect of
+doping, either induced by the surroundings
+\cite{Chen_2013,Varchon_2007,Giovannetti_2008}, or by the electrostatic
+gating \cite{Das_2008,Perera_2013}, also comes into play. Very recently,
+the doping-induced change in the wettability of graphene has been
+observed in the contact-angle experiments
+\cite{hong_mechanism_2016,goniszewski_correlation_2016,ashraf_doping-induced_2016},
+and the molecular dynamics (MD) simulations
+\cite{ostrowski_tunable_2014,ren_interfacial_2015,Taherian_2015,daub_electrowetting_2007}. However,
+most reports described the doping-dependent wettability with the basic
+Young-Lippmann equation (YLE) \cite{Lippmann_1875}, whereas the
+interplay between the polar orientation of water molecules at the
+interface \cite{Shen_2006} and the electronic structure of the 2D
+materials is often ignored. In order to address the discrepancies
+among the literature, a more complete theoretical picture that bridges
+the gap between different length scales is clearly required.
 

### 2017-06-01 writing/paper-Tian-gr-wetting.tex
Minor change and clean up files

@@
-% Created 2017-02-22 Wed 21:46
+% Created 2017-06-01 Thu 19:09
 % Intended LaTeX compiler: pdflatex
-\documentclass[journal=ancac3,manuscript=article,email=true]{achemso}
+\documentclass[journal=jacsat,manuscript=article,email=true]{achemso}
  \usepackage{minted}
@@
 \usepackage{xcolor}
+\usepackage{amsmath}
 \usepackage{fontspec}
+\keywords{Two-dimensional materials, doping, wettability, multiscale analysis, MD Simulation, eletrical double layer}
 \author{Tian Tian}
 \affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
+\author{Siyu Li}
+\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy & Environment, Southeast University, Nanjing, Jiangsu 210096, China}
+\author{Lingling Zhao}
+\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy & Environment, Southeast University, Nanjing, Jiangsu 210096, China}
 \author{Elton J. G. Santos}
@@
 \date{}
-\title{Wettability of Doped Two-Dimensional Materials}
+\title{Multiscale Understanding the Wettability of Doped Two-Dimensional Materials}
 \begin{document}
@@
 \begin{abstract}
-  Understanding molecular interactions between liquid and the doped two-dimensional (2D) 
-  materials enables new technology opportunities in functional surfaces and ultrathin membranes. 
-  Here, we develop the first theoretical framework to model the wettability of the doped two-dimensional 
-  (2D) materials as a function of their doping level. Multiscale physical phenomena are considered, 
-  including: (i) the change of 2D materials surface energy, 
+  Engineering molecular interactions at two-dimensional (2D) materials interfaces enables new technological opportunities 
+  in functional surfaces and molecular epitaxy. Quantifying the interplay between the interfacial forces and electric 
+  potential of 2D materials represents the crucial first step for understanding their wettability.
+  Here we develop the first theoretical framework to model the wettability of the doped 2D 
+  materials by properly bridging the multiscale physical phenomena at the 2D interfaces,
+  including: (i) the change of 2D materials surface energy (atomistic scale), 
   (ii) the molecular reorientation of liquid molecules adjacent to the interface, 
-  and (iii) the electrical double layer (EDL) formed in the liquid phase. 
-  \textcolor{cyan}{We propose that the EDL effect dominates the contact angle change }
-  and show that upon doping, the decrease of the equilibrium water contact angle on a sheet of defect-free, 
-  monolayer 2D material is typically less than 7 degrees. 
-  We then study the role of the surface defects and the influence of 2D material choice.
-  \textcolor{cyan}{Our analysis show that the defect density plays a crucial role in the water contact angle on the doped
-  2D materials, and is responsible for the discrepancy between the recent experimental observations and our proposed 
-  theory. Based on the quantum capacitances (QCs) of various 2D materials calculated by density functional theory (DFT),
-  we predict that when the the 2D material is doped by electrostatic gating, 
-  the contact angle change on 2D semiconductors (e.g. transition metal dichalcogenides (TMDCs)) is more
-  sensitive to the gate voltage compared to that on 2D semimetals (e.g. graphene). 
-  Selecting a 2D material with a higher QC essentially reduces the gate voltage required to reach the same doping level,
-  and ensures a wider operational region in 2D-material-based liquid phase devices.}
-  \textcolor{magenta}{
-  FINAL CONCLUSIONS PLACE HOLDER.
-  }
+  (molecular scale), and (iii) the electrical double layer (EDL) formed in the liquid phase (macroscopic scale). 
+  The latter two effects are found to be the major mechanisms responsible for the contact angle change upon doping.
+  When the doping level is electrostatically tuned, we demonstrate that 2D materials with high quantum capacitances 
+  (e.g., transition metal dichalcogenides, TMDCs) possess a wider range of tunability in the interfacial tension. 
+  Furthermore, practical considerations such as defect and airborne contamination are also quantitatively discussed. 
+  Our analysis implies that the doping level can be another variable to modulate the wettability at the interface of 2D materials,
+  as well as the molecular packing behavior on a 2D material-coated surface, 
+  essentially faciliating the interfacial engineering of 2D materials.
+\end{abstract}
+# \maketitle
 
-\end{abstract}
-\maketitle
+\newpage{}
 
 \section{Introduction}
-\label{sec:org30908ab}
+\label{sec:org435dbee}
 
@@
 of one atom or one molecule, combine optical transparency and the
-quantum-confined properties.
-\begin{center}
-\fbox{
-\begin{minipage}[c]{.8\linewidth}
-\textbf{\textsf{\textsc{TODO}}} [cite some review papers].
-
-\end{minipage}
-}
-\end{center}
-Recent progress in the scalable production of large-area 2D materials
-\begin{center}
-\fbox{
-\begin{minipage}[c]{.8\linewidth}
-\textbf{\textsf{\textsc{TODO}}} cite review papers
-
-\end{minipage}
-}
-\end{center}
-has paved the way for the applications of functional surfaces and
-ultrathin membranes.
-\begin{center}
-\fbox{
-\begin{minipage}[c]{.8\linewidth}
-\textbf{\textsf{\textsc{TODO}}} cite review papers
-
-\end{minipage}
-}
-\end{center}
-
-The realization of these technologies essentially requires precise
-control over the interactions between liquid and the ultrathin
-materials, which motivates fundamental research of their
-wettability. An accurate determination of the interfacial tension,
-nevertheless, remains highly disputed
+quantum-confined properties
+\cite{Novoselov_2005,Mas_Ballest__2011,Novoselov_2016}.  Recent progress in the scalable production of large-area 2D
+materials \cite{Boott_2015,Li_2016} has paved the way for the
+applications of functional surfaces and ultrathin membranes
+\cite{Prasai_2012,Feng_2016,Rafiee_2010,Yin_2014,Surwade_2015,Hern_ndez_2013}.
+The concept of van der Waals (vdW) epitaxy has been further extended
+to grow molecular heterostructures on 2D material-coated surfaces for
+a variety of applications
+\cite{Shi_2012_epitaxy_graphene,Kim_2017_remote_epitaxy,Novoselov_2016}. The
+realization of these technologies essentially requires precise control
+over the molecular interactions at 2D material interfaces, which
+motivates fundamental research of their interfacial properties, in
+particular the wettability.  An accurate determination of the
+interfacial tension, nevertheless, remains highly disputed
 \cite{taherian2013what,Kozbial_2015,Parobek_2015,Govind_Rajan_2016}. Early
@@
 \cite{raj_wettability_2013,rafiee_wetting_2012,shih_breakdown_2012,shih_wetting_2013},
-since the length scale for the van der Waals (vdW) interactions is
+since the length scale for the van der Waals (vdW) radius is
 comparable to the thickness of a monolayer. On the other hand, a
@@
 \cite{Chen_2013,Varchon_2007,Giovannetti_2008}, or by the electrostatic
-gating \cite{Das_2008,Perera_2013}, also comes into play. Very recently,
-the doping-induced change in the wettability of graphene has been
-observed in the contact-angle experiments
+gating \cite{Das_2008,Perera_2013}, also comes into play. Recent advance
+in the \textit{ab initio} calculations and scanning tunneling
+microscopy (STM) studies on the adsorbed molecules on graphene
+\cite{Muruganathan_2015,Huttmann_2015} has provided some clues to the
+doping-dependent vdW interactions. Subsequently, the doping-induced
+change in the wettability of graphene has been observed in the
+contact-angle experiments
 \cite{hong_mechanism_2016,goniszewski_correlation_2016,ashraf_doping-induced_2016},
 and the molecular dynamics (MD) simulations
-\cite{ostrowski_tunable_2014,ren_interfacial_2015,Taherian_2015,daub_electrowetting_2007}. However,
-most reports described the doping-dependent wettability with the basic
-Young-Lippmann equation (YLE) \cite{Lippmann_1875}, whereas the
-interplay between the polar orientation of water molecules at the
-interface \cite{Shen_2006} and the electronic structure of the 2D
-materials is often ignored. In order to address the discrepancies
-among the literature, a more complete theoretical picture that bridges
-the gap between different length scales is clearly required.
+\cite{ostrowski_tunable_2014,ren_interfacial_2015,Taherian_2015,daub_electrowetting_2007}. In
+this respect, however, most reports described the doping-dependent
+wettability with the basic Young-Lippmann equation (YLE)
+\cite{Lippmann_1875}, whereas the interplay between the orientation of
+liquid molecules at the interface \cite{Shen_2006} and the electronic
+structure of the 2D materials is often ignored. In order to address
+the discrepancies among the literature, a general and complete
+theoretical picture that bridges the gap between different length
+scales, is clearly required.
 
-In this letter, we propose a multiscale approach to properly model the
-doping-induced tuning of 2D materials' wettability. We model the
-change of surface adhesion energy between water and 2D material as a
-combined effect of (i) reorientation of water molecules, characterized
-by molecular dynamic (MD) simulations and (ii) electrowetting due to
-formation of electric double layer, calculated by a continuum model
-based on modified Young-Lippman theory. By using graphene as an
-example, we demonstrate that, the electrostatic interaction plays a
-major role in both the reorientation and electrowetting effects. By
-further considering the surface coverage of 2D materials, we evaluate
-the previous reported result on the doping-induced wetting behavior of
-graphene using the proposed multiscale model. We find that the
-existence of minor defects can cause great discrepancy between the
-observed wetting property and theoretical values, requesting attentive
-interpretation of the experimental results. Moreover, we quantify the
-tunability of interfacial tension in a gate-controlled
-2D-material-based electrowetting device as a function of the DOS of
-the 2D material, and rank several 2D materials according to their
-tunability. We show that 2D materials with higher DOS such as
-transition metal dichalcogenides (TMDCs), perform better than graphene
-by means of wettability regulation. Our findings provide a
-comprehensional view of the wettability of 2D materials, as well as
-guidance for operational liquid-phase 2D material-based devices.
+In this report, we propose the first theoretical framework to model
+the change of interfacial tension between liquid and a sheet of
+monolayer 2D material. Multiscale physical phenomena are
+considered. At the atomistic scale, we formulate the dependence of
+surface energy of a 2D material on the doping density using the
+quantum capacitance (QC) calculated by the density functional theory
+(DFT). Next, the surface-charge-induced reorientation of liquid
+molecules adjacent to the interface is associated with an N-body
+system, which is resolved by molecular dynamics (MD) simulations,
+allowing quantification of the interfacial tension in the absence of
+electrolytes in liquid. The effect of the electrical double layer
+(EDL) induced by the electrostatic interactions between the 2D
+material surface charges and the ionic species in liquid, is then
+addressed at the continuum level. Practical considerations, such as
+the defect density and the surface contamination are also taken into
+account to provide a comprehensive understanding of the
+phenomena. Finally, we examine and validate our theory by comparing
+with the contact angle changes reported in the electrowetting and the
+substrate-induced doping experiments.
 
-Due to the complex dynamic nature of wetting
-\cite{Cassie_1944,Wenzel_1936,Gao_2007,Marmur_2009}, we only study the
-static wettability of 2D materials. We only consider water as the
-liquid phase, as most liquid-phase applications of 2D materials are
-also in aqueous environment. The macroscopic feature of
-wetting--contact angle \(\theta\), is connected to the interfacial
-adhesion energy \(\Phi_{\mathrm{2D-w}}\) by the Young's equation:
+\section{Results and Discussions}
+\label{sec:org66b0b42}
+
+\subsection{Surface Energy of Doped 2D Materials}
+\label{sec:org87cc68c}
+
+Consider a liquid (\emph{L}) droplet sitting on a flat, monolayer 2D
+material (\emph{2D}) supported by a solid substrate, following the Young’s
+equation, the change of the equilibrium contact angle \(\theta\) upon
+doping, is given by
 \begin{equation}
-\label{eqn:young's equation}
-\Phi_{\mathrm{2D-w}} = -\gamma_{\mathrm{L}}(1+\cos\theta)
+\label{eqn-def-Young-Delta-theta}
+\gamma_{\mathrm{L}} \Delta \cos\theta = \Delta \gamma_{\mathrm{2D}}
+                                 - \Delta \gamma_{\mathrm{2D-L}}
 \end{equation}
-where \(\Phi_{\mathrm{2D-w}}\) is defined as:
+where \(\gamma_{\mathrm{L}}\) and \(\gamma_{\mathrm{2D}}\) are the surface
+tensions of liquid and the 2D material considered,
+respectively, \(\gamma_{\mathrm{2D-L}}\) is the interfacial tension between the
+liquid and the contacting 2D material. We define \(\Delta \gamma =
+\gamma - \gamma_{0}\) for all the surface (interfacial) tensions considered and
+\(\Delta \cos \theta = \cos \theta - \cos \theta_{0}\), where the
+subscript 0 corresponds to that in the case of intrinsic 2D material,
+with the doping density per unit area, \(\sigma_{\mathrm{2D}} = 0\). In
+the theoretical analysis presented here, we aim to model \(\Delta \cos
+\theta\) as a function of \(\sigma_{\mathrm{2D}}\). Note that under the
+assumptions that (i) the change of \(E_{\mathrm{F}}\) in the doped 2D
+materials does not result in the interfacial electron transfer,
+namely, the electrochemical reactions, (ii) the doping effect does not
+change the surface energy of the underlying substrate, and (iii) the
+vdW and electrostatic interactions are perfectly additive and
+pairwise, one can decouple the effect of the underlying
+substrate. Therefore the debate of the “wetting transparency”
+\cite{rafiee_wetting_2012,shih_wetting_2013}, does not affect our analysis.
+
+First, we model the dependence of \(\gamma_{\mathrm{2D}}\) on the doping
+level. Consider a closed system with constant pressure and volume
+containing a sheet of free-standing 2D material, following the Euler
+homogeneous function theorem of thermodynamics, the total internal
+energy of the system \(U\), is given by \(U = TS + \mu_{\mathrm{2D}} N +
+\gamma_{\mathrm{2D}} A + \psi_{\mathrm{2D}} q\)
+\cite{bard_electrochemical_1980}, where \(T\) is the temperature, \(S\) is
+the entropy, \(\mu_{\mathrm{2D}}\) is the chemical potential of the 2D
+material per unit lattice, \(N\) is the number of unit lattices, \(A\) is
+the area of the 2D material, and \(\psi_{\mathrm{2D}}\) and \(q\) are the
+electric potential and total charge in the 2D material,
+respectively. At constant \(T\), combining with the first law of
+thermodynamics and the differential form of \(U\), it follows:
 \begin{equation}
-\label{eqn:def-adhesion}
-\Phi_{\mathrm{2D-w}} = \gamma_{\mathrm{2D-w}} - \gamma_{\mathrm{2D}} - \gamma_{\mathrm{w}}
+\label{eqn-dgamma-dpsi}
+\mathrm{d} \gamma_{\mathrm{2D}} = -\frac{q}{A} \mathrm{d} \psi_{\mathrm{2D}}
+                                = -\sigma_{\mathrm{2D}} \mathrm{d} \psi_{\mathrm{2D}}
 \end{equation}
+relating the surface tension change of a free-standing 2D material as
+a function of its doping density \(\sigma_{\mathrm{2D}}\). After bringing an amount of charge
+\(q\) from infinity to a charge-neutral 2D material in the
+aforementioned system, the surface energy change is therefore given
+by:
+\begin{equation}
+\label{eqn-delta-gamma-sigma-free-2D}
+\Delta \gamma_{\mathrm{2D}} = - \int_{0}^{\psi_{\mathrm{2D}}} \sigma_{\mathrm{2D}} \mathrm{d}\psi'
+                            = - \int_{0}^{\sigma_{\mathrm{2D}}} \sigma' \left( \frac{1}{C_{\mathrm{2D}}}\right) \mathrm{d} \sigma'
+\end{equation}
+where \(C_{\mathrm{2D}} = g(E_{\mathrm{F}}) e^{2}\) is the quantum
+capacitance of the 2D material \cite{davies_two-dimensional_1997,Das_Sarma_2011},
+\(g(E_{\mathrm{F}})\) is the DOS as a function of \(E_{\mathrm{F}}\),
+\(\psi_{\mathrm{2D}} = -(E_{\mathrm{F}} - E_{\mathrm{F,0}})/e\) and
+\(E_{\mathrm{F,0}}\) corresponds to the Fermi level of the 2D material
+at the charge neutral point (CNP). Accordingly, eq
+\ref{eqn-delta-gamma-sigma-free-2D} provides a simple relation which
+depicts the surface tension change of a 2D material at the
+quantum-mechanical level. We have calculated the DOSs as a function of
+\(E_{\mathrm{F}}\) for a variety of 2D materials using the density
+functional theory \cite{tian_multiscale_2016}. Note that we take into
+account a fractional component of the exact exchange from the
+Hartree-Fock (HF) theory hybridized with the DFT exchange-correlation
+functional at the level of the HSE06 hybrid functional. Therefore, any
+limitation of the exchange and correlation functional utilized in the
+chemical description of the energy levels can be improved. The
+following 2D materials are considered: TMDC monolayers (MX\(_{\text{2}}\), M =
+Mo, W and X = S, Se, Te), silicene, germanene, phosphorene (monolayer
+black phosphorus), and graphene. The doping density in a 2D material
+is calculated by integrating the DOS from its intrinsic Fermi level,
+i.e., \(\sigma_{\mathrm{2D}} = \int_{E_{\mathrm{F,0}}}^{E_{\mathrm{F}}}
+g(E')e \mathrm{d}E'\) \cite{john_quantum_2004}.
 
-where \(\gamma_{\mathrm{2D-w}}\) is the surface tension between the
-interface of the 2D material and the aqueous phase,
-\(\gamma_{\mathrm{2D}}\) and \(\gamma_{\mathrm{w}}\) are the surface
-tensions of the 2D material and water in air,
+Figure \ref{fig:dgamma-sigma} presents the calculated \(\Delta
+\gamma_{\mathrm{2D}}\) as a function of \(\sigma_{\mathrm{2D}}\) for the
+2D materials considered here. Clearly, the doping of 2D materials
+reduces their surface energy, or based on the classical definition,
+the work required to separate two stacked monolayers is lowered. Among
+the 2D materials, we find that graphene shows the highest degree of
+surface energy decrease, up to -16 mJ\(\cdot \mathrm{m}^{-2}\) , or
+\textasciitilde{}20\% reduction of its intrinsic surface tension
+\cite{shih_wetting_2013}, at \(\sigma_{\mathrm{2D}}\) = \(\pm
+4\times10^{13}\ e\cdot \mathrm{cm}^{-2}\). However, as will be
+discussed later, it does not imply a reduced wettability because the
+quantum capacitance effect also reduces the interfacial tension,
+\(\gamma_{\mathrm{2D-L}}\). A clear trend is that the surface energy
+decrease is more significant in the 2D semimetals (e.g. graphene,
+silicene, and germanene) than that in the 2D semiconductors
+(e.g. TMDCs). This reflects the fact that the effective mass of
+carriers in the 2D semiconductors is much higher than that in the 2D
+semimetals \cite{davies_two-dimensional_1997}, thereby resulting in
+high DOS, as well as a high \(C_{\mathrm{2D}}\) (see eq
+\ref{eqn-delta-gamma-sigma-free-2D}). This concept also explains why the
+surface energy decrease for silicene and germanene are lower than
+that for graphene \cite{Yan_2013}.  To our knowledge, the doping-induced
+surface energy change in 2D materials has never been investigated
+experimentally, which may be of interest for future study.
+
+\subsection{Reorientation of Liquid Molecules}
+\label{sec:org188528c}
+
+Next, we discuss the interactions between 2D materials and liquid. In
+a doped 2D material, the delocalized carriers are confined in the 2D
+plane. Therefore, following the spirit of the mean-field theory, we
+treat it as a continuously, uniformly charged surface. Since these
+charges are either generated by interacting with the underlying
+substrate, or electrostatically induced by gating, the
+electroneutrality still holds before in contact with liquid. The
+surface charges result in two consequences that may change
+\(\gamma_{\mathrm{2D-L}}\), including (i) the reorientation of adjacent
+liquid molecules \cite{ostrowski_tunable_2014} and (ii) the formation of
+the electric double layer (EDL) at the liquid-solid interface, known
+as the electrowetting effect
+\cite{Lippmann_1908,mugele_electrowetting:_2005}. Under the assumption
+that the vdW and electrostatic (Coulombic) interactions are additive,
+which compose the interfacial tension, we propose that the
+interfacial tension change is given by:
+
+\begin{equation}
+\label{eqn-delta-gamma-decompose}
+\Delta \gamma_{\mathrm{2D-L}} = \Delta \gamma_{\mathrm{2D-L}}^{\mathrm{Orien}}
+                              + \Delta \gamma_{\mathrm{2D-L}}^{\mathrm{EDL}}
+\end{equation}
+where \(\Delta \gamma_{\mathrm{2D-L}}^{\mathrm{Orien}}\) and \(\Delta
+\gamma_{\mathrm{2D-L}}^{\mathrm{EDL}}\) correspond to the contributions
+from the reorientation and the EDL effects, respectively, as
+schematically illustrated in Figure \ref{fig:scheme-method}. We also
+assume that \(\Delta \gamma_{\mathrm{2D-L}}^{Orien}\) is independent of
+the electrolyte concentration, since the concentration of liquid
+molecules is typically orders-of-magnitude higher.
+
+First we discuss the orientation effect. Understanding the
+reorientation effect involves positioning and sampling the collective,
+time-averaged motion of liquid molecules near the interface, which is
+a standard molecular dynamics (MD) problem. Note that even with the
+state-of-the-art MD algorithms, it remains challenging to accommodate
+the calculations for the EDL, in which the length scale of electric
+field can be larger than one micrometer in diluted electrolyte
+solutions, e.g., pure water with self-ionized H\(_{\text{3}}\)O\(^{\text{+}}\) and OH\(^{\text{-}}\)
+ions. Here we consider the graphene-water interface as a model
+system. All MD simulations were carried out using the GROMACS 4.5
+software package \cite{Hess_2008}. Monolayer graphene was modeled as an
+infinite rigid sheet in the x-y plane. The carbon atoms of graphene
+were treated as uncharged Lennard-Jones (LJ) spheres with \(\sigma\) =
+0.34 nm and \(\epsilon\) = 0.223 kJ/mol \cite{Cheng_1990}, using the
+force-field parameters reported by Tummala and Striolo
+\cite{Tummala_2008}. The doping effect is included by assigning an equal
+amount of charge \(\sigma_{\mathrm{2D}} / \rho_{\mathrm{G}}\), where
+\(\rho_{\mathrm{G}}\) is the surface density of carbon atoms, to each
+carbon atom. The \(\sigma_{\mathrm{2D}}\) range considered here
+approximately correspond to the partial atomic charge from −0.012 to
+0.012 \(e/\mathrm{atom}\). Water molecules were modeled using the SPC/E
+model \cite{Berendsen_1987} with bond lengths and angles of water
+molecules constrained using the SETTLE algorithm
+\cite{Miyamoto_1992}. Lennard-Jones interactions were treated with a
+cutoff distance of 1 nm, with those between different atoms calculated
+using the standard geometric averaging rule. Long-range electrostatic
+interactions were treated using the particle mesh Ewald (PME)
+summation method \cite{Darden_1993,Essmann_1995} with a short-range
+cutoff distance of 1 nm. The velocity-rescaled Berendsen thermostat
+was implemented to maintain a constant system temperature of 298.15 K
+\cite{Bussi_2007}. All simulations were carried out under the NVT
+ensemble.
+
+In order to precisely determine the interfacial interactions using MD
+simulations, instead of the commonly used model that compared the
+nanoscale contact angle by placing a nanodroplet onto a sheet of
+suspended 2D material
+\cite{ostrowski_tunable_2014,daub_electrowetting_2007,ren_interfacial_2015,Taherian_2015},
+we simulate the difference of the total potential energy, \(E\), between
+two separate systems that contain (i) only water molecules with two
+surfaces exposing to vacuum (L), and (ii) the same amount of water
+molecules with one surface in contact with graphene (placed at z = 0)
+and the other surface exposing to vacuum (GL) (see Figure
+\ref{fig:MD-res}(a) and \ref{fig:MD-res}(b)) . Periodic boundary
+conditions are used in all three directions of the simulation boxes in
+both systems. Additionally, a vacuum layer of 3 nm thick along the
+\emph{z}-axis is placed to separate the periodic images of the
+graphene-water system. The total energy in both systems can be
+formulated as: \(E_{\mathrm{L}} = \mu_{\mathrm{L}}n_{\mathrm{L}} +
+2\gamma_{\mathrm{L}}S\) and
+\(E_{\mathrm{GL}}=\mu_{\mathrm{L}}n_{\mathrm{L}}+(\gamma_{\mathrm{L}} +
+\gamma_{\mathrm{2D-L}} + \gamma_{\mathrm{2D}})S\), respectively, where
+\(\mu_{\mathrm{L}}\) is the chemical potential per water molecule in the
+bulk phase, \(n_{\mathrm{L}}\) is the number of liquid molecules in the
+simulation box, and \(S\) is the area of the \emph{xy}-plane.  A simulation
+box with a sufficiently large length of 21 nm in the \emph{z}-direction is used,
+with a 18-nm thick block of water molecules, to minimize the effect of
+the long-range electrostatic interaction between the charged graphene
+and the water molecules at the water-vacuum interface, by ensuring
+that the time-averaged dipole moment for the water molecules at the
+water-vacuum interface is approximately zero (see Supporting Information
+Figure S1).  One can show that \(E_{\mathrm{GL}} - E_{\mathrm{L}} =
+(\gamma_{\mathrm{2D-L}} + \gamma_{\mathrm{2D}} - \gamma_{L})S =
+(\Phi + 2 \gamma_{\mathrm{2D}})S\), where \(\Phi\) is the interfacial
+energy, which is defined as \(\Phi = \gamma_{\mathrm{2D-L}} -
+\gamma_{\mathrm{2D}} - \gamma_{\mathrm{L}}\), and combining with eq
+\ref{eqn-def-Young-Delta-theta}, the change of interfacial energy
+\(\Delta \Phi\) can be formulated as:
+\begin{equation}
+\label{eqn-Delta-Phi-Delta-cos}
+\Delta \Phi = \Delta (E_{\mathrm{GL}} - E_{\mathrm{L}})/S - 2\Delta \gamma_{\mathrm{2D}} = -\gamma_{\mathrm{L}} (\Delta \cos \theta)^{\mathrm{Orien}}
+\end{equation}
+where \((\Delta\cos \theta)^{\mathrm{Orien}}\) corresponds to the
+contact angle change due to the reorientation effect. Note that in the
+current MD simulation setup, the surface tension of the 2D material
+remains unchanged (i.e. \(\Delta \gamma_{\mathrm{2D}}=0\)), since the
+Fermi level change with
+respect to \(\sigma_{\mathrm{2D}}\) (see eq
+\ref{eqn-delta-gamma-sigma-free-2D}) is not included in the algorithm. In all simulations we assume a
+constant surface tension of water \(\gamma_{\mathrm{L}}=72.8\
+\mathrm{mJ}\cdot \mathrm{m}^{-2}\). Accordingly, \(\Delta \Phi\) follows
+\(\Delta \Phi = \Delta (E_{\mathrm{GL}} - E_{\mathrm{L}})/S = \Delta
+\Phi_{\mathrm{LJ}} + \Delta \Phi_{\mathrm{Coul}}\), where \(\Delta
+\Phi_{\mathrm{LJ}}\) and \(\Delta \Phi_{\mathrm{Coul}}\) correspond to
+the change for the vdW and Coulombic interaction potentials,
 respectively.
 
-\(\Phi_{\mathrm{2D-w}}\) is contributed by both the
-short-range dispersion interaction and long-range electrostatic
-interaction between the 2D material and water. The existence of
-additional charges in 2D materials gives rise to the reorientation of
-adjacent water molecules \cite{ostrowski_tunable_2014}. On the other
-hand, the formation of electric double layer (EDL) in an ionic
-solution near the interface also alters the interfacial adhesion
-properties, known as the electrowetting effect \cite{Lippmann_1908},
-which has been widely used in microfluidic applications
-\cite{Mugele_2005}.  Owing to the additive nature of dispersion and
-electrostatic interactions, we propose that the change of interfacial
-adhesion energy \(\Delta \Phi_{\mathrm{2D-w}}\) is a combined effect of
-the reorientation effect \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{or}}\) and EDL
-formation \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}\):
-\begin{equation}
-\label{eqn:contrib-adhesion-change}
-\Delta \Phi_{\mathrm{2D-w}} = \Delta \Phi_{\mathrm{2D-w}}^{\mathrm{or}}
-                              + \Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}
-\end{equation}
-
-A multiscale approach is needed to combine both effects as their
-effective length scales are different. We use molecular dynamics (MD)
-simulations for sampling the orientation effect adjacent to the 2D
-material; in addition a continuum model is implemented to describe the
-contribution of EDL formation, since state-of-art MD simulations fail to
-handle diluted ionic solution systems where the Debye length can be as
-long as 10\(^{\text{3}}\) nm. Our multiscale modeling approach is schematically illustrated in Fig. \ref{fig:scheme-method}.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.95\linewidth]{../img/scheme-methods.pdf}
-\caption{\label{fig:scheme-method}
-Scheme of the multiscale approach for modeling the doping-induced wettability tuning of 2D materials.}
-\end{figure}
-
-It is also noteworthy that our multiscale approach is compatible with
-the issues of the intrinsic wettability and wetting translucency of 2D
-materials. Since we are dealing with the change of interfacial
-adhesion energy as a function of surface charge, the absolute value of
-\(\Phi_{\mathrm{2D-w}}\) or \(\gamma_{\mathrm{2D-w}}\) (extracted from intrinsic wetting property and wetting translucency theory) can be treated as
-independent variables.
-
-We model the charged 2D materials as rigid sheets with uniform surface
-charge density \(\sigma_{\mathrm{2D}}\), either by substrate or
-electrostatic doping. We also assume that the 2D material has no
-dissociable groups which can change the aqueous pH value
-\cite{zuccaro_tuning_2015} and the 2D material is inert to
-electrochemical reaction at the interface
-\cite{bard_electrochemical_1980}.  First we use graphene as a model
-system to show the effect of reorientation of water molecules on the
-interfacial adhesion energy. Different from previous approaches which
-used MD simulations to extract the contact angle of nanodroplets on
-graphene
-\cite{ostrowski_tunable_2014,daub_electrowetting_2007,ren_interfacial_2015,Taherian_2015},
-where the interfacial adhesion energy cannot be accurately measured
-due to changed contact area between water and graphene, here we
-propose to use a continuous water monolith in the MD simulation with periodic boundary conditions in the x and y directions to
-calculate the interfacial adhesion energy \(\Phi_{\mathrm{2D-w}}\).
+Figure \ref{fig:MD-res}(c) shows the values of \(\Delta \Phi\), and its
+contributions from the Lennard-Jones (\(\Delta \Phi_{\mathrm{LJ}}\)) and
+Coulombic interactions (\(\Delta \Phi_{\mathrm{Coul}}\)), as functions
+of \(\sigma_{\mathrm{2D}}\). We note that the change of adhesion energy
+in the doped graphene system is dominated by the Coulombic
+interaction. When the doping level of graphene is \(\pm 4 \times
+10^{13}\ e\cdot \mathrm{cm}^{-2}\), the Coulombic interaction causes a
+decrease in the adhesion energy of -10\textasciitilde{}-15 mJ\(\cdot \mathrm{m}^{-2}\),
+while the vdW interaction, on the other hand, causes a slight increase
+in the adhesion energy by less than 5 mJ\(\cdot \mathrm{m}^{-2}\). In
+other words, concerning the reorientation of water molecules at high
+doping levels, the Coulombic interaction favors the decrease of
+\(\gamma_{\mathrm{2D-L}}\), and thus the contact angle \(\theta\), while
+the vdW interaction slightly increases \(\gamma_{\mathrm{2D-L}}\) and
+\(\theta\). We shall note that due to the highly polar nature of water
+molecules, the average inter-molecular equilibrium distance in the
+absence of external electric field is shorter than the Lennard-Jones
+equilibrium distance. Increasing the doping density of the graphene
+sheet essentially enhances the electrostatic attractions between
+graphene and water molecules and further decreases the inter-molecular
+equilibrium distance, as reflected from the red shifts of the first
+peaks in Figure \ref{fig:MD-res}(d) for the two charged graphene cases
+compared to the charge-neutral case, which eventually leads to a
+slight increase in .  The plot of \(\Delta \Phi\) as a function of
+\(\sigma_{\mathrm{2D}}\) in Figure \ref{fig:MD-res}(b) shows an apparent
+asymmetric shape. This is can be further revealed from the
+\emph{z}-dependent local molecular density \(\rho_{\mathrm{L}}\) and charge
+density \(\delta_{\mathrm{L}}\) profiles of the water molecules, as
+shown in Figure \ref{fig:MD-res}(d) and \ref{fig:MD-res}(c),
+respectively. The molecular density of the first water layer adjacent
+to graphene increases when graphene is p-doped
+(\(\sigma_{\mathrm{2D}}=0.012\ e\cdot \mathrm{cm}^{-2}\), or
+equivalently 4.56 \textit{e}/atom) and decreases when graphene is
+n-doped (\(\sigma_{\mathrm{2D}}=-0.012\ e\cdot \mathrm{cm}^{-2}\), or
+equivalently 4.56 \textit{e}/atom) compared with the case of
+charge-neutral graphene, indicating the polarity-dependent adsorption
+of water molecules on graphene. Similar trend can also be observed in
+the \(\delta_{\mathrm{L}}\) profiles. Interestingly, \(\Delta \Phi\)
+exhibits positive Coulombic contribution for slightly n-doped
+graphene, when \(\sigma_{\mathrm{2D}} \approx -2\times10^{13}\ e\cdot
+\mathrm{cm}^{-2}\), indicating that the reorientation of interfacial
+water molecules by small negative charges on graphene helps minimizing
+the Coulombic interactions.
 \begin{center}
@@
 \begin{minipage}[c]{.8\linewidth}
-\textbf{\textsf{\textsc{TODO}}} Description for MD simulation
+\textbf{\textsf{\textsc{TODO}}} Explanation of the positive part of \(\Delta \Phi\) when \(\sigma_{\mathrm{2D}} \approx -2\) ?
+
+\end{minipage}
+}
+\end{center}
+Although the MD simulation results show the Coulombic interaction
+between the doped graphene and water molecules dominate the
+reorientation effect, such conclusion may not be readily applied to
+other types of 2D materials. For 2D semimetal systems (silicene and
+germanene), the intensity of Coulombic interactions may vary due to
+the mismatch among the lattice constants. On the other hand, for the
+2D semiconductors such as the TMDCs, in which their
+\(\gamma_{\mathrm{2D-L}}\) are already largely determined by the
+Coulombic interactions in the intrinsic case
+\cite{Govind_Rajan_2016,Chow_2015}. Therefore we anticipate that
+case-by-case studies and DFT calculations which deal with the
+post-doping charge redistribution, might be required.
+\begin{center}
+\fbox{
+\begin{minipage}[c]{.8\linewidth}
+\textbf{\textsf{\textsc{TODO}}} Try find other references?
 
@@
 
-The adhesion energy \(\Phi_{\mathrm{2D-w}}^{or}\) in the MD simulation is
-defined as:
+\subsection{Electrical Double Layer Effect}
+\label{sec:org0491aea}
+
+The EDL effect that decreases the interfacial tension has been
+extensively studied in the context of the electrowetting phenomena
+\cite{Mugele_2005}, in which the interfacial tension is reduced due to
+the adsorption of ionic species at the solid-liquid interface. Here we
+extend the concept to the 2D material-liquid systems. Consider a
+closed system containing an interface formed between liquid and a
+sheet of free-standing 2D material, by combining with the Gibbs
+adsorption theory \cite{bard_electrochemical_1980}, one can obtain:
 \begin{equation}
-\label{eqn:Delta-Phi-or-definition}
+\label{eq:2}
+\mathrm{d} \gamma_{\mathrm{2D-L}}^{\mathrm{EDL}} = -\sigma_{\mathrm{2D}} \mathrm{d} \psi_{\mathrm{2D}}
+                                                   -\sum_{\mathrm{i}} \Gamma_{\mathrm{i}} \mathrm{d}\mu_{\mathrm{i}}
+\end{equation}
+where \(\Gamma_{\mathrm{i}}\) and \(\mu_{\mathrm{i}}\) are the interfacial
+excess and the chemical potential of the ionic specie \(i\) at the
+interface, respectively. Relative to that in the bulk phase
+(\(\psi=0\)), the interfacial chemical potential of a charged solute
+\(\mu_{\mathrm{i}}\), is given by
+\(\mu_{\mathrm{i}}=z_{\mathrm{i}}e\psi_{\mathrm{2D}}\), where
+\(z_{\mathrm{i}}\) is the valency of component \(i\), under the assumption
+that the interfacial electric potential is equal to
+\(\psi_{\mathrm{2D}}\). As with the approach leading to eq
+\ref{eqn-delta-gamma-sigma-free-2D}, it follows:
+\begin{equation}
+\label{eqn-Delta-gamma-2DL-EDL-full}
+\Delta \gamma_{\mathrm{2D-L}}^{\mathrm{EDL}} = 
+-\int_{0}^{\sigma_{\mathrm{2D}}} \sigma' \left(\frac{1}{C_{\mathrm{2D}}}\right) \mathrm{d}\sigma'
+-\int_{0}^{\sigma_{\mathrm{L}}} \sigma' \left(\frac{1}{C_{\mathrm{EDL}}}\right) \mathrm{d}\sigma'
+\end{equation}
+where \(\sigma_{\mathrm{L}}\) is the interfacial charge density per unit
+area in the liquid phase, and \(C_{\mathrm{EDL}}\) is the EDL
+capacitance. Combining eq \ref{eqn-Delta-gamma-2DL-EDL-full} with eqs
+\ref{eqn-def-Young-Delta-theta} and \ref{eqn-delta-gamma-sigma-free-2D},
+the contact angle change due to the EDL effect, \((\Delta \cos
+\theta)^{\mathrm{EDL}}\) is given by:
+\begin{equation}
+\label{eqn-Delta-cos-EDL}
+(\Delta \cos \theta)^{\mathrm{EDL}} = -\frac{1}{\gamma_{\mathrm{L}}}
+                                      \int_{0}^{\sigma_{\mathrm{L}}} \sigma' 
+                                      \left(\frac{1}{C_{\mathrm{EDL}}}\right) \mathrm{d}\sigma'
+\end{equation}
+In other words, eqs \ref{eqn-delta-gamma-sigma-free-2D} and
+\ref{eqn-Delta-gamma-2DL-EDL-full} suggest that \(\sigma_{\mathrm{2D}}\)
+decreases both \(\gamma_{\mathrm{2D}}\) and \(\gamma_{\mathrm{2D-L}}\) to
+the same extent, i.e. \(\int_{0}^{\sigma_{\mathrm{2D}}}
+\sigma'/C_{\mathrm{2D}} \mathrm{d}\sigma'\), such that the contribution
+of quantum capacitance cancels out in the YLE.
+
+For a \(z:z\) electrolyte solution, with the molar concentration \(c_{0}\)
+and the electrolyte valence \(z\), we describe the electric potential
+profile in liquid with the one-dimensional Gouy-Chapman-Stern model
+\cite{Stern_1924_theory}, as schematically shown in Figure
+\ref{fig:res-EDL}(a).  The EDL consists of a Helmholtz layer with the
+permittivity of liquid \(\epsilon_{\mathrm{L}}\) and thickness
+\(d_{\mathrm{H}}\), next to the Gouy-Chapman (GC) diffuse layer where
+the electric potential profile follows the Poisson Boltzmann equation
+\cite{bard_electrochemical_1980}. The \(C_{\mathrm{EDL}}\) of the
+Gouy-Chapman-Stern model is equivalent to two capacitors in series,
+namely,
+\begin{equation}
+\label{eqn-GCS-capacitance-series}
+\frac{1}{C_{\mathrm{EDL}}} = \frac{1}{C_{\mathrm{H}}} + \frac{1}{C_{\mathrm{GC}}}
+\end{equation}
+where \(C_{\mathrm{H}}=\epsilon_{\mathrm{L}}/d_{\mathrm{H}}\) is the
+capacitance of the Helmholtz double layer and
+\(C_{\mathrm{GC}}=\sqrt{\frac{2z^{2}e^{2}\epsilon_{\mathrm{L}}c_{0}N_{\mathrm{A}}}{k_{\mathrm{B}}T}}
+\cosh(\frac{ze\psi_{\mathrm{GC}}}{2k_{\mathrm{B}}T})\) is the
+differential capacitance of the GC layer, with \(\psi_{\mathrm{GC}}\)
+corresponding to the electric potential at the GC interface. Consider
+a Gaussian enclosure including the 2D material layer and the EDL, due
+to a zero net electric field at the surface of the Gaussian enclosure,
+the electroneutrality of the system \cite{bard_electrochemical_1980}
+suggests:
+\begin{equation}
+\label{eqn-neutrality}
+\sigma_{\mathrm{2D}} + \sigma_{\mathrm{L}} = 0
+\end{equation}
+And therefore, the electric potentials corresponding to the surface of
+the 2D material and the outer Helmholtz plane, \(\psi_{\mathrm{2D}}\)
+and \(\psi_{\mathrm{GC}}\), are given by:
+\begin{equation}
+\label{eqn-psi-GC}
 \begin{aligned}
-\Phi_{\mathrm{2D-w}}^{or} &= (\Psi_{\mathrm{2D-w}} - \Psi_{\mathrm{w}} - \Psi_{\mathrm{2D}})\frac{1}{S \cdot N_{\mathrm{A}}} \\
-                     &= \Phi_{\mathrm{LJ}} + \Phi_{\mathrm{CL}}
+  \psi_{\mathrm{GC}} &= -\frac{2k_{\mathrm{B}}T}{ze} 
+                         \sinh^{-1}\left(
+                         \frac{-\sigma_{\mathrm{2D}}}{\sqrt{8c_{0}N_{\mathrm{A}}\epsilon_{\mathrm{L}}k_{\mathrm{B}}T}}
+                            \right) \\
+  \psi_{\mathrm{2D}} &= \psi_{\mathrm{GC}} + \sigma_{\mathrm{2D}}\frac{d_{\mathrm{H}}}{\epsilon_{\mathrm{L}}}
 \end{aligned}
 \end{equation}
-where \(S\) is the area of the graphene sheet (same as the contact area
- between water and graphene), \(N_{\mathrm{A}}\) is the Avogadro's
- number, \(\Psi_{\mathrm{2D-w}}\) is the total internal potential of the
- 2D material-water system, and \(\Psi_{\mathrm{w}}\) and
- \(\Psi_{\mathrm{2D}}\) are the potentials of the separated water phase
- and 2D materials, respectively.  The adhesion energy can be further
- decomposed into the short-range Lenard-Jones potential term
- (\(\Phi_{\mathrm{LJ}}\)) and the long-range Coulombic interaction term
- (\(\Phi_{\mathrm{CL}}\)). Since \(\Psi_{\mathrm{w}}\) and
- \(\Psi_{\mathrm{2D}}\) are unalterable in the MD simulation, the change
- of interfacial adhesion energy \(\Delta \Phi_{\mathrm{2D-w}}^{or}\) as a
- result of surface doping, is calculated as:
+where \(N_{\mathrm{A}}\) is the Avogadro constant and \(k_{\mathrm{B}}\)
+is the Boltzmann constant. Accordingly, the final form
+of \((\Delta \cos \theta)^{\mathrm{EDL}}\) is given by:
 \begin{equation}
-\label{eqn:delta-Phi-2D-or}
+\label{eqn-Delta-cos-EDL-final}
 \begin{aligned}
-\Delta \Phi_{\mathrm{2D}}^{or} &= \frac{\Delta \Phi_{\mathrm{2D-w}}}{S \cdot N_{\mathrm{A}}} \\
-                               &= \Delta \Phi_{\mathrm{LJ}} + \Delta \Phi_{\mathrm{CL}}
+(\Delta \cos \theta)^{\mathrm{EDL}} &= \frac{\sigma_{\mathrm{2D}}^{2}}{2\gamma_{\mathrm{L}}
+                                       C_{\mathrm{H}}}\frac{1}{\gamma_{\mathrm{L}}}
+                                       \sqrt{\frac{32k_{\mathrm{B}}^{3}T^{3} \epsilon_{\mathrm{L}} c_{0} 
+                                       N_{\mathrm{A}}}{z^{2}e^{2}}} 
+                                       \left[\cosh(\frac{z e \psi_{\mathrm{GC}}}{2k_{\mathrm{B}} T}) -1 \right]\\
+                                    &= \frac{\Delta \sigma_{\mathrm{2D}}^{2}}{2\gamma_{\mathrm{L}}}
+                                       \left[ \frac{1}{C_{\mathrm{H}}} + \frac{1}{(C_{\mathrm{DH}} + 
+                                       C_{\mathrm{GC}})/2}\right]
 \end{aligned}
 \end{equation}
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.9\linewidth]{../img/fig-pot-dens.pdf}
-\caption{\label{fig:pot-dens}
-(a) Change of total adhesion energy \(\Delta\Phi_{\mathrm{2D}}^{or}\), contribution of Lenard-Jones interaction \(\Delta\Phi_{\mathrm{LJ}}\) and Coulombic interaction \(\Delta\Phi_{\mathrm{CL}}\), as a function of charge density on graphene.
-(b) Local density of water molecule (\(\rho_{\mathrm{w}}\))  as a function of distance \(z\) from graphene surface.}
-\end{figure}
+where \(C_{\mathrm{DH}}=\epsilon_{\mathrm{L}}/\lambda_{\mathrm{D}}\) is
+the differential capacitance of the diffuse layer using the
+Debye-Hückel approximation \cite{bard_electrochemical_1980}, and
+\(\lambda_{\mathrm{D}}=\sqrt{\frac{\epsilon_{\mathrm{L}}k_{\mathrm{B}}T}{2z^{2}e^{2}c_{0}N_{\mathrm{A}}}}\)
+is the Debye screening length. Compared with the classical YLE,
+\(\Delta \cos \theta =
+-\frac{\sigma^{2}}{2\gamma_{\mathrm{L}}C_{\mathrm{YL}}}\), where
+\(C_{\mathrm{YL}}\) is the equivalent capacitance in YLE, one can show that \(C_{\mathrm{YL}}\)
+is given by:
+\begin{equation}
+\label{eqn-CYL-model}
+\frac{1}{C_{\mathrm{YL}}} = \frac{1}{C_{\mathrm{H}}} + \frac{1}{(C_{\mathrm{DH}} + C_{\mathrm{GC}})/2}
+\end{equation}
 
-The changes of adhesion energy terms \(\Delta
-\Phi_{\mathrm{2D-w}}^{or}\), \(\Delta \Phi_{\mathrm{LJ}}\) and \(\Delta
-\Phi_{\mathrm{CL}}\), as functions of \(\sigma_{\mathrm{2D}}\) , are
-shown in Fig. \ref{fig:pot-dens}(a). It can be seen that the
-contribution from dispersion interaction \(\Delta \Phi_{\mathrm{LJ}}\)
-has a very small magnitude of negative change (less than 2.5 mJ\(\cdot
-\mathrm{m}^{-2}\)) when \(\sigma_{\mathrm{2D}}\) ranges from
--5\(\times10^{13}\) \textasciitilde{} 5\(\times10^{13}\) \(e\cdot \mathrm{cm}^{-2}\). On the
-other hand, we find that \(\Delta \Phi_{\mathrm{CL}}\) contributes
-majorly to \(\Delta \Phi_{\mathrm{2D-w}}^{or}\), indicating the
-electrostatic nature of the doping-induced reorientation of water
-molecules.
-\begin{center}
-\fbox{
-\begin{minipage}[c]{.8\linewidth}
-\textbf{\textsf{\textsc{TODO}}} Validate the statement above
+The above analysis leads to two important observations: (i) If a thin
+contamination layer (usually composed of charge-neutral hydrocarbon
+species \cite{li_effect_2013}) exists between the Helmholtz layer and
+the 2D material surface, the electroneutrality at the interface (eq
+\ref{eqn-neutrality}) still holds, such that \((\Delta \cos
+\theta)^{\mathrm{EDL}}\) remains the same (see eq
+\ref{eqn-Delta-cos-EDL-final}). In other words, despite the recent
+debate about the role of the airborne adsorbates in the contact angle
+measurement on 2D materials
+\cite{li_effect_2013,Kozbial_2015,Xu_2013_withwhat,Chow_2015}, we expect
+that the experimental characterization of the doping-induced contact
+angle change is more robust and reproducible. (ii) As shown in eqs
+\ref{eqn-GCS-capacitance-series} and \ref{eqn-Delta-gamma-2DL-EDL-full},
+the equivalent capacitance in the YLE, \(C_{\mathrm{YL}}\), is not
+identical to the total capacitance in the EDL, \(C_{\mathrm{EDL}}\). We
+notice that the literature in this field (e.g. Refs.
+\citenum{ostrowski_tunable_2014,daub_electrowetting_2007,goniszewski_correlation_2016,ashraf_doping-induced_2016})
+often simply assumed that \(C_{\mathrm{YL}}=C_{\mathrm{DH}}\) in the
+YLE, which significantly overestimates \((\Delta cos
+\theta)^{\mathrm{EDL}}\), when \(\psi_{\mathrm{2D}} \gg
+k_{\mathrm{B}}T/e\) \cite{israelachvili03_inter}, as can be found in heavily-doped 2D materials.
 
-\end{minipage}
-}
-\end{center}
-It is also interesting to find that, unlike its counterpart from
-dispersion interaction, \(\Delta \Phi_{\mathrm{CL}}\) has a asymmetric
-response to \(\sigma_{\mathrm{2D}}\). We further plot the local density
-of water molecules \(\rho_{\mathrm{w}}\), as a function of distance \(z\)
-from the graphene plane, which can be seen in Fig. \ref{fig:pot-dens}(b). We consider
-3 cases where the graphene layer is either charge-neutral, or
-\(\sigma_{\mathrm{2D}}=\pm 0.012\ e/ \mathrm{atom}\), respectively. We
-find that the \(\rho_{\mathrm{w}}\) at the first water layer adjacent to
-graphene (\(z \approx 3.2\ \mathrm{\AA}\)) also responsed asymmetrically with
-\(\sigma_{\mathrm{2D}}\).  When \(\sigma_{\mathrm{2D}}=-0.012\ e/
-\mathrm{atom}\), \(\rho_{\mathrm{w}}\) drops to ca. 80\% of that in the
-electroneutral system, while \(\rho_{\mathrm{w}}\) at
-\(\sigma_{\mathrm{2D}}=0.012\ e/ \mathrm{atom}\) has a 8\% increase in the density compared with the electroneutral system. The change of interfacial water
-density can be ascribed by the polarity of water molecules. When the
-graphene layer is positively charged, the O atom is more favorably
-facing the graphene surface, while H atom is more favorably facing the
-negatively-charged surface.
-\begin{center}
-\fbox{
-\begin{minipage}[c]{.8\linewidth}
-\textbf{\textsf{\textsc{TODO}}} Describe the density change
+Consider the interface formed between graphene and an (1:1) aqueous
+solution, using the parameters of \(d_{\mathrm{H}}=3\) Å
+\cite{mcclendon_thickness_1927}, and \(\gamma_{\mathrm{L}}=72.8\
+\mathrm{mJ}\cdot \mathrm{m}^{-2}\) at \(T=298\) K, the calculated
+\((\Delta \cos \theta)^{\mathrm{EDL}}\) as a function of
+\(\sigma_{\mathrm{2D}}\) is shown in Figure \ref{fig:res-EDL}(b).  Note
+that \(c_{0}=10^{-7}\) mol\(\cdot \mathrm{L}^{-1}\) corresponds to the
+pure water system. We find that the contact angle change is
+stronger in a more diluted electrolyte solution, resulting from an
+increase in Debye screening length \(\lambda_{\mathrm{D}}\), which
+in turn decreases both \(C_{\mathrm{GC}}\) and \(C_{\mathrm{DH}}\). This
+is distinct from the that in the typical electrowetting experiment on
+a dielectric layer, in which \(C_{\mathrm{YL}}\) is governed by the
+capacitance of the dielectric layer, so the contact angle change is
+almost independent of the electrolyte concentration
+\cite{Mugele_2005}. Moreover, within the range of \(\sigma_{\mathrm{2D}}\)
+considered here (\(-4\times10^{13}\) \textasciitilde{} \(4\times10^{13}\ e\cdot
+\mathrm{cm}^{-2}\)), the calculated \((\Delta \cos
+\theta)^{\mathrm{EDL}}\) is always less than 0.06.  In combination with
+the \(\Delta \gamma^{\mathrm{Orien}}_{\mathrm{2D-L}}\) (equivalent to
+\(\Delta \Phi\), see previous section) calculated by the MD simulations,
+the total change of contact angle \((\Delta \cos
+\theta)^{\mathrm{Orien + EDL}}\) due to the doping effect is shown in
+Figure \ref{fig:res-EDL}(c). The MD-calculated \(\Delta \Phi\) as
+a function of \(\sigma_{\mathrm{2D}}\) is fitted by a third-order
+polynomial function (see Supporting Information Figure S3).  We find
+that the reorientation effect is more predominant than the EDL effect,
+therefore the overall change of contact angle is less dependent on the
+solute concentration, compared with Figure \ref{fig:res-EDL}(b).
 
-\end{minipage}
-}
-\end{center}
-\begin{center}
-\fbox{
-\begin{minipage}[c]{.8\linewidth}
-\textbf{\textsf{\textsc{TODO}}} More in-depth discussion?
+Together with the reorientation effect, the calculated \(\Delta \cos
+\theta\) change only reaches 0.06\textasciitilde{}0.08, corresponding to a maximum
+contact angle decrease of 3.5\textasciitilde{}4.5\(^{\circ}\), for
+\(\sigma_{\mathrm{2D}}=\pm1\times10^{13}\ e\cdot \mathrm{cm}^{-2}\),
 
-\end{minipage}
-}
-\end{center}
+which is is a typical range for both the electrostatic gating
+\cite{hong_mechanism_2016} and substrate-induced doping
+\cite{ashraf_doping-induced_2016}. Clearly, the predicted contact angle
+change upon doping is still lower than those observed
+experimentally. In the next section, we discuss the practical
+considerations that may influence a 2D material-coated surface.
 
-It is noteworthy that although the process for investigating the
-magnitude of \(\Delta \Phi_{\mathrm{2D-w}}^{or}\) is similar for other 2D
-materials other than graphene, the result obtained here cannot be
-readily applied to other 2D materials, since the contribution of
-dispersion interaction and electrostatic interaction can be completely
-different \cite{Govind_Rajan_2016,Chow_2015}. Nevertheless, in
-real-world measurements, due to the existence of the contamination
-layer which has a typical thickness ca. 1\textasciitilde{}2 nm, the dispersion
-interactions contributed by surface charge can be nearly completely
-screened out; aqueous electrolytes can also greatly attenuate the
-electric displacement field, compared with the dipole water model used
-in the MD simulations. Therefore we propose that the effect of
-reorientation may not be easily observable in current experimental
-setups.
+\subsection{Practical Considerations}
+\label{sec:org80c83d8}
 
-While the interfacial dispersion interaction vanishes several
-molecules away from the surface, the long range electrostatic
-interaction will cause the aqueous ions to rearrange at a much longer
-length scale, forming an EDL at the interface and decrease the
-interfacial surface tension by the phenomenon known as electrowetting.
-Revisiting Eq. (\ref{eqn:def-adhesion}), we know that the change of
-interfacial tension due to electrostatic interactions, \(\Delta
-\Phi_{\mathrm{2D-w}}^{\mathrm{el}}\), is given by:
+In practice, in order to
+carry out the contact angle measurement, a large-area sheet of 2D
+material is required to cover the surface. Therefore, most of the
+experimental findings are based on the chemical-vapor-deposited (CVD)
+samples, which are inherently polycrystalline with grain boundaries
+and point defects \cite{Banhart_2011_defect}.  In addition, the transfer
+of the ultrathin films onto a solid surface often results in
+nanometer- to micrometer- scale tears and wrinkles. Although our
+analysis has suggested that the charge-neutral polymer residues and
+airborne contaminations do not influence \((\Delta
+\theta)^{\mathrm{EDL}}\), here we show that the defect density plays an
+important role in determining the wettability of doped 2D
+materials.
 
+Figures \ref{fig:f-nc-exp}(a) and \ref{fig:f-nc-exp}(b) illustrate how an
+ electric field, either from the dopants on the substrate surface or
+ from the electrostatic gating, penetrate through a void in a 2D
+ material sheet and interact with the liquid phase directly. As a
+ result, the EDL is built up adjacent to the substrate surface, with
+ the surface excess \(\sigma_{\mathrm{v}}\) and the effective
+ capacitance \(C_{\mathrm{v}}\).  Since \(\sigma_{v}\) is equivalent to
+ \(\sigma_{\mathrm{2D}}\), together with the EDL and the reorientation
+ effects discussed earlier, the modified YLE considering a 2D material
+ with voids follows:
 \begin{equation}
-\label{eqn:Delta-Phi-el-def}
-\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}} = \Delta \gamma_{\mathrm{2D-w}}^{\mathrm{el}}
-                                           -\Delta \gamma_{\mathrm{2D}}^{\mathrm{el}}
-                                           -\Delta \gamma_{\mathrm{w}}^{\mathrm{el}}
+\label{eqn-def-Delta-cos-mixture}
+\Delta \cos \theta = -f\frac{\sigma_{\mathrm{2D}}^{2}}{\gamma_{\mathrm{L}} C_{\mathrm{v}}} 
+                     + (1-f)[(\Delta \cos \theta)^{\mathrm{Orien}} + (\Delta \cos \theta)^{\mathrm{EDL}}]
 \end{equation}
-where \(\Delta \gamma_{\mathrm{2D-w}}^{\mathrm{el}}\), \(\Delta
-\gamma_{\mathrm{2D}}^{\mathrm{el}}\) and \(\Delta
-\gamma_{\mathrm{w}}^{\mathrm{el}}\) denote the change of surface
-tension of 2D material-water interface, 2D material-air and
-water-air, respectively. In the continuum model, all the changes of
-surface tensions can be modeled by surface excesses. From the
-isothermal 2D Gibbs-Duhem equation we can calculate the change of surface
-energy \(\mathrm{d} \gamma\):
+where \(f\) is the void (defect) fraction in the 2D material. For the
+electrostatic gating experiments (see Figure
+\ref{fig:f-nc-exp}(a)), the 2D material quantum capacitor
+and the dielectric  capacitor are connected in
+series, so that the voltage applied between the gate electrode and
+2D material, \(V_{\mathrm{G}}\), is given by \cite{tian_multiscale_2016}:
+\begin{equation}
+\label{eqn-VG-gating}
+V_{\mathrm{G}} = \frac{\sigma_{\mathrm{2D}} - \sigma_{\mathrm{0}}}{C_{\mathrm{d}}}
+                  + \int_{\sigma_{0}}^{\sigma_{\mathrm{2D}}} \frac{1}{C_{\mathrm{2D}}} \mathrm{d}\sigma'
+\end{equation}
+where \(C_{\mathrm{d}}\) is the capacitance of the dielectric layer, and
+\(\sigma_{0}\) is the initial doping density of the 2D material,
+corresponding to \(V_{\mathrm{G}}=0\).
 
+Next, in order to examine the effect of incomplete 2D material
+coverage, two independent sets of experimental results, which measure
+the water contact angle on (i) substrate-doped graphene
+\cite{ashraf_doping-induced_2016} and (ii) electrostatically-gated
+graphene \cite{hong_mechanism_2016} are chosen to compare, with
+\(C_{\mathrm{v}} = C_{\mathrm{DH}}\) and \(C_{\mathrm{v}} =
+C_{\mathrm{d}}\) in eq \ref{eqn-def-Delta-cos-mixture}, respectively. The
+parameter \(f\) and \(\sigma_{0}\) are determined by least-square fitting
+the experimentally-observed \(\Delta \cos \theta\) with respect to
+\(\sigma_{\mathrm{2D}}\) using eq \ref{eqn-def-Delta-cos-mixture}. Figure
+\ref{fig:f-nc-exp}(c) compares the calculated \(\Delta \cos \theta\) as a
+function of \(\sigma_{\mathrm{2D}}\), together with the two sets of
+experimental data. In both cases considered, we observe a slight
+degree of shift in the minima of the fitted curves, corresponding to
+the CNP of graphene, or \(\sigma_{\mathrm{2D}} = 0\). In other words, we
+observe \(\sigma_{0} \neq 0\) in both cases, which is typical for
+CVD-grown graphene samples
+\cite{Shih2015PartiallyScreened,goniszewski_correlation_2016}.  The
+fitted values of \(f\) are reasonably small (3.6\% for the
+electrostatically-gated graphene and 3.0\% for substrate-doped
+graphene), clearly demonstrating that the contact angle change can be
+greatly influenced by the defect density. We believe this explains the
+discrepancy between the experimental observations and the multiscale
+theoretical framework proposed here.
+
+Finally, we discuss the influence of 2D material choice under
+electrostatic gating condition. The above analysis (eq
+\ref{eqn-Delta-cos-EDL-final}) has clearly suggested that the contact
+angle change effect \((\Delta \cos \theta)^{\mathrm{EDL}}\) only depends
+on \(\sigma_{\mathrm{2D}}\), which can be controlled by an electric
+displacement field, with the experimental setup shown in Figure
+\ref{fig:dcos-all-2D}(a). Specifically,  eqs \ref{eqn-psi-GC} and
+\ref{eqn-VG-gating} suggest:
 \begin{equation}
-\label{eqn:iso-gibbs-duhem}
-\displaystyle
-\mathrm{d}\gamma = -\frac{\sum_{\mathrm{i}} n_{\mathrm{i}}^{\mathrm{ex}}}{A} \mathrm{d} \mu_{\mathrm{i}} 
-                 = -\sum_{\mathrm{i}} \Gamma_{i} \mathrm{d} \mu_{\mathrm{i}}
-\end{equation}
-where \(n_{\mathrm{i}}^{\mathrm{ex}}\) is the surface excess amount of
-specie i, \(A\) is the unit are of the surface, \(\Gamma_{\mathrm{i}}\) is
-the surface excess concentration of specie i, and \(\mu_{\mathrm{i}}\)
-is the chemical potential of specie i. Eq. (\ref{eqn:iso-gibbs-duhem})
-indicates that: both the charges accumulated on the 2D material
-surface and the formation of electric double layer will alter the
-interfacial tension of 2D materials. As far as we are concerned, the
-effect of charge-induced surface tension change of 2D materials has
-rarely been addressed previously. For a charged 2D material surface in
-air, the decrease of surface tension equals the work required to
-charge the isolated 2D material:
-
-\begin{equation}
-\label{eqn:dgamma-QC}
+\label{eqn-dVG-choice-2D}
 \begin{aligned}
-\mathrm{d} \gamma_{\mathrm{2D}}^{\mathrm{el}} &= -\Gamma_{e} \mathrm{d} E_{\mathrm{F}} \\
-                                              &= -\frac{\sigma_{\mathrm{2D}}}{C_{\mathrm{2D}}} \mathrm{d}\sigma_{\mathrm{2D}}
+\mathrm{d} V_{\mathrm{G}} &= (\frac{1}{C_{\mathrm{d}}} + \frac{1}{C_{\mathrm{2D}}}) \mathrm{d} \sigma_{\mathrm{2D}} \\
+\mathrm{d} \psi_{\mathrm{2D}} &= -(\frac{1}{C_{\mathrm{H}}} + \frac{1}{C_{\mathrm{GC}}}) \mathrm{d} \sigma_{\mathrm{L}}
 \end{aligned}
 \end{equation}
-where \(E_{\mathrm{F}}=\mu_{e}\) is the Fermi level of the 2D material
-(equals the chemical potential of electrons in the 2D materials) and
-\(C_{\mathrm{2D}}\) is the quantum capacitance of the 2D material, which
-is proportional to the density of states (DOS) \(g(E_{\mathrm{F}})\) at
-Fermi level \(E_{\mathrm{F}}\):
-\(C_{\mathrm{2D}}=g(E_{\mathrm{F}})e^{2}\). Due to the fact that most 2D
-materials possess quantum capacitances essentially smaller than those
-of bulk materials, one would expect that the charge-induced-decrease
-of surface tension of 2D materials is more prominent than bulk
-materials. Here we demonstrate the degree of charge-induced
-surface tension decrease of several typical 2D materials in
-air. The selected 2D materials are graphene, silicene (2D allotrope
-of Si), germanene (2D allotrope of Ge), MoS\(_{\text{2}}\), MoTe\(_{\text{2}}\), WS\(_{\text{2}}\) and
-WTe\(_{\text{2}}\), respectively. Their DOS as functions of \(E_{\mathrm{F}}\) have been previously
-reported by density functional theory (DFT) calculation, based on the
-HSE06 hybrid functional approach \cite{tian_multiscale_2016}. The
-charge-induced decrease of surface tension of the 2D materials
-\(\Delta \gamma_{\mathrm{2D}}^{\mathrm{el}}\), as a function of the
-surface charge density \(\sigma_{\mathrm{2D}}\), is shown in Fig. \ref{fig:dgamma-sigma}.
+And since \(\sigma_{\mathrm{2D}} = -\sigma_{\mathrm{L}}\), the first
+derivative of \(\psi_{\mathrm{2D}}\) with respect to \(V_{\mathrm{G}}\), namely \(\beta\), is given by:
+\begin{equation}
+\label{eqn-def-beta}
+\beta = \frac{\mathrm{d} \psi_{\mathrm{2D}}}{\mathrm{d} V_{\mathrm{G}}} 
+      = \frac{\frac{1}{C_{\mathrm{H}}} + \frac{1}{C_{\mathrm{GC}}}}{\frac{1}{C_{\mathrm{d}}} + \frac{1}{C_{\mathrm{2D}}}}
+\end{equation}
+The index \(\beta\) here quantifies the tunability of the contact angle change
+by \(V_{\mathrm{G}}\). Accordingly, a high degree of \(\beta\) can be attained by increasing both \(C_{\mathrm{d}}\) and
+\(C_{\mathrm{2D}}\), thereby introducing the dependence on the choice of 2D material.
+
+Here we demonstrate such phenomenon by considering an electrowetting
+setup comprised of a thin, high-\(k\) dielectric layer (2 nm HfO\(_{\text{2}}\)
+layer with the relative permittivity \(\epsilon_{\mathrm{d}}=24.0\))
+underlying a layer of monolayer 2D material (Figure
+\ref{fig:dcos-all-2D}(a)).  As addressed earlier, due to the fact that
+\((\Delta \cos \theta)^{\mathrm{Orien}}\) of graphene-water system may
+not be readily applied to other 2D materials, we compare the
+calculated \((\Delta \cos \theta)^{\mathrm{EDL}}\) as a function of
+\(V_{\mathrm{G}}\), by using the DFT-calculated \(C_{\mathrm{2D}} -
+\sigma_{\mathrm{2D}}\) relations for a variety of 2D materials, as
+shown in \ref{fig:dcos-all-2D}(b). Clearly, as a consequence of the high
+quantum capacitance, the wettability of the 2D semiconductors
+considered is more tunable compared to that for the 2D semimetals. In
+other words, in a 2D semiconductor, the value required to reach a
+certain is lowered. We predict that the contact angle change \(\Delta \cos \theta\) for
+the 2D semiconductors (e.g. TMDCs) can reach up to 0.22\textasciitilde{}0.25 within the range of
+\(V_{\mathrm{G}}\) considered, corresponding to an interfacial tension change of 15\textasciitilde{}18 \(\mathrm{mJ} \cdot \mathrm{m}^{-2}\).
+The analysis presented here suggests that the manipulation of a liquid
+droplet on a layer of 2D material doped by an electric displacement field may be feasible
+\cite{Mugele_2005,Hayes_2003_nature_EWOD}.
+
+An interesting implication is that, together with the recent
+development in engineering 2D materials’ wetting translucency
+\cite{raj_wettability_2013,rafiee_wetting_2012,shih_breakdown_2012,shih_wetting_2013},
+in principle, upon doping, a 2D material becomes less “transparent” (or more screening)
+to both van der Waals and Coulombic interactions exerted from the underlying
+substrate, due to enhanced liquid-2D material interactions. That is to say, the doping level can be
+another control variable to modulate the molecular packing and
+epitaxial behavior on a 2D material-coated surface, which may bring
+new technology opportunity for a variety of applications.
+
+\section{Conclusion}
+\label{sec:org333a0f3}
+
+In conclusion, we present a multiscale theoretical framework
+concerning the wettability of doped 2D materials, by considering: (i)
+the change of 2D materials surface energy, (ii) the molecular
+reorientation of liquid molecules adjacent to the interface, and (iii)
+the electrical double layer formed in the liquid phase. Taking
+graphene as an example, we show that the Coulombic interaction
+dominates the change of liquid-2D material interfacial tension, at
+both atomistic and continuum length scales.The latter two effects were
+found to be the major mechanisms responsible for the water contact angle
+change at the 2D material interfaces upon doping.
+
+The doping-induced reorientation of liquid molecules at the
+graphene-liquid interface is revealed by MD simulations, which also
+allow decoupling of vdW and Coulombic energy contributions to the
+interfacial tension in the absence of electrolytes in liquid. It is
+found that the interfacial energy change is dominated by the Coulombic
+interactions. Our results also reveal an asymmetric change of
+graphene-water interfacial energy upon doping, such that slightly
+n-doped graphene can reorient interfacial water molecules to minimize
+electrostatic attractions, and therefore, slightly increase the
+interfacial energy.
+
+On the hand, the EDL effect is calculated by a continuum model. Our
+analysis suggests that the reorientation effect is more predominant
+than the EDL effect, On the graphene-water interface, we predict that
+the combined reorientation and EDL effects can induce a significant
+change of the interfacial tension \(\Delta
+\gamma_{\mathrm{2D-L}}\), up to -15\textasciitilde{}-20 \(\mathrm{mJ}\cdot
+\mathrm{m}^{-2}\), at the doping level of \(\pm 4 \times 10^{13}\ e\cdot
+\mathrm{cm}^{-2}\). By adding the fitting parameter concerning the
+defect density, our theoretical framework can nicely describe the
+experimentally observed doping-induced contact angle change. Finally,
+based on the DFT-calculated quantum capacitances (QCs) for a variety
+of 2D materials, we predict that the wettability of 2D semiconductors
+(e.g., TMDCs) is more tunable under an electric displacement field,
+compared with 2D semimetals (e.g. graphene) due to their high quantum
+capacitances. Our findings reveal a complete picture for the
+modulation of the molecular interactions between liquid and a 2D monolayer upon
+doping. The multiscale theoretical
+framework proposed here is expected to shed
+light on the surface science of 2D materials, 
+as well as to provide a quantitative estimation for the wettability
+of the doped 2D materials. We hope that the development for the 2D
+materials-based functional surfaces in liquid manipulation, energy
+harvesting, and molecular epitaxy will be facilitated by the
+fundamental principles and theoretical insights presented here.
+
+\bibliography{ref}
+
+\newpage{}
+\section{Figures}
+\label{sec:org0a7d2b4}
+
 \begin{figure}[htbp]
@@
 \caption{\label{fig:dgamma-sigma}
-\(\Delta \gamma_{\mathrm{2D}}^{\mathrm{el}}\) as a function of \(\sigma_{\mathrm{2D}}\) for several 2D materials: graphene, silicene, germanene, MoS\(_{2}\), MoTe\(_{2}\), WS\(_{2}\) and WTe\(_{2}\)}
+\(\Delta \gamma_{\mathrm{2D}}\) as a function of \(\sigma_{\mathrm{2D}}\) for selected 2D materials: graphene, silicene, germanene, phosphorene, MoS\(_{2}\), MoSe\(_{2}\), MoTe\(_{2}\), WS\(_{2}\), WSe\(_{2}\) and WTe\(_{2}\)}
 \end{figure}
-It can be observed from our calculations that graphene has the largest
-degree of surface tension decrease (ca. 22 mJ\(\cdot\mathrm{m}^{-2}\)
-when \(\sigma_{\mathrm{2D}}=\pm5\times10^{13}\ e\cdot
-\mathrm{cm}^{-2}\)), due to the fact that graphene has the lowest
-\(C_{\mathrm{2D}}\) among the selected 2D materials
-\cite{tian_multiscale_2016}. We can rationalize the \(\Delta
-\gamma_{\mathrm{2D}}^{\mathrm{el}}\) - \(\sigma_{\mathrm{2D}}\) relation
-of the 2D materials by their \(C_{\mathrm{2D}}\) values: the 2D
-semimetals (graphene, silicene and germanene) generally have larger
-decrease of surface tension, compared with the semiconducting 2D TMDCs
-at same doping level, due to the limited DOS dispersion in 2D
-semimetals. Notably, the results indicate that a significant decrease
-of surface tension of 2D materials (at the order of 10 mJ\(\cdot
-\mathrm{m}^{-2}\)) can be achieved with a doping at the order of
-\(10^{13}\ e\cdot \mathrm{cm}^{-2}\), and may eventually be experimentally
-observed.
-
-Similarly, \(\Delta \gamma_{\mathrm{2D-w}}^{\mathrm{el}}\) is
-contributed by both the 2D surface charge and the charge accumulation
-in the EDL:
-
-\begin{equation}
-\label{eqn:dgamma-2D-w}
-\mathrm{d}\gamma_{\mathrm{2D-w}}^{\mathrm{el}} = -\frac{\sigma_{\mathrm{2D}}}{e} \mathrm{d}E_{\mathrm{F}}
--\sum_{\mathrm{i}} z_{\mathrm{i}}e\Gamma_{\mathrm{i}}^{\mathrm{s}} \mathrm{d}\psi_{\mathrm{2D}}
-\end{equation}
-where \(\Gamma_{\mathrm{i}}^{\mathrm{s}}\) and \(z_{\mathrm{i}}\) are the
-surface excess concentration and valency of ionic solute i,
-respectively; \(\psi_{\mathrm{2D}}\) is the electrostatic potential at the 2D
-material-water interface. On the other hand \(\gamma_{\mathrm{w}}\) is
-independent of the surface charge of the 2D material, since no surface
-excess is present at the water-air interface. We therefore derive
-the expression for \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}\) as
-follows:
-
-\begin{equation}
-\label{eqn:Delta-Phi-final}
-\begin{aligned}
-\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}} &= -\frac{\sigma_{\mathrm{2D}}}{e}dE_{\mathrm{F}} 
-                                             -\sum_{\mathrm{i}} z_{\mathrm{i}}e\Gamma_{\mathrm{i}}^{\mathrm{s}} \mathrm{d}\psi_{\mathrm{2D}}
-                                             +\frac{\sigma_{\mathrm{2D}}}{e}dE_{\mathrm{F}} \\
-                                          &= -\sigma_{\mathrm{L}} \mathrm{d}\psi_{\mathrm{2D}}
-\end{aligned}
-\end{equation}
-where \(\sigma_{\mathrm{L}}\) is the total charge density in the EDL. As
-the accumulation of charge on the 2D material surface occurs both on
-the 2D material-air and 2D material-water interfaces, their
-contributions to the surface tension is canceled out. As a result
-\(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}\) is governed by the ion
-accumulation in EDL alone, in consistent with the trivial
-electrowetting theory (constant solid surface tension). However, the
-absolute values of \(\gamma_{\mathrm{2D-w}}\) and \(\gamma_{\mathrm{2D}}\)
-do change due to the aforementioned phenomenon.
-
-To evaluate the effect of electrowetting, we first
-consider that a contamination layer with thickness \(d_{\mathrm{c}}\)
-covers the 2D material surface. Since the airborne contaminants are
-mostly hydrocarbon compounds, they can be treated as a dielectric
-layer with permittivity \(\epsilon_{\mathrm{c}}\). We use the
-Gouy-Chapman-Stern model to describe the EDL in the aqueous phase,
-which consists a Helmholtz double layer with the same permittivity
-\(\epsilon_{\mathrm{w}}\) as water, and thickness \(d_{\mathrm{H}}\),
-together with a diffuse layer where ionic distribution is described by
-the Gouy-Chapman equation.  The potentials at the surface of the 2D
-material, the contamination layer surface and the outer Helmholtz
-plane (the interface between the Helmholtz double layer and the
-diffuse layer) are \(\psi_{\mathrm{2D}}^{*}\), \(\psi_{\mathrm{2D}}\) and
-\(\psi_{\mathrm{L}}\), respectively. An illustration of the model for the
-2D-material-water interface is shown in Fig. \ref{fig:scheme-EDL}.
 
@@
 \centering
-\includegraphics[width=0.95\linewidth]{../img/scheme-EDL.pdf}
-\caption{\label{fig:scheme-EDL}
-Scheme of the interface between the 2D material and the aqueous phase.
-A electrostatic potential \(\psi_{\mathrm{2D}}\) is built at the interface, as a result of surface charge on 2D material \(\sigma_{\mathrm{2D}}\).}
+\includegraphics[width=0.95\linewidth]{../img/scheme-methods.png}
+\caption{\label{fig:scheme-method}
+Scheme of the multiscale approach for modeling the doping-induced wettability tuning of 2D materials.}
 \end{figure}
-
-If we neglect specific adsorption of ions at the solid-liquid interface,
-electroneutrality ensures that the charge density of the 2D material
-\(\sigma_{\mathrm{2D}}\) balances the total charge density of the EDL
-\(\sigma_{\mathrm{L}}\) \cite{bard_electrochemical_1980}:
-\begin{equation}
-\sigma_{\mathrm{2D}} + \sigma_{\mathrm{L}} = 0
-\end{equation}
-From the Gouy-Chapman model of 1 symmetric electrolyte we know:
-\begin{align}
-\displaystyle
-\label{eqn:psi-L}
-\psi_{\mathrm{L}} &= -\frac{2k_{\mathrm{B}}T}{z_{0}e} 
-                       \sinh^{-1}\left(
-                         \frac{\sigma_{\mathrm{L}}}{\sqrt{8c_{0}N_{\mathrm{A}}\epsilon_{\mathrm{w}}k_{\mathrm{B}}T}}
-                          \right) \\
-\label{eqn:psi-2D}
-\psi_{\mathrm{2D}} &= \psi_{\mathrm{L}} - \sigma_{\mathrm{L}}\frac{d_{\mathrm{H}}}{\epsilon_{\mathrm{w}}} \\
-\psi_{\mathrm{2D}}^{*} &= \psi_{\mathrm{2D}} - \sigma_{\mathrm{L}}\frac{d_{\mathrm{c}}}{\epsilon_{\mathrm{c}}}
-\end{align} 
-where \(z_{0}\) is the valency of the electrolyte, \(c_{0}\) is the
-concentration of the electrolyte, \(N_{\mathrm{A}}\) is the Avogadro
-constant and \(k_{\mathrm{B}}\) is the Boltzmann constant. While the
-contamination layer is responsible for a potential drop across the
-solid phase, the solid-liquid interfacial potential
-\(\psi_{\mathrm{2D}}\) which contributes to the \(\Delta \Phi_{\mathrm{2D-w}}^{el}\), is only governed by \(\sigma_{\mathrm{L}}\). Therefore
-we conclude that the existence of a contamination layer does not affect
-the magnitude of \(\Delta \Phi_{\mathrm{2D-w}}}^{el}\).
-
-The exact solution of \(\Delta
-\Phi_{\mathrm{2D-w}}^{el}\) can be derived from Eqs (\ref{eqn:psi-2D})
-and (\ref{eqn:psi-L}):
-\begin{equation}
-\label{eqn:Delta-Phi-exact}
-\begin{aligned}
-\Delta \Phi_{\mathrm{2D-w}}^{el}
-&= -\int_{0}^{\psi_{\mathrm{2D}}} \sigma_{\mathrm{L}} \mathrm{d}\psi' \\
-&= -\int_{0}^{\sigma_{\mathrm{L}}} \sigma'\left(
-   \frac{1}{C_{\mathrm{H}}} + \frac{1}{C_{\mathrm{L}}}
-                                          \right) \mathrm{d}\sigma' \\
-&= -\frac{\sigma_{\mathrm{L}}^{2}}{2C_{\mathrm{H}}}
-    -\sqrt{\frac{32k_{\mathrm{B}}^{3}T^{3} \epsilon_{\mathrm{w}} c_{0} N_{\mathrm{A}}}{z_{0}^{2}e^{2}}}
-   \left[\cosh(\frac{z_{0}e\psi_{\mathrm{L}}}{2k_{\mathrm{B}}T}) - 1\right] \\
-&= -\frac{\sigma_{\mathrm{L}}^{2}}{2C_{\mathrm{H}}} 
-   - \frac{\sigma_{\mathrm{L}}^{2}}{C_{\mathrm{L}} 
-   + \frac{\epsilon_{w}}{\lambda_{\mathrm{D}}}}
-\end{aligned}
-\end{equation}
-where \(C_{\mathrm{H}}=\epsilon_{w}/d_{\mathrm{H}}\) is the geometric
-capacitance of the Helmholtz double layer,
-\(C_{\mathrm{L}}=\sqrt{\frac{2z_{0}^{2}e^{2}\epsilon_{\mathrm{w}}c_{0}N_{\mathrm{A}}}{k_{\mathrm{B}}T}}
-\cosh (\frac{z_{0}e\psi_{\mathrm{L}}}{2k_{\mathrm{B}}T})\) is the
-capacitance of diffuse layer derived from the Gouy-Chapman equation,
-and
-\(\lambda_{\mathrm{D}}=\sqrt{\frac{\epsilon_{\mathrm{w}}k_{\mathrm{B}}T}{2z^{2}e^{2}c_{0}N_{\mathrm{A}}}}\)
-is the Debye length of the electrolyte. The quantity
-\(\epsilon_{\mathrm{w}}/\lambda_{\mathrm{D}}\) is actually the
-Debye-Hückel-style capacitance of the EDL.
-Eq. (\ref{eqn:Delta-Phi-exact}) shows that \(\Delta
-\Phi_{\mathrm{2D-w}}^{el}\) consists of the contributions from the
-Helmholtz double layer and the diffuse layer, respectively.  Note that
-at room temperature, when \(\sigma_{\mathrm{2D}}\) is large
-(e.g. \(10^{13}\) \(e\cdot \mathrm{cm}^{-2}\)) and \(c_{0}\) is small
-(e.g. \(10^{-7}\) mol\(\cdot \mathrm{L}^{-1}\)),
-\(\psi_{\mathrm{L}}\)=347 mV
-, which is much larger than \(k_{\mathrm{B}}T/e\), causing a significant
-discrepancy between the Gouy-Chapman capacitance \(C_{\mathrm{L}}\) and
-the Debye-Hückel capacitance
-\(\epsilon_{\mathrm{w}}/\lambda_{\mathrm{D}}\). This effect is often
-ignored in previous studies concerning the electrowetting on graphene
-and other 2D materials
-\cite{ostrowski_tunable_2014,daub_electrowetting_2007,goniszewski_correlation_2016,ashraf_doping-induced_2016},
-and the classical Young-Lippman equation \(\Delta
-\gamma=-\frac{1}{2}C\psi^{2}\) (or \(\Delta
-\gamma=-\frac{\sigma^{2}}{2C}\)) is casually used instead, assuming the
-capacitance to be constant.
-Since most of the reported samples deals with pure water with extremely low \(c_{0}\), the Debye-Hückel capacitance is much smaller than the Gouy-Chapman capacitance, leading to an overestimation of \(\Delta\cos\theta\).
-Therefore our
-derivation in Eq. \ref{eqn:Delta-Phi-exact} provides a more accurate
-approach to analyze \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}\) as a function of \(\sigma_{\mathrm{2D}}\).
 
@@
 \centering
-\includegraphics[width=0.85\linewidth]{../img/2d-ph-dependency.pdf}
-\caption{\label{fig:Delta-cos-dependency}
-(a) \(\Delta\cos\theta\) as a function of \(\sigma_{\mathrm{2D}}\).The concentration varies from \(10^{0}\) to \(10^{-7}\) mol\(\cdot\mathrm{L}^{-1}\) (b) \(\Delta\theta\) as a function of \(\sigma_{\mathrm{2D}}\) and the hypothetical contact angle on a charge-neutral 2D material layer \(\theta^{*}\).
-c\(_{\text{0}}\) is taken as \(10^{-7}\) mol\(\cdot\mathrm{L}^{-1}\).}
+\includegraphics[width=0.9\linewidth]{../img/fig-pot-dens.pdf}
+\caption{\label{fig:MD-res}
+Geometry of the periodic MD simulation box for (a) water molecules only and (b) water-graphene systems.(c) Change of total adhesion energy \(\Delta\Phi\), and its partial contributionsfrom Lennard-Jones interaction \(\Delta\Phi_{\mathrm{LJ}}\) and Coulombic interaction \(\Delta\Phi_{\mathrm{CL}}\), as a function of \(\sigma_{\mathrm{2D}}\).
+10\(^{\text{-3}}\) \$e\$/atom corresponds to a charge density of \(3.80 \times 10^{12}\ e \cdot \mathrm{cm}^{-2}\).
+(d) Local density \(\rho_{\mathrm{L}}\) (e) local charge density \(\delta_{\mathrm{L}}\) of water molecules as a function of distance \(z\) from graphene surface.}
 \end{figure}
-
-Consider that the aqueous phase contains a 1:1 electrolyte with
-concentration \(c_{0}\), the thickness of the Helmholtz plane
-\(d_{\mathrm{H}}=3\ \mathrm{\AA}\) \cite{mcclendon_thickness_1927}, and
-the surface tension of water \(\gamma_{\mathrm{w}}=72.8\) mJ\(\cdot
-\mathrm{m}^{-2}\) at \(T=298\) K, we calculate the magnitude of
-\(\Delta\Phi_{\mathrm{2D-w}}^{el}\) and \(\Delta\cos\theta\) as function
-of \(\sigma_{\mathrm{2D}}\), as shown in
-Fig. \ref{fig:Delta-cos-dependency}(a). We discover that both the
-changes in the magnitude of interfacial adhesion energy and the
-contact angle become more pronounced when the concentration of
-electrolyte is lower. On the contrary, in conventional electrowetting
-model, \(\Delta\theta\) is governed by the constant capacitance of the
-dielectric layer and is almost irrelevant to the \(c_{0}\). The results indicate that the variation of \(c_{0}\) has a significant impact on \(\Delta
-\Phi_{\mathrm{2D-w}}^{el}\) and \(\Delta \cos \theta\) in the
-electrowetting on doped 2D materials. This is due to the fact that the
-interfacial potential \(\psi_{\mathrm{2D}}\) is affected by both the
-surface charge \(\sigma_{\mathrm{2D}}\) and \(c_{0}\), as indicated by
-Eq. (\ref{eqn:psi-L}) and (\ref{eqn:psi-2D}). When \(c_{0}\) is lower, a
-larger potential is required to be built upon the interface, giving
-rise to a larger change in the interfacial wetting property.
-
-Although the ``real'' contact angle of a 2D material can be tedious to
-determine, it is still possible to estimate the magnitude of contact
-angle change due to the electrowetting effect, by assuming that the
-hypothetical contact angle \(\theta^{*}\) on a charge-neutral 2D
-material layer. \(\theta^{*}\) consists of the effect of intrinsic
-wettability, surface contamination as well the wetting translucency of
-the 2D material-liquid interface. Fig. \ref{fig:Delta-cos-dependency}(b)
-shows the magnitude of contact angle decrease as a function of both
-\(\sigma_{\mathrm{2D}}\) and \(\theta^{*}\), when \(c_{0}=10^{-7}\)
-mol\(\cdot \mathrm{L}^{-1}\) (e.g. ideally pure water). Within the range
-of typical contact angles reported on graphene (ca. 40\(^{\circ}\) \textasciitilde{}
-100\(^{\circ}\)), and a doping level of \(-5\times10^{13}\) \textasciitilde{}
-\(5\times10^{13}\) \(e \cdot \mathrm{cm}^{-2}\), we find that the maximum
-magnitude \(\Delta\theta\) is only ca. 7\(^{\circ}\) when doping level is
-as high as \(\pm 5 \times 10^{13}\) \(e\cdot \mathrm{cm}^{-2}\),
-essentially smaller than previously reported values which were
-measured both under smaller doping levels
-\cite{hong_mechanism_2016,ashraf_doping-induced_2016}.  Due to the
-saturation of CO\(_{\text{2}}\) in water and soluble contaminants, the effect of
-electrowetting may be even less prominent in real
-situations. Therefore we believe that the electrowetting effect theory
-on 2D materials alone, cannot explain the current findings of
-doping-induced wettability change on graphene.
-
-Practically in a contact angle measurement, the amount of water varies
-from pL (using environmental scanning electron microscopy, ESEM) to
-\(\mathrm{\mu L}\) (using goniometer). Unlike nanodroplet models used in
-MD contact angle simulations, the droplets used experimentally are
-large enough to be exposed to both pristine and defect 2D surface, and
-can therefore be trapped in the local minimal state caused by nanoscale
-defects \cite{raj_wettability_2013}, giving rise to uncertainty of the
-measured contact angle. Meanwhile, it is widely observed that
-nanopores and macroscopic cracks exist in the transferred 2D material,
-increasing the adhesion interaction between the substrate and the
-water droplet.
 
@@
 \centering
-\includegraphics[width=0.95\linewidth]{../img/scheme-crack.pdf}
-\caption{\label{fig:scheme-crack}
-Schematic drawing of the incomplete surface coverage in (a) substrate doping and (b) electrostatic doping systems.
-In both cases the aqueous phase is exposed directly to the substrate, leading to a discrepancy of apparent wetting properties compared with theoretical values.}
+\includegraphics[width=0.5\linewidth]{../img/2d-ph-dependency+MD.pdf}
+\caption{\label{fig:res-EDL}
+(a) Scheme of the interface between the 2D material and the aqueous phase.
+(b) \((\Delta\cos\theta)^{\mathrm{EDL}}\) as a function of \(\sigma_{\mathrm{2D}}\) with varied solute concentrations.
+The concentration \(c_{0}\) varies from \(10^{0}\) to \(10^{-7}\) mol\(\cdot\mathrm{L}^{-1}\) (c) Overall change of contact angle \((\Delta \cos \theta)^{\mathrm{Orien+EDL}}\) combining the orientation and EDL effects, with varied solute concentrations as in (b).}
 \end{figure}
-
-We further consider the cases where the 2D material does not
-completely cover the substrate. In both the substrate-induced doping
-(see Fig. \ref{fig:scheme-crack}(a)) and the electrostatic doping (see
-Fig. \ref{fig:scheme-crack}(b)) systems, substrate surface charge still
-exists in non-covered regions: in surface doping the charged dopants
-(i.e. polyelectrolytes) will instantly build up a EDL near the
-substrate surface, while in electrostatic doping the electric
-displacement field still forms between the conducting 2D material and
-the gate electrode via the non-covered region, also causing the ions
-to accumulate at the substrate-water interface. The interfacial
-adsorption density of ions can essentially be larger than the surface
-charge density on 2D material, due to the partial screening of
-electric displacement field of the 2D material
-\cite{tian_multiscale_2016,Shih2015PartiallyScreened,Muruganathan_2015,Huttmann_2015}. Since
-the electrowetting effect is amphipolar, the accumulation of cations
-and anions at the 2D material surface or the non-covered region
-both contribute to the decrease of the apparent surface tension
-\(\hat{\gamma}_{\mathrm{2D-w}}\). We assume that the electrowetting at
-the non-covered region is described by the classical Young-Lippman
-\(\Delta
-\gamma_{\mathrm{nc}}=-\frac{\sigma_{\mathrm{2D}}^{2}}{2C_{\mathrm{nc}}}\),
-where \(C_{\mathrm{nc}}\) is the effective capacitance of the
-non-covered region (taken as the EDL capacitance in substrate doping,
-or the geometric capacitance of dielectric layer in electrostatic
-doping). We therefore describe \(\Delta
-\hat{\gamma}_{\mathrm{2D-w}}\) as a combined effect of the
-electrowetting on both pristine 2D material surface and non-covered substrate surface,
-characterized by the surface coverage index \(f\):
-\begin{equation}
-\label{eqn:apparent-gamma-combined}
-\begin{aligned}
-\Delta \hat{\gamma}_{\mathrm{2D-w}} &= f \Delta \gamma_{\mathrm{2D-w}} + (1-f)\Delta \gamma_{\mathrm{nc}} \\
-&= f \Delta \gamma_{\mathrm{2D-w}}  -\frac{1}{2}(1-f)\frac{\sigma_{\mathrm{2D}}^{2}}{C_{\mathrm{nc}}}
-\end{aligned}
-\end{equation}
-
-It should also be noted that in electrowetting experiments
-where additional charge is doped to the 2D material via dielectric
-layer \cite{hong_mechanism_2016}, the initial doping density
-\(\sigma_{\mathrm{i}}\) should also be considered to explain the
-asymmetric electrowetting behavior. In an electrowetting system where a
-dielectric layer with geometric capacitance \(C_{\mathrm{d}}\) and external
-voltage \(V_{\mathrm{2D}}\) is applied to the 2D material, the doping
-density in the 2D material is calculated as \cite{tian_multiscale_2016}:
-\begin{equation}
-\label{eqn:doping-vm-2D}
-V_{\mathrm{2D}} = \frac{\sigma_{\mathrm{2D}} - \sigma_{\mathrm{i}}} {C_{\mathrm{d}}} 
-                 + \int_{\sigma_{\mathrm{i}}}^{\sigma_{\mathrm{2D}}} 
-                   \frac{1}{C_{\mathrm{2D}}} \mathrm{d}\sigma'
-\end{equation}
 
@@
 \caption{\label{fig:f-nc-exp}
-Theoretical and fitted experimental data of \(\Delta\cos\theta\) as a function of \(\sigma_{\mathrm{2D}}\).
+Schemes of the void region in (a) substrated doped 2D material and (b) electrostatic gated 2D material.(c) Fitted experimental data of \(\Delta\cos\theta\) as a function of \(\sigma_{\mathrm{2D}}\).
 The electrowetting data are extracted from Ref.
-\cite{hong_mechanism_2016}; the ESEM data are extracted from Ref.
-\cite{ashraf_doping-induced_2016}.}
+\citenum{hong_mechanism_2016}; the ESEM data are extracted from Ref.
+\citenum{ashraf_doping-induced_2016}.}
 \end{figure}
 
-To examine the effect of incomplete 2D material coverage, we select
-two sets of reported experimental measurements of the wettability on
-doped graphene sheet, namely the contact angles of substrate-doped
-graphene measured by ESEM from Ref. \cite{ashraf_doping-induced_2016}
-and the contact angles of electostatically-doped graphene via
-goniometer from Ref. \cite{hong_mechanism_2016}. The contact angle at
-experimentally ``charge-neutral'' condition (graphene attached to SiO\(_{\text{2}}\)
-substrate for ESEM experiment or \(V_{\mathrm{2D}}=0\) V in
-electrowetting experiment, however \(\sigma_{\mathrm{2D}}\) may not be 0
-due to existence of \(\sigma_{\mathrm{i}}\)) is used as reference for
-calculating \(\mathrm{d}\cos\theta\). We use
-Eq. \ref{eqn:apparent-gamma-combined} to extract \(f\) and
-\(\sigma_{\mathrm{i}}\) for both experiments, as seen in
-Fig. \ref{fig:f-nc-exp}. We observe that in both experimental data sets,
-the measured \(\Delta \cos \theta\) is essential larger than the
-theoretical value derived from the Gouy-Chapman-Stern model described
-here. Fitting results reveals both systems are lightly p-doped in the
-``charge-neutral'' condition, which corresponds well with other
-experimental reports
-\cite{Shih2015PartiallyScreened,goniszewski_correlation_2016}.  The
-fitted \(f\) values for both systems are as small as 3.7\%-3.8\%,
-indicating the graphene layers are mostly complete. It is very
-surprising to find out that due to large discrepancy of wetting
-behavior on the 2D material and the underlying substrate, the measured
-contact angle change can be greatly influenced by the existence of
-minor defects in the 2D material. Our calculations show that extreme
-care should be taken to interpret the true doping-tunable wetting
-behavior of 2D materials.
-
-The doping-induced tuning of wetting on 2D materials opens a novel
-avenue for 2D-material-based liquid manipulating devices. Unlike
-conventional electrowetting on dielectric (EWOD) setup, no counter
-electrode is required in the liquid phase, ensuring simpler device
-design. Although Eq. \ref{eqn:Delta-Phi-exact} shows that the
-electrowetting effect of 2D material is only dependent on the surface
-charge \(\sigma_{\mathrm{2D}}\), practically it is more favorable to
-achieve the desired electrowetting by applying a smaller
-\(V_{\mathrm{2D}}\). A usual setup for electrostatic doping of 2D
-material involves the use of high-k dielectric or ionic gating
-\cite{Das_2008,Radisavljevic_2011,Xu_2011,Newaz_2012}, where the
-\(C_{\mathrm{d}}\) is comparable with \(C_{\mathrm{2D}}\). Therefore the
-contribution of \(C_{\mathrm{2D}}\) in Eq. \ref{eqn:doping-vm-2D} cannot
-be ignored. Combing Eqs. \ref{eqn:psi-L}, \ref{eqn:psi-2D} and
-\ref{eqn:doping-vm-2D}, we get:
-
-\begin{align}
-\label{eqn:dV-sigma-2D}
-\mathrm{d} V_{\mathrm{2D}} &= \left(\frac{1}{C_{\mathrm{d}}} +
-\frac{1}{C_{\mathrm{2D}}}\right) \mathrm{d}\sigma_{\mathrm{2D}} \\
-\label{eqn:dpsi-sigma-L}
-\mathrm{d} \psi_{\mathrm{2D}} &= -\left( \frac{1}{C_{\mathrm{H}}}
-+ \frac{1}{C_{\mathrm{L}}} \right) \mathrm{d}\sigma_{\mathrm{L}}
-\end{align}
-and by substituting \(\sigma_{\mathrm{2D}} = -\sigma_{\mathrm{L}}\), we derive the ratio between \(\psi_{\mathrm{2D}}\) and \(V_{\mathrm{2D}}\), named as \(\beta\):
-\begin{equation}
-\label{eqn:beta}
-\beta = \frac{\mathrm{d} \psi_{\mathrm{2D}}}{\mathrm{d}
-V_{\mathrm{2D}}} = \dfrac{\dfrac{1}{C_{\mathrm{L}}} +
-\dfrac{1}{C_{\mathrm{H}}}}{\dfrac{1}{C_{\mathrm{d}}} + \dfrac{1}{C_{\mathrm{2D}}}}
-\end{equation}
-at a certain \(c_{0}\), the larger \(\beta\) is, the higher tunability in
-wettability of the 2D material will be. On the device side, it can be
-achieved if both \(C_{\mathrm{d}}\) and \(C_{\mathrm{2D}}\) are
-larger. Increasing the value of \(C_{\mathrm{2D}}\) can be implemented
-by replacing graphene--a 2D semimetal, with a 2D semiconductor, such
-as TMDC \cite{tian_multiscale_2016}. Here we evaluate a
-2D-material-based electrowetting device consists of a 2 nm thick HfO\(_{\text{2}}\)
-dielectric layer with \(\epsilon_{\mathrm{d}}=24.0\), and an 2D material
-sheet selected from graphene, silicene, germanene, MoS\(_{\text{2}}\), MoTe\(_{\text{2}}\), WS\(_{\text{2}}\)
-and WTe\(_{\text{2}}\) (see Fig. \ref{fig:dcos-all-2D}(a)). The magnitude of \(\Delta
-\cos \theta\) as a function of \(V_{\mathrm{2D}}\) in devices based on
-different 2D materials is shown in Fig. \ref{fig:dcos-all-2D}(b).
 \begin{figure}[htbp]
 \centering
-\includegraphics[width=0.95\linewidth]{../img/dcos-all-2D.pdf}
+\includegraphics[width=0.65\linewidth]{../img/dcos-all-2D.pdf}
 \caption{\label{fig:dcos-all-2D}
-(a) Schematic illustration of the 2D-material-based electrowetting device. (b) \(\Delta\cos\theta\) as a function of \(V_{\mathrm{2D}}\) for selected 2D materials.}
+(a) Schematic illustration of the 2D-material-based electrowetting device, where the 2D material is electostatically doped.
+(b) \((\Delta\cos\theta)^{\mathrm{EDL}}\) as a function of \(V_{\mathrm{G}}\) for selected 2D materials.}
 \end{figure}
-
-As expected in Eq. \ref{eqn:beta}, at the same \(V_{\mathrm{2D}}\) level,
-the 2D TMDC semiconductors (MoS\(_{\text{2}}\), MoTe\(_{\text{2}}\), WS\(_{\text{2}}\), WTe\(_{\text{2}}\)) exhibit a much
-higher response \(\Delta \cos \theta\) than 2D semimetals (silicene,
-germanene and graphene). We can briefly rank the voltage tunability of
-the selected 2D materials by their DOS: MoTe\(_{\text{2}}\) > MoS\(_{\text{2}}\) > WTe\(_{\text{2}}\) > WS\(_{\text{2}}\)
-> germanene > silicene > graphene. Notably, TMDCs can achieve a
-\(\Delta \Phi_{\mathrm{2D}}\) as high as 0.15 when
-\(V_{\mathrm{2D}}=\pm1.5\) V is applied, corresponding a contact angle
-decrease at the magnitude of 10\(^{\circ}\) when the intrinsic contact
-angle is ca. 90\(^{\circ}\).  A high-DOS 2D material further suppresses
-electrochemical reactions at the solid-liquid interface, as less
-electrochemical potential (i.e. the Fermi level \(E_{\mathrm{F}}\)) is
-required. We conclude that a 2D material with higher DOS can
-essentially reduced the voltage needed for doping, pushing
-liquid-phase 2D-material-based devices to a more operational regime.
-
-In conclusion, we propose a multiscale approach for modeling the
-doping-induced tunable wettability of 2D materials, by combining the
-reorientation effect of water molecules estimated by MD simulations,
-and the electrowetting effect calculated by a continuum model. Taking
-graphene as an example, we find that electrostatic interaction plays a
-major role at both scales for the graphene-water interface. We further
-show that, by considering the incomplete coverage of 2D material on
-the substrate, it is possible to evaluate the recent findings of
-doping-induced tuning of graphene's wettability with the proposed
-model. We find that minor surface incompleteness can cause great
-discrepancy in the measured value of interfacial wettability, and
-extreme care should be taken to interpret the observed
-electrowetting phenomena. In addition, we prove that a 2D material
-with higher density of states can essentially reduce the gating
-voltage in a 2D-material-based electrowetting device, and rank the
-tunability of the 2D materials as: MoTe\(_{\text{2}}\) > MoS\(_{\text{2}}\) > WTe\(_{\text{2}}\) > WS\(_{\text{2}}\) >
-germanene > silicene > graphene. Our multiscale analysis provides a
-comprehensive view of the wettability of 2D material interface, and we
-believe operational 2D-material-based liquid manipulating devices will
-be facilitated by the principles presented in this letter.
-\bibliography{ref}
 \end{document}

### 2017-06-01 writing/supporting_information.tex
Minor change and clean up files

--- 2017-02-22 writing/paper-Tian-gr-wetting.tex
@@
-% Created 2017-02-22 Wed 21:46
+% Created 2017-05-04 Thu 21:33
 % Intended LaTeX compiler: pdflatex
-\documentclass[journal=ancac3,manuscript=article,email=true]{achemso}
+\documentclass[journal=ancac3,manuscript=suppinfo,email=true]{achemso}
  \usepackage{minted}
@@
 \usepackage{xcolor}
+\usepackage{amsmath}
 \usepackage{fontspec}
@@
 \newpage{}
-\begin{abstract}
-  Understanding molecular interactions between liquid and the doped two-dimensional (2D) 
-  materials enables new technology opportunities in functional surfaces and ultrathin membranes. 
-  Here, we develop the first theoretical framework to model the wettability of the doped two-dimensional 
-  (2D) materials as a function of their doping level. Multiscale physical phenomena are considered, 
-  including: (i) the change of 2D materials surface energy, 
-  (ii) the molecular reorientation of liquid molecules adjacent to the interface, 
-  and (iii) the electrical double layer (EDL) formed in the liquid phase. 
-  \textcolor{cyan}{We propose that the EDL effect dominates the contact angle change }
-  and show that upon doping, the decrease of the equilibrium water contact angle on a sheet of defect-free, 
-  monolayer 2D material is typically less than 7 degrees. 
-  We then study the role of the surface defects and the influence of 2D material choice.
-  \textcolor{cyan}{Our analysis show that the defect density plays a crucial role in the water contact angle on the doped
-  2D materials, and is responsible for the discrepancy between the recent experimental observations and our proposed 
-  theory. Based on the quantum capacitances (QCs) of various 2D materials calculated by density functional theory (DFT),
-  we predict that when the the 2D material is doped by electrostatic gating, 
-  the contact angle change on 2D semiconductors (e.g. transition metal dichalcogenides (TMDCs)) is more
-  sensitive to the gate voltage compared to that on 2D semimetals (e.g. graphene). 
-  Selecting a 2D material with a higher QC essentially reduces the gate voltage required to reach the same doping level,
-  and ensures a wider operational region in 2D-material-based liquid phase devices.}
-  \textcolor{magenta}{
-  FINAL CONCLUSIONS PLACE HOLDER.
-  }
+\section{Figures}
+\label{sec:org176b821}
+\subsection{Dipole Orientation Profiles of MD Simulations}
+\label{sec:org3abd37b}
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.85\linewidth]{../img/SI-dipole-profile.pdf}
+\caption{\label{fig-SI-dipole}
+Dipole orientation \(\cos \mu\) as a function of \(z\) in MD simulations of different systems (L, and GL with varied graphene doping densities).
+The orientation at the water-vacuum interface (\$z\$=20 nm) is invariable in all cases, indicating a minimal effect of the long range Coulombic interaction on the selected interface.}
+\end{figure}
 
-\end{abstract}
-\maketitle
+\newpage{}
+\subsection{Hydrogen Bond Profiles of MD Simulations}
+\label{sec:orge06c9b9}
 
-\section{Introduction}
-\label{sec:org30908ab}
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.85\linewidth]{../img/hydrogen-bond.pdf}
+\caption{\label{fig-H-bond}
+Hydrogen bond strength as a function of \(z\) in MD simulations of various conditions (L, GL with graphene doping densities of -0.012, 0 and 0.012 \$e\$/atom).}
+\end{figure}
 
-Two-dimensional (2D) materials, the crystalline films with a thickness
-of one atom or one molecule, combine optical transparency and the
-quantum-confined properties.
 \begin{center}
@@
 \begin{minipage}[c]{.8\linewidth}
-\textbf{\textsf{\textsc{TODO}}} [cite some review papers].
+\textbf{\textsf{\textsc{TODO}}} Ask Prof. Lin for unit and explanation of H-Bond result
 
@@
 \end{center}
-Recent progress in the scalable production of large-area 2D materials
-\begin{center}
-\fbox{
-\begin{minipage}[c]{.8\linewidth}
-\textbf{\textsf{\textsc{TODO}}} cite review papers
-
-\end{minipage}
-}
-\end{center}
-has paved the way for the applications of functional surfaces and
-ultrathin membranes.
-\begin{center}
-\fbox{
-\begin{minipage}[c]{.8\linewidth}
-\textbf{\textsf{\textsc{TODO}}} cite review papers
-
-\end{minipage}
-}
-\end{center}
-
-The realization of these technologies essentially requires precise
-control over the interactions between liquid and the ultrathin
-materials, which motivates fundamental research of their
-wettability. An accurate determination of the interfacial tension,
-nevertheless, remains highly disputed
-\cite{taherian2013what,Kozbial_2015,Parobek_2015,Govind_Rajan_2016}. Early
-literature on understanding the surface science of 2D materials has
-highlighted the effects of the airborne contaminants
-\cite{li_effect_2013,Xu_2013_withwhat,kozbial_study_2014,Kozbial_2015,Chow_2015}
-and the underlying substrate
-\cite{raj_wettability_2013,rafiee_wetting_2012,shih_breakdown_2012,shih_wetting_2013},
-since the length scale for the van der Waals (vdW) interactions is
-comparable to the thickness of a monolayer. On the other hand, a
-subtle but important fact is that the 2D semimetals (e.g, graphene and
-silicene) and 2D semiconductors (e.g., transition metal
-dichalcogenides (TMDCs)) possess low density of states (DOSs) around
-the intrinsic Fermi level (\(E_{\mathrm{F}}\)), such that the effect of
-doping, either induced by the surroundings
-\cite{Chen_2013,Varchon_2007,Giovannetti_2008}, or by the electrostatic
-gating \cite{Das_2008,Perera_2013}, also comes into play. Very recently,
-the doping-induced change in the wettability of graphene has been
-observed in the contact-angle experiments
-\cite{hong_mechanism_2016,goniszewski_correlation_2016,ashraf_doping-induced_2016},
-and the molecular dynamics (MD) simulations
-\cite{ostrowski_tunable_2014,ren_interfacial_2015,Taherian_2015,daub_electrowetting_2007}. However,
-most reports described the doping-dependent wettability with the basic
-Young-Lippmann equation (YLE) \cite{Lippmann_1875}, whereas the
-interplay between the polar orientation of water molecules at the
-interface \cite{Shen_2006} and the electronic structure of the 2D
-materials is often ignored. In order to address the discrepancies
-among the literature, a more complete theoretical picture that bridges
-the gap between different length scales is clearly required.
-
-In this letter, we propose a multiscale approach to properly model the
-doping-induced tuning of 2D materials' wettability. We model the
-change of surface adhesion energy between water and 2D material as a
-combined effect of (i) reorientation of water molecules, characterized
-by molecular dynamic (MD) simulations and (ii) electrowetting due to
-formation of electric double layer, calculated by a continuum model
-based on modified Young-Lippman theory. By using graphene as an
-example, we demonstrate that, the electrostatic interaction plays a
-major role in both the reorientation and electrowetting effects. By
-further considering the surface coverage of 2D materials, we evaluate
-the previous reported result on the doping-induced wetting behavior of
-graphene using the proposed multiscale model. We find that the
-existence of minor defects can cause great discrepancy between the
-observed wetting property and theoretical values, requesting attentive
-interpretation of the experimental results. Moreover, we quantify the
-tunability of interfacial tension in a gate-controlled
-2D-material-based electrowetting device as a function of the DOS of
-the 2D material, and rank several 2D materials according to their
-tunability. We show that 2D materials with higher DOS such as
-transition metal dichalcogenides (TMDCs), perform better than graphene
-by means of wettability regulation. Our findings provide a
-comprehensional view of the wettability of 2D materials, as well as
-guidance for operational liquid-phase 2D material-based devices.
-
-Due to the complex dynamic nature of wetting
-\cite{Cassie_1944,Wenzel_1936,Gao_2007,Marmur_2009}, we only study the
-static wettability of 2D materials. We only consider water as the
-liquid phase, as most liquid-phase applications of 2D materials are
-also in aqueous environment. The macroscopic feature of
-wetting--contact angle \(\theta\), is connected to the interfacial
-adhesion energy \(\Phi_{\mathrm{2D-w}}\) by the Young's equation:
-\begin{equation}
-\label{eqn:young's equation}
-\Phi_{\mathrm{2D-w}} = -\gamma_{\mathrm{L}}(1+\cos\theta)
-\end{equation}
-where \(\Phi_{\mathrm{2D-w}}\) is defined as:
-\begin{equation}
-\label{eqn:def-adhesion}
-\Phi_{\mathrm{2D-w}} = \gamma_{\mathrm{2D-w}} - \gamma_{\mathrm{2D}} - \gamma_{\mathrm{w}}
-\end{equation}
-
-where \(\gamma_{\mathrm{2D-w}}\) is the surface tension between the
-interface of the 2D material and the aqueous phase,
-\(\gamma_{\mathrm{2D}}\) and \(\gamma_{\mathrm{w}}\) are the surface
-tensions of the 2D material and water in air,
-respectively.
-
-\(\Phi_{\mathrm{2D-w}}\) is contributed by both the
-short-range dispersion interaction and long-range electrostatic
-interaction between the 2D material and water. The existence of
-additional charges in 2D materials gives rise to the reorientation of
-adjacent water molecules \cite{ostrowski_tunable_2014}. On the other
-hand, the formation of electric double layer (EDL) in an ionic
-solution near the interface also alters the interfacial adhesion
-properties, known as the electrowetting effect \cite{Lippmann_1908},
-which has been widely used in microfluidic applications
-\cite{Mugele_2005}.  Owing to the additive nature of dispersion and
-electrostatic interactions, we propose that the change of interfacial
-adhesion energy \(\Delta \Phi_{\mathrm{2D-w}}\) is a combined effect of
-the reorientation effect \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{or}}\) and EDL
-formation \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}\):
-\begin{equation}
-\label{eqn:contrib-adhesion-change}
-\Delta \Phi_{\mathrm{2D-w}} = \Delta \Phi_{\mathrm{2D-w}}^{\mathrm{or}}
-                              + \Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}
-\end{equation}
-
-A multiscale approach is needed to combine both effects as their
-effective length scales are different. We use molecular dynamics (MD)
-simulations for sampling the orientation effect adjacent to the 2D
-material; in addition a continuum model is implemented to describe the
-contribution of EDL formation, since state-of-art MD simulations fail to
-handle diluted ionic solution systems where the Debye length can be as
-long as 10\(^{\text{3}}\) nm. Our multiscale modeling approach is schematically illustrated in Fig. \ref{fig:scheme-method}.
-
+\newpage{}
+\subsection{Fitting of the \(\Delta \Phi\) - \(\sigma_{\mathrm{2D}}\) Data in MD Simulations}
+\label{sec:orgb2e4751}
 \begin{figure}[htbp]
 \centering
-\includegraphics[width=0.95\linewidth]{../img/scheme-methods.pdf}
-\caption{\label{fig:scheme-method}
-Scheme of the multiscale approach for modeling the doping-induced wettability tuning of 2D materials.}
+\includegraphics[width=0.85\linewidth]{../img/e-Phi-fitting.pdf}
+\caption{\label{fig-SI-fitting}
+Fitting of \(\Delta \Phi\) - \(\sigma_{\mathrm{2D}}\) data from MD simulations with different polynomial functions. The 3rd degree polynomial function is chosen as the best fitting model.}
 \end{figure}
-
-It is also noteworthy that our multiscale approach is compatible with
-the issues of the intrinsic wettability and wetting translucency of 2D
-materials. Since we are dealing with the change of interfacial
-adhesion energy as a function of surface charge, the absolute value of
-\(\Phi_{\mathrm{2D-w}}\) or \(\gamma_{\mathrm{2D-w}}\) (extracted from intrinsic wetting property and wetting translucency theory) can be treated as
-independent variables.
-
-We model the charged 2D materials as rigid sheets with uniform surface
-charge density \(\sigma_{\mathrm{2D}}\), either by substrate or
-electrostatic doping. We also assume that the 2D material has no
-dissociable groups which can change the aqueous pH value
-\cite{zuccaro_tuning_2015} and the 2D material is inert to
-electrochemical reaction at the interface
-\cite{bard_electrochemical_1980}.  First we use graphene as a model
-system to show the effect of reorientation of water molecules on the
-interfacial adhesion energy. Different from previous approaches which
-used MD simulations to extract the contact angle of nanodroplets on
-graphene
-\cite{ostrowski_tunable_2014,daub_electrowetting_2007,ren_interfacial_2015,Taherian_2015},
-where the interfacial adhesion energy cannot be accurately measured
-due to changed contact area between water and graphene, here we
-propose to use a continuous water monolith in the MD simulation with periodic boundary conditions in the x and y directions to
-calculate the interfacial adhesion energy \(\Phi_{\mathrm{2D-w}}\).
-\begin{center}
-\fbox{
-\begin{minipage}[c]{.8\linewidth}
-\textbf{\textsf{\textsc{TODO}}} Description for MD simulation
-
-\end{minipage}
-}
-\end{center}
-
-The adhesion energy \(\Phi_{\mathrm{2D-w}}^{or}\) in the MD simulation is
-defined as:
-\begin{equation}
-\label{eqn:Delta-Phi-or-definition}
-\begin{aligned}
-\Phi_{\mathrm{2D-w}}^{or} &= (\Psi_{\mathrm{2D-w}} - \Psi_{\mathrm{w}} - \Psi_{\mathrm{2D}})\frac{1}{S \cdot N_{\mathrm{A}}} \\
-                     &= \Phi_{\mathrm{LJ}} + \Phi_{\mathrm{CL}}
-\end{aligned}
-\end{equation}
-where \(S\) is the area of the graphene sheet (same as the contact area
- between water and graphene), \(N_{\mathrm{A}}\) is the Avogadro's
- number, \(\Psi_{\mathrm{2D-w}}\) is the total internal potential of the
- 2D material-water system, and \(\Psi_{\mathrm{w}}\) and
- \(\Psi_{\mathrm{2D}}\) are the potentials of the separated water phase
- and 2D materials, respectively.  The adhesion energy can be further
- decomposed into the short-range Lenard-Jones potential term
- (\(\Phi_{\mathrm{LJ}}\)) and the long-range Coulombic interaction term
- (\(\Phi_{\mathrm{CL}}\)). Since \(\Psi_{\mathrm{w}}\) and
- \(\Psi_{\mathrm{2D}}\) are unalterable in the MD simulation, the change
- of interfacial adhesion energy \(\Delta \Phi_{\mathrm{2D-w}}^{or}\) as a
- result of surface doping, is calculated as:
-\begin{equation}
-\label{eqn:delta-Phi-2D-or}
-\begin{aligned}
-\Delta \Phi_{\mathrm{2D}}^{or} &= \frac{\Delta \Phi_{\mathrm{2D-w}}}{S \cdot N_{\mathrm{A}}} \\
-                               &= \Delta \Phi_{\mathrm{LJ}} + \Delta \Phi_{\mathrm{CL}}
-\end{aligned}
-\end{equation}
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.9\linewidth]{../img/fig-pot-dens.pdf}
-\caption{\label{fig:pot-dens}
-(a) Change of total adhesion energy \(\Delta\Phi_{\mathrm{2D}}^{or}\), contribution of Lenard-Jones interaction \(\Delta\Phi_{\mathrm{LJ}}\) and Coulombic interaction \(\Delta\Phi_{\mathrm{CL}}\), as a function of charge density on graphene.
-(b) Local density of water molecule (\(\rho_{\mathrm{w}}\))  as a function of distance \(z\) from graphene surface.}
-\end{figure}
-
-The changes of adhesion energy terms \(\Delta
-\Phi_{\mathrm{2D-w}}^{or}\), \(\Delta \Phi_{\mathrm{LJ}}\) and \(\Delta
-\Phi_{\mathrm{CL}}\), as functions of \(\sigma_{\mathrm{2D}}\) , are
-shown in Fig. \ref{fig:pot-dens}(a). It can be seen that the
-contribution from dispersion interaction \(\Delta \Phi_{\mathrm{LJ}}\)
-has a very small magnitude of negative change (less than 2.5 mJ\(\cdot
-\mathrm{m}^{-2}\)) when \(\sigma_{\mathrm{2D}}\) ranges from
--5\(\times10^{13}\) \textasciitilde{} 5\(\times10^{13}\) \(e\cdot \mathrm{cm}^{-2}\). On the
-other hand, we find that \(\Delta \Phi_{\mathrm{CL}}\) contributes
-majorly to \(\Delta \Phi_{\mathrm{2D-w}}^{or}\), indicating the
-electrostatic nature of the doping-induced reorientation of water
-molecules.
-\begin{center}
-\fbox{
-\begin{minipage}[c]{.8\linewidth}
-\textbf{\textsf{\textsc{TODO}}} Validate the statement above
-
-\end{minipage}
-}
-\end{center}
-It is also interesting to find that, unlike its counterpart from
-dispersion interaction, \(\Delta \Phi_{\mathrm{CL}}\) has a asymmetric
-response to \(\sigma_{\mathrm{2D}}\). We further plot the local density
-of water molecules \(\rho_{\mathrm{w}}\), as a function of distance \(z\)
-from the graphene plane, which can be seen in Fig. \ref{fig:pot-dens}(b). We consider
-3 cases where the graphene layer is either charge-neutral, or
-\(\sigma_{\mathrm{2D}}=\pm 0.012\ e/ \mathrm{atom}\), respectively. We
-find that the \(\rho_{\mathrm{w}}\) at the first water layer adjacent to
-graphene (\(z \approx 3.2\ \mathrm{\AA}\)) also responsed asymmetrically with
-\(\sigma_{\mathrm{2D}}\).  When \(\sigma_{\mathrm{2D}}=-0.012\ e/
-\mathrm{atom}\), \(\rho_{\mathrm{w}}\) drops to ca. 80\% of that in the
-electroneutral system, while \(\rho_{\mathrm{w}}\) at
-\(\sigma_{\mathrm{2D}}=0.012\ e/ \mathrm{atom}\) has a 8\% increase in the density compared with the electroneutral system. The change of interfacial water
-density can be ascribed by the polarity of water molecules. When the
-graphene layer is positively charged, the O atom is more favorably
-facing the graphene surface, while H atom is more favorably facing the
-negatively-charged surface.
-\begin{center}
-\fbox{
-\begin{minipage}[c]{.8\linewidth}
-\textbf{\textsf{\textsc{TODO}}} Describe the density change
-
-\end{minipage}
-}
-\end{center}
-\begin{center}
-\fbox{
-\begin{minipage}[c]{.8\linewidth}
-\textbf{\textsf{\textsc{TODO}}} More in-depth discussion?
-
-\end{minipage}
-}
-\end{center}
-
-It is noteworthy that although the process for investigating the
-magnitude of \(\Delta \Phi_{\mathrm{2D-w}}^{or}\) is similar for other 2D
-materials other than graphene, the result obtained here cannot be
-readily applied to other 2D materials, since the contribution of
-dispersion interaction and electrostatic interaction can be completely
-different \cite{Govind_Rajan_2016,Chow_2015}. Nevertheless, in
-real-world measurements, due to the existence of the contamination
-layer which has a typical thickness ca. 1\textasciitilde{}2 nm, the dispersion
-interactions contributed by surface charge can be nearly completely
-screened out; aqueous electrolytes can also greatly attenuate the
-electric displacement field, compared with the dipole water model used
-in the MD simulations. Therefore we propose that the effect of
-reorientation may not be easily observable in current experimental
-setups.
-
-While the interfacial dispersion interaction vanishes several
-molecules away from the surface, the long range electrostatic
-interaction will cause the aqueous ions to rearrange at a much longer
-length scale, forming an EDL at the interface and decrease the
-interfacial surface tension by the phenomenon known as electrowetting.
-Revisiting Eq. (\ref{eqn:def-adhesion}), we know that the change of
-interfacial tension due to electrostatic interactions, \(\Delta
-\Phi_{\mathrm{2D-w}}^{\mathrm{el}}\), is given by:
-
-\begin{equation}
-\label{eqn:Delta-Phi-el-def}
-\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}} = \Delta \gamma_{\mathrm{2D-w}}^{\mathrm{el}}
-                                           -\Delta \gamma_{\mathrm{2D}}^{\mathrm{el}}
-                                           -\Delta \gamma_{\mathrm{w}}^{\mathrm{el}}
-\end{equation}
-where \(\Delta \gamma_{\mathrm{2D-w}}^{\mathrm{el}}\), \(\Delta
-\gamma_{\mathrm{2D}}^{\mathrm{el}}\) and \(\Delta
-\gamma_{\mathrm{w}}^{\mathrm{el}}\) denote the change of surface
-tension of 2D material-water interface, 2D material-air and
-water-air, respectively. In the continuum model, all the changes of
-surface tensions can be modeled by surface excesses. From the
-isothermal 2D Gibbs-Duhem equation we can calculate the change of surface
-energy \(\mathrm{d} \gamma\):
-
-\begin{equation}
-\label{eqn:iso-gibbs-duhem}
-\displaystyle
-\mathrm{d}\gamma = -\frac{\sum_{\mathrm{i}} n_{\mathrm{i}}^{\mathrm{ex}}}{A} \mathrm{d} \mu_{\mathrm{i}} 
-                 = -\sum_{\mathrm{i}} \Gamma_{i} \mathrm{d} \mu_{\mathrm{i}}
-\end{equation}
-where \(n_{\mathrm{i}}^{\mathrm{ex}}\) is the surface excess amount of
-specie i, \(A\) is the unit are of the surface, \(\Gamma_{\mathrm{i}}\) is
-the surface excess concentration of specie i, and \(\mu_{\mathrm{i}}\)
-is the chemical potential of specie i. Eq. (\ref{eqn:iso-gibbs-duhem})
-indicates that: both the charges accumulated on the 2D material
-surface and the formation of electric double layer will alter the
-interfacial tension of 2D materials. As far as we are concerned, the
-effect of charge-induced surface tension change of 2D materials has
-rarely been addressed previously. For a charged 2D material surface in
-air, the decrease of surface tension equals the work required to
-charge the isolated 2D material:
-
-\begin{equation}
-\label{eqn:dgamma-QC}
-\begin{aligned}
-\mathrm{d} \gamma_{\mathrm{2D}}^{\mathrm{el}} &= -\Gamma_{e} \mathrm{d} E_{\mathrm{F}} \\
-                                              &= -\frac{\sigma_{\mathrm{2D}}}{C_{\mathrm{2D}}} \mathrm{d}\sigma_{\mathrm{2D}}
-\end{aligned}
-\end{equation}
-where \(E_{\mathrm{F}}=\mu_{e}\) is the Fermi level of the 2D material
-(equals the chemical potential of electrons in the 2D materials) and
-\(C_{\mathrm{2D}}\) is the quantum capacitance of the 2D material, which
-is proportional to the density of states (DOS) \(g(E_{\mathrm{F}})\) at
-Fermi level \(E_{\mathrm{F}}\):
-\(C_{\mathrm{2D}}=g(E_{\mathrm{F}})e^{2}\). Due to the fact that most 2D
-materials possess quantum capacitances essentially smaller than those
-of bulk materials, one would expect that the charge-induced-decrease
-of surface tension of 2D materials is more prominent than bulk
-materials. Here we demonstrate the degree of charge-induced
-surface tension decrease of several typical 2D materials in
-air. The selected 2D materials are graphene, silicene (2D allotrope
-of Si), germanene (2D allotrope of Ge), MoS\(_{\text{2}}\), MoTe\(_{\text{2}}\), WS\(_{\text{2}}\) and
-WTe\(_{\text{2}}\), respectively. Their DOS as functions of \(E_{\mathrm{F}}\) have been previously
-reported by density functional theory (DFT) calculation, based on the
-HSE06 hybrid functional approach \cite{tian_multiscale_2016}. The
-charge-induced decrease of surface tension of the 2D materials
-\(\Delta \gamma_{\mathrm{2D}}^{\mathrm{el}}\), as a function of the
-surface charge density \(\sigma_{\mathrm{2D}}\), is shown in Fig. \ref{fig:dgamma-sigma}.
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.95\linewidth]{../img/dgamma-sigma.pdf}
-\caption{\label{fig:dgamma-sigma}
-\(\Delta \gamma_{\mathrm{2D}}^{\mathrm{el}}\) as a function of \(\sigma_{\mathrm{2D}}\) for several 2D materials: graphene, silicene, germanene, MoS\(_{2}\), MoTe\(_{2}\), WS\(_{2}\) and WTe\(_{2}\)}
-\end{figure}
-It can be observed from our calculations that graphene has the largest
-degree of surface tension decrease (ca. 22 mJ\(\cdot\mathrm{m}^{-2}\)
-when \(\sigma_{\mathrm{2D}}=\pm5\times10^{13}\ e\cdot
-\mathrm{cm}^{-2}\)), due to the fact that graphene has the lowest
-\(C_{\mathrm{2D}}\) among the selected 2D materials
-\cite{tian_multiscale_2016}. We can rationalize the \(\Delta
-\gamma_{\mathrm{2D}}^{\mathrm{el}}\) - \(\sigma_{\mathrm{2D}}\) relation
-of the 2D materials by their \(C_{\mathrm{2D}}\) values: the 2D
-semimetals (graphene, silicene and germanene) generally have larger
-decrease of surface tension, compared with the semiconducting 2D TMDCs
-at same doping level, due to the limited DOS dispersion in 2D
-semimetals. Notably, the results indicate that a significant decrease
-of surface tension of 2D materials (at the order of 10 mJ\(\cdot
-\mathrm{m}^{-2}\)) can be achieved with a doping at the order of
-\(10^{13}\ e\cdot \mathrm{cm}^{-2}\), and may eventually be experimentally
-observed.
-
-Similarly, \(\Delta \gamma_{\mathrm{2D-w}}^{\mathrm{el}}\) is
-contributed by both the 2D surface charge and the charge accumulation
-in the EDL:
-
-\begin{equation}
-\label{eqn:dgamma-2D-w}
-\mathrm{d}\gamma_{\mathrm{2D-w}}^{\mathrm{el}} = -\frac{\sigma_{\mathrm{2D}}}{e} \mathrm{d}E_{\mathrm{F}}
--\sum_{\mathrm{i}} z_{\mathrm{i}}e\Gamma_{\mathrm{i}}^{\mathrm{s}} \mathrm{d}\psi_{\mathrm{2D}}
-\end{equation}
-where \(\Gamma_{\mathrm{i}}^{\mathrm{s}}\) and \(z_{\mathrm{i}}\) are the
-surface excess concentration and valency of ionic solute i,
-respectively; \(\psi_{\mathrm{2D}}\) is the electrostatic potential at the 2D
-material-water interface. On the other hand \(\gamma_{\mathrm{w}}\) is
-independent of the surface charge of the 2D material, since no surface
-excess is present at the water-air interface. We therefore derive
-the expression for \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}\) as
-follows:
-
-\begin{equation}
-\label{eqn:Delta-Phi-final}
-\begin{aligned}
-\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}} &= -\frac{\sigma_{\mathrm{2D}}}{e}dE_{\mathrm{F}} 
-                                             -\sum_{\mathrm{i}} z_{\mathrm{i}}e\Gamma_{\mathrm{i}}^{\mathrm{s}} \mathrm{d}\psi_{\mathrm{2D}}
-                                             +\frac{\sigma_{\mathrm{2D}}}{e}dE_{\mathrm{F}} \\
-                                          &= -\sigma_{\mathrm{L}} \mathrm{d}\psi_{\mathrm{2D}}
-\end{aligned}
-\end{equation}
-where \(\sigma_{\mathrm{L}}\) is the total charge density in the EDL. As
-the accumulation of charge on the 2D material surface occurs both on
-the 2D material-air and 2D material-water interfaces, their
-contributions to the surface tension is canceled out. As a result
-\(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}\) is governed by the ion
-accumulation in EDL alone, in consistent with the trivial
-electrowetting theory (constant solid surface tension). However, the
-absolute values of \(\gamma_{\mathrm{2D-w}}\) and \(\gamma_{\mathrm{2D}}\)
-do change due to the aforementioned phenomenon.
-
-To evaluate the effect of electrowetting, we first
-consider that a contamination layer with thickness \(d_{\mathrm{c}}\)
-covers the 2D material surface. Since the airborne contaminants are
-mostly hydrocarbon compounds, they can be treated as a dielectric
-layer with permittivity \(\epsilon_{\mathrm{c}}\). We use the
-Gouy-Chapman-Stern model to describe the EDL in the aqueous phase,
-which consists a Helmholtz double layer with the same permittivity
-\(\epsilon_{\mathrm{w}}\) as water, and thickness \(d_{\mathrm{H}}\),
-together with a diffuse layer where ionic distribution is described by
-the Gouy-Chapman equation.  The potentials at the surface of the 2D
-material, the contamination layer surface and the outer Helmholtz
-plane (the interface between the Helmholtz double layer and the
-diffuse layer) are \(\psi_{\mathrm{2D}}^{*}\), \(\psi_{\mathrm{2D}}\) and
-\(\psi_{\mathrm{L}}\), respectively. An illustration of the model for the
-2D-material-water interface is shown in Fig. \ref{fig:scheme-EDL}.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.95\linewidth]{../img/scheme-EDL.pdf}
-\caption{\label{fig:scheme-EDL}
-Scheme of the interface between the 2D material and the aqueous phase.
-A electrostatic potential \(\psi_{\mathrm{2D}}\) is built at the interface, as a result of surface charge on 2D material \(\sigma_{\mathrm{2D}}\).}
-\end{figure}
-
-If we neglect specific adsorption of ions at the solid-liquid interface,
-electroneutrality ensures that the charge density of the 2D material
-\(\sigma_{\mathrm{2D}}\) balances the total charge density of the EDL
-\(\sigma_{\mathrm{L}}\) \cite{bard_electrochemical_1980}:
-\begin{equation}
-\sigma_{\mathrm{2D}} + \sigma_{\mathrm{L}} = 0
-\end{equation}
-From the Gouy-Chapman model of 1 symmetric electrolyte we know:
-\begin{align}
-\displaystyle
-\label{eqn:psi-L}
-\psi_{\mathrm{L}} &= -\frac{2k_{\mathrm{B}}T}{z_{0}e} 
-                       \sinh^{-1}\left(
-                         \frac{\sigma_{\mathrm{L}}}{\sqrt{8c_{0}N_{\mathrm{A}}\epsilon_{\mathrm{w}}k_{\mathrm{B}}T}}
-                          \right) \\
-\label{eqn:psi-2D}
-\psi_{\mathrm{2D}} &= \psi_{\mathrm{L}} - \sigma_{\mathrm{L}}\frac{d_{\mathrm{H}}}{\epsilon_{\mathrm{w}}} \\
-\psi_{\mathrm{2D}}^{*} &= \psi_{\mathrm{2D}} - \sigma_{\mathrm{L}}\frac{d_{\mathrm{c}}}{\epsilon_{\mathrm{c}}}
-\end{align} 
-where \(z_{0}\) is the valency of the electrolyte, \(c_{0}\) is the
-concentration of the electrolyte, \(N_{\mathrm{A}}\) is the Avogadro
-constant and \(k_{\mathrm{B}}\) is the Boltzmann constant. While the
-contamination layer is responsible for a potential drop across the
-solid phase, the solid-liquid interfacial potential
-\(\psi_{\mathrm{2D}}\) which contributes to the \(\Delta \Phi_{\mathrm{2D-w}}^{el}\), is only governed by \(\sigma_{\mathrm{L}}\). Therefore
-we conclude that the existence of a contamination layer does not affect
-the magnitude of \(\Delta \Phi_{\mathrm{2D-w}}}^{el}\).
-
-The exact solution of \(\Delta
-\Phi_{\mathrm{2D-w}}^{el}\) can be derived from Eqs (\ref{eqn:psi-2D})
-and (\ref{eqn:psi-L}):
-\begin{equation}
-\label{eqn:Delta-Phi-exact}
-\begin{aligned}
-\Delta \Phi_{\mathrm{2D-w}}^{el}
-&= -\int_{0}^{\psi_{\mathrm{2D}}} \sigma_{\mathrm{L}} \mathrm{d}\psi' \\
-&= -\int_{0}^{\sigma_{\mathrm{L}}} \sigma'\left(
-   \frac{1}{C_{\mathrm{H}}} + \frac{1}{C_{\mathrm{L}}}
-                                          \right) \mathrm{d}\sigma' \\
-&= -\frac{\sigma_{\mathrm{L}}^{2}}{2C_{\mathrm{H}}}
-    -\sqrt{\frac{32k_{\mathrm{B}}^{3}T^{3} \epsilon_{\mathrm{w}} c_{0} N_{\mathrm{A}}}{z_{0}^{2}e^{2}}}
-   \left[\cosh(\frac{z_{0}e\psi_{\mathrm{L}}}{2k_{\mathrm{B}}T}) - 1\right] \\
-&= -\frac{\sigma_{\mathrm{L}}^{2}}{2C_{\mathrm{H}}} 
-   - \frac{\sigma_{\mathrm{L}}^{2}}{C_{\mathrm{L}} 
-   + \frac{\epsilon_{w}}{\lambda_{\mathrm{D}}}}
-\end{aligned}
-\end{equation}
-where \(C_{\mathrm{H}}=\epsilon_{w}/d_{\mathrm{H}}\) is the geometric
-capacitance of the Helmholtz double layer,
-\(C_{\mathrm{L}}=\sqrt{\frac{2z_{0}^{2}e^{2}\epsilon_{\mathrm{w}}c_{0}N_{\mathrm{A}}}{k_{\mathrm{B}}T}}
-\cosh (\frac{z_{0}e\psi_{\mathrm{L}}}{2k_{\mathrm{B}}T})\) is the
-capacitance of diffuse layer derived from the Gouy-Chapman equation,
-and
-\(\lambda_{\mathrm{D}}=\sqrt{\frac{\epsilon_{\mathrm{w}}k_{\mathrm{B}}T}{2z^{2}e^{2}c_{0}N_{\mathrm{A}}}}\)
-is the Debye length of the electrolyte. The quantity
-\(\epsilon_{\mathrm{w}}/\lambda_{\mathrm{D}}\) is actually the
-Debye-Hückel-style capacitance of the EDL.
-Eq. (\ref{eqn:Delta-Phi-exact}) shows that \(\Delta
-\Phi_{\mathrm{2D-w}}^{el}\) consists of the contributions from the
-Helmholtz double layer and the diffuse layer, respectively.  Note that
-at room temperature, when \(\sigma_{\mathrm{2D}}\) is large
-(e.g. \(10^{13}\) \(e\cdot \mathrm{cm}^{-2}\)) and \(c_{0}\) is small
-(e.g. \(10^{-7}\) mol\(\cdot \mathrm{L}^{-1}\)),
-\(\psi_{\mathrm{L}}\)=347 mV
-, which is much larger than \(k_{\mathrm{B}}T/e\), causing a significant
-discrepancy between the Gouy-Chapman capacitance \(C_{\mathrm{L}}\) and
-the Debye-Hückel capacitance
-\(\epsilon_{\mathrm{w}}/\lambda_{\mathrm{D}}\). This effect is often
-ignored in previous studies concerning the electrowetting on graphene
-and other 2D materials
-\cite{ostrowski_tunable_2014,daub_electrowetting_2007,goniszewski_correlation_2016,ashraf_doping-induced_2016},
-and the classical Young-Lippman equation \(\Delta
-\gamma=-\frac{1}{2}C\psi^{2}\) (or \(\Delta
-\gamma=-\frac{\sigma^{2}}{2C}\)) is casually used instead, assuming the
-capacitance to be constant.
-Since most of the reported samples deals with pure water with extremely low \(c_{0}\), the Debye-Hückel capacitance is much smaller than the Gouy-Chapman capacitance, leading to an overestimation of \(\Delta\cos\theta\).
-Therefore our
-derivation in Eq. \ref{eqn:Delta-Phi-exact} provides a more accurate
-approach to analyze \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}\) as a function of \(\sigma_{\mathrm{2D}}\).
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.85\linewidth]{../img/2d-ph-dependency.pdf}
-\caption{\label{fig:Delta-cos-dependency}
-(a) \(\Delta\cos\theta\) as a function of \(\sigma_{\mathrm{2D}}\).The concentration varies from \(10^{0}\) to \(10^{-7}\) mol\(\cdot\mathrm{L}^{-1}\) (b) \(\Delta\theta\) as a function of \(\sigma_{\mathrm{2D}}\) and the hypothetical contact angle on a charge-neutral 2D material layer \(\theta^{*}\).
-c\(_{\text{0}}\) is taken as \(10^{-7}\) mol\(\cdot\mathrm{L}^{-1}\).}
-\end{figure}
-
-Consider that the aqueous phase contains a 1:1 electrolyte with
-concentration \(c_{0}\), the thickness of the Helmholtz plane
-\(d_{\mathrm{H}}=3\ \mathrm{\AA}\) \cite{mcclendon_thickness_1927}, and
-the surface tension of water \(\gamma_{\mathrm{w}}=72.8\) mJ\(\cdot
-\mathrm{m}^{-2}\) at \(T=298\) K, we calculate the magnitude of
-\(\Delta\Phi_{\mathrm{2D-w}}^{el}\) and \(\Delta\cos\theta\) as function
-of \(\sigma_{\mathrm{2D}}\), as shown in
-Fig. \ref{fig:Delta-cos-dependency}(a). We discover that both the
-changes in the magnitude of interfacial adhesion energy and the
-contact angle become more pronounced when the concentration of
-electrolyte is lower. On the contrary, in conventional electrowetting
-model, \(\Delta\theta\) is governed by the constant capacitance of the
-dielectric layer and is almost irrelevant to the \(c_{0}\). The results indicate that the variation of \(c_{0}\) has a significant impact on \(\Delta
-\Phi_{\mathrm{2D-w}}^{el}\) and \(\Delta \cos \theta\) in the
-electrowetting on doped 2D materials. This is due to the fact that the
-interfacial potential \(\psi_{\mathrm{2D}}\) is affected by both the
-surface charge \(\sigma_{\mathrm{2D}}\) and \(c_{0}\), as indicated by
-Eq. (\ref{eqn:psi-L}) and (\ref{eqn:psi-2D}). When \(c_{0}\) is lower, a
-larger potential is required to be built upon the interface, giving
-rise to a larger change in the interfacial wetting property.
-
-Although the ``real'' contact angle of a 2D material can be tedious to
-determine, it is still possible to estimate the magnitude of contact
-angle change due to the electrowetting effect, by assuming that the
-hypothetical contact angle \(\theta^{*}\) on a charge-neutral 2D
-material layer. \(\theta^{*}\) consists of the effect of intrinsic
-wettability, surface contamination as well the wetting translucency of
-the 2D material-liquid interface. Fig. \ref{fig:Delta-cos-dependency}(b)
-shows the magnitude of contact angle decrease as a function of both
-\(\sigma_{\mathrm{2D}}\) and \(\theta^{*}\), when \(c_{0}=10^{-7}\)
-mol\(\cdot \mathrm{L}^{-1}\) (e.g. ideally pure water). Within the range
-of typical contact angles reported on graphene (ca. 40\(^{\circ}\) \textasciitilde{}
-100\(^{\circ}\)), and a doping level of \(-5\times10^{13}\) \textasciitilde{}
-\(5\times10^{13}\) \(e \cdot \mathrm{cm}^{-2}\), we find that the maximum
-magnitude \(\Delta\theta\) is only ca. 7\(^{\circ}\) when doping level is
-as high as \(\pm 5 \times 10^{13}\) \(e\cdot \mathrm{cm}^{-2}\),
-essentially smaller than previously reported values which were
-measured both under smaller doping levels
-\cite{hong_mechanism_2016,ashraf_doping-induced_2016}.  Due to the
-saturation of CO\(_{\text{2}}\) in water and soluble contaminants, the effect of
-electrowetting may be even less prominent in real
-situations. Therefore we believe that the electrowetting effect theory
-on 2D materials alone, cannot explain the current findings of
-doping-induced wettability change on graphene.
-
-Practically in a contact angle measurement, the amount of water varies
-from pL (using environmental scanning electron microscopy, ESEM) to
-\(\mathrm{\mu L}\) (using goniometer). Unlike nanodroplet models used in
-MD contact angle simulations, the droplets used experimentally are
-large enough to be exposed to both pristine and defect 2D surface, and
-can therefore be trapped in the local minimal state caused by nanoscale
-defects \cite{raj_wettability_2013}, giving rise to uncertainty of the
-measured contact angle. Meanwhile, it is widely observed that
-nanopores and macroscopic cracks exist in the transferred 2D material,
-increasing the adhesion interaction between the substrate and the
-water droplet.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.95\linewidth]{../img/scheme-crack.pdf}
-\caption{\label{fig:scheme-crack}
-Schematic drawing of the incomplete surface coverage in (a) substrate doping and (b) electrostatic doping systems.
-In both cases the aqueous phase is exposed directly to the substrate, leading to a discrepancy of apparent wetting properties compared with theoretical values.}
-\end{figure}
-
-We further consider the cases where the 2D material does not
-completely cover the substrate. In both the substrate-induced doping
-(see Fig. \ref{fig:scheme-crack}(a)) and the electrostatic doping (see
-Fig. \ref{fig:scheme-crack}(b)) systems, substrate surface charge still
-exists in non-covered regions: in surface doping the charged dopants
-(i.e. polyelectrolytes) will instantly build up a EDL near the
-substrate surface, while in electrostatic doping the electric
-displacement field still forms between the conducting 2D material and
-the gate electrode via the non-covered region, also causing the ions
-to accumulate at the substrate-water interface. The interfacial
-adsorption density of ions can essentially be larger than the surface
-charge density on 2D material, due to the partial screening of
-electric displacement field of the 2D material
-\cite{tian_multiscale_2016,Shih2015PartiallyScreened,Muruganathan_2015,Huttmann_2015}. Since
-the electrowetting effect is amphipolar, the accumulation of cations
-and anions at the 2D material surface or the non-covered region
-both contribute to the decrease of the apparent surface tension
-\(\hat{\gamma}_{\mathrm{2D-w}}\). We assume that the electrowetting at
-the non-covered region is described by the classical Young-Lippman
-\(\Delta
-\gamma_{\mathrm{nc}}=-\frac{\sigma_{\mathrm{2D}}^{2}}{2C_{\mathrm{nc}}}\),
-where \(C_{\mathrm{nc}}\) is the effective capacitance of the
-non-covered region (taken as the EDL capacitance in substrate doping,
-or the geometric capacitance of dielectric layer in electrostatic
-doping). We therefore describe \(\Delta
-\hat{\gamma}_{\mathrm{2D-w}}\) as a combined effect of the
-electrowetting on both pristine 2D material surface and non-covered substrate surface,
-characterized by the surface coverage index \(f\):
-\begin{equation}
-\label{eqn:apparent-gamma-combined}
-\begin{aligned}
-\Delta \hat{\gamma}_{\mathrm{2D-w}} &= f \Delta \gamma_{\mathrm{2D-w}} + (1-f)\Delta \gamma_{\mathrm{nc}} \\
-&= f \Delta \gamma_{\mathrm{2D-w}}  -\frac{1}{2}(1-f)\frac{\sigma_{\mathrm{2D}}^{2}}{C_{\mathrm{nc}}}
-\end{aligned}
-\end{equation}
-
-It should also be noted that in electrowetting experiments
-where additional charge is doped to the 2D material via dielectric
-layer \cite{hong_mechanism_2016}, the initial doping density
-\(\sigma_{\mathrm{i}}\) should also be considered to explain the
-asymmetric electrowetting behavior. In an electrowetting system where a
-dielectric layer with geometric capacitance \(C_{\mathrm{d}}\) and external
-voltage \(V_{\mathrm{2D}}\) is applied to the 2D material, the doping
-density in the 2D material is calculated as \cite{tian_multiscale_2016}:
-\begin{equation}
-\label{eqn:doping-vm-2D}
-V_{\mathrm{2D}} = \frac{\sigma_{\mathrm{2D}} - \sigma_{\mathrm{i}}} {C_{\mathrm{d}}} 
-                 + \int_{\sigma_{\mathrm{i}}}^{\sigma_{\mathrm{2D}}} 
-                   \frac{1}{C_{\mathrm{2D}}} \mathrm{d}\sigma'
-\end{equation}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.95\linewidth]{../img/plot-fitting.pdf}
-\caption{\label{fig:f-nc-exp}
-Theoretical and fitted experimental data of \(\Delta\cos\theta\) as a function of \(\sigma_{\mathrm{2D}}\).
-The electrowetting data are extracted from Ref.
-\cite{hong_mechanism_2016}; the ESEM data are extracted from Ref.
-\cite{ashraf_doping-induced_2016}.}
-\end{figure}
-
-To examine the effect of incomplete 2D material coverage, we select
-two sets of reported experimental measurements of the wettability on
-doped graphene sheet, namely the contact angles of substrate-doped
-graphene measured by ESEM from Ref. \cite{ashraf_doping-induced_2016}
-and the contact angles of electostatically-doped graphene via
-goniometer from Ref. \cite{hong_mechanism_2016}. The contact angle at
-experimentally ``charge-neutral'' condition (graphene attached to SiO\(_{\text{2}}\)
-substrate for ESEM experiment or \(V_{\mathrm{2D}}=0\) V in
-electrowetting experiment, however \(\sigma_{\mathrm{2D}}\) may not be 0
-due to existence of \(\sigma_{\mathrm{i}}\)) is used as reference for
-calculating \(\mathrm{d}\cos\theta\). We use
-Eq. \ref{eqn:apparent-gamma-combined} to extract \(f\) and
-\(\sigma_{\mathrm{i}}\) for both experiments, as seen in
-Fig. \ref{fig:f-nc-exp}. We observe that in both experimental data sets,
-the measured \(\Delta \cos \theta\) is essential larger than the
-theoretical value derived from the Gouy-Chapman-Stern model described
-here. Fitting results reveals both systems are lightly p-doped in the
-``charge-neutral'' condition, which corresponds well with other
-experimental reports
-\cite{Shih2015PartiallyScreened,goniszewski_correlation_2016}.  The
-fitted \(f\) values for both systems are as small as 3.7\%-3.8\%,
-indicating the graphene layers are mostly complete. It is very
-surprising to find out that due to large discrepancy of wetting
-behavior on the 2D material and the underlying substrate, the measured
-contact angle change can be greatly influenced by the existence of
-minor defects in the 2D material. Our calculations show that extreme
-care should be taken to interpret the true doping-tunable wetting
-behavior of 2D materials.
-
-The doping-induced tuning of wetting on 2D materials opens a novel
-avenue for 2D-material-based liquid manipulating devices. Unlike
-conventional electrowetting on dielectric (EWOD) setup, no counter
-electrode is required in the liquid phase, ensuring simpler device
-design. Although Eq. \ref{eqn:Delta-Phi-exact} shows that the
-electrowetting effect of 2D material is only dependent on the surface
-charge \(\sigma_{\mathrm{2D}}\), practically it is more favorable to
-achieve the desired electrowetting by applying a smaller
-\(V_{\mathrm{2D}}\). A usual setup for electrostatic doping of 2D
-material involves the use of high-k dielectric or ionic gating
-\cite{Das_2008,Radisavljevic_2011,Xu_2011,Newaz_2012}, where the
-\(C_{\mathrm{d}}\) is comparable with \(C_{\mathrm{2D}}\). Therefore the
-contribution of \(C_{\mathrm{2D}}\) in Eq. \ref{eqn:doping-vm-2D} cannot
-be ignored. Combing Eqs. \ref{eqn:psi-L}, \ref{eqn:psi-2D} and
-\ref{eqn:doping-vm-2D}, we get:
-
-\begin{align}
-\label{eqn:dV-sigma-2D}
-\mathrm{d} V_{\mathrm{2D}} &= \left(\frac{1}{C_{\mathrm{d}}} +
-\frac{1}{C_{\mathrm{2D}}}\right) \mathrm{d}\sigma_{\mathrm{2D}} \\
-\label{eqn:dpsi-sigma-L}
-\mathrm{d} \psi_{\mathrm{2D}} &= -\left( \frac{1}{C_{\mathrm{H}}}
-+ \frac{1}{C_{\mathrm{L}}} \right) \mathrm{d}\sigma_{\mathrm{L}}
-\end{align}
-and by substituting \(\sigma_{\mathrm{2D}} = -\sigma_{\mathrm{L}}\), we derive the ratio between \(\psi_{\mathrm{2D}}\) and \(V_{\mathrm{2D}}\), named as \(\beta\):
-\begin{equation}
-\label{eqn:beta}
-\beta = \frac{\mathrm{d} \psi_{\mathrm{2D}}}{\mathrm{d}
-V_{\mathrm{2D}}} = \dfrac{\dfrac{1}{C_{\mathrm{L}}} +
-\dfrac{1}{C_{\mathrm{H}}}}{\dfrac{1}{C_{\mathrm{d}}} + \dfrac{1}{C_{\mathrm{2D}}}}
-\end{equation}
-at a certain \(c_{0}\), the larger \(\beta\) is, the higher tunability in
-wettability of the 2D material will be. On the device side, it can be
-achieved if both \(C_{\mathrm{d}}\) and \(C_{\mathrm{2D}}\) are
-larger. Increasing the value of \(C_{\mathrm{2D}}\) can be implemented
-by replacing graphene--a 2D semimetal, with a 2D semiconductor, such
-as TMDC \cite{tian_multiscale_2016}. Here we evaluate a
-2D-material-based electrowetting device consists of a 2 nm thick HfO\(_{\text{2}}\)
-dielectric layer with \(\epsilon_{\mathrm{d}}=24.0\), and an 2D material
-sheet selected from graphene, silicene, germanene, MoS\(_{\text{2}}\), MoTe\(_{\text{2}}\), WS\(_{\text{2}}\)
-and WTe\(_{\text{2}}\) (see Fig. \ref{fig:dcos-all-2D}(a)). The magnitude of \(\Delta
-\cos \theta\) as a function of \(V_{\mathrm{2D}}\) in devices based on
-different 2D materials is shown in Fig. \ref{fig:dcos-all-2D}(b).
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.95\linewidth]{../img/dcos-all-2D.pdf}
-\caption{\label{fig:dcos-all-2D}
-(a) Schematic illustration of the 2D-material-based electrowetting device. (b) \(\Delta\cos\theta\) as a function of \(V_{\mathrm{2D}}\) for selected 2D materials.}
-\end{figure}
-
-As expected in Eq. \ref{eqn:beta}, at the same \(V_{\mathrm{2D}}\) level,
-the 2D TMDC semiconductors (MoS\(_{\text{2}}\), MoTe\(_{\text{2}}\), WS\(_{\text{2}}\), WTe\(_{\text{2}}\)) exhibit a much
-higher response \(\Delta \cos \theta\) than 2D semimetals (silicene,
-germanene and graphene). We can briefly rank the voltage tunability of
-the selected 2D materials by their DOS: MoTe\(_{\text{2}}\) > MoS\(_{\text{2}}\) > WTe\(_{\text{2}}\) > WS\(_{\text{2}}\)
-> germanene > silicene > graphene. Notably, TMDCs can achieve a
-\(\Delta \Phi_{\mathrm{2D}}\) as high as 0.15 when
-\(V_{\mathrm{2D}}=\pm1.5\) V is applied, corresponding a contact angle
-decrease at the magnitude of 10\(^{\circ}\) when the intrinsic contact
-angle is ca. 90\(^{\circ}\).  A high-DOS 2D material further suppresses
-electrochemical reactions at the solid-liquid interface, as less
-electrochemical potential (i.e. the Fermi level \(E_{\mathrm{F}}\)) is
-required. We conclude that a 2D material with higher DOS can
-essentially reduced the voltage needed for doping, pushing
-liquid-phase 2D-material-based devices to a more operational regime.
-
-In conclusion, we propose a multiscale approach for modeling the
-doping-induced tunable wettability of 2D materials, by combining the
-reorientation effect of water molecules estimated by MD simulations,
-and the electrowetting effect calculated by a continuum model. Taking
-graphene as an example, we find that electrostatic interaction plays a
-major role at both scales for the graphene-water interface. We further
-show that, by considering the incomplete coverage of 2D material on
-the substrate, it is possible to evaluate the recent findings of
-doping-induced tuning of graphene's wettability with the proposed
-model. We find that minor surface incompleteness can cause great
-discrepancy in the measured value of interfacial wettability, and
-extreme care should be taken to interpret the observed
-electrowetting phenomena. In addition, we prove that a 2D material
-with higher density of states can essentially reduce the gating
-voltage in a 2D-material-based electrowetting device, and rank the
-tunability of the 2D materials as: MoTe\(_{\text{2}}\) > MoS\(_{\text{2}}\) > WTe\(_{\text{2}}\) > WS\(_{\text{2}}\) >
-germanene > silicene > graphene. Our multiscale analysis provides a
-comprehensive view of the wettability of 2D material interface, and we
-believe operational 2D-material-based liquid manipulating devices will
-be facilitated by the principles presented in this letter.
-\bibliography{ref}
 \end{document}

### 2017-06-01 writing/dcos_sigma.py

@@ -85,7 +85,7 @@ def plot_ph_dep(fig, MD=False):
                         facecolor="k",
                         edgecolor=None,))
     else:
-        ax.text(0, 0.10,
+        ax.text(-0.8, 0.10,
                 s=r"$c_{0}=10^{0}$~$10^{-7}$ mol$\cdot$L$^{-1}$",
                 ha="center",
                 va="center")
@@ -121,7 +121,7 @@ def plot_theta_2D(fig):
     fig.tight_layout(pad=0)
 
 if __name__ == "__main__":
-    fc = FigureCollection(pagesize=(4, 7),
+    fc = FigureCollection(pagesize=(3, 5.5),
                           figure_style="science",
                           col=1, row=9)
     # fc.fc_param["figure.lpad"] = 0.02
@@ -136,15 +136,15 @@ if __name__ == "__main__":
     fig3, num2 = fc.add_figure(loc=(0, 6, 1, 3), label=True)
     fig3.set_plot_func(plot_ph_dep, MD=True)
     org.figure(fc.save_all("../img/2d-ph-dependency+MD.pdf", outline=False),
-	       label="fig:res-EDL",
-	       caption=("(a) Scheme of the interface between the 2D material "
+               label="fig:res-EDL",
+               caption=("(a) Scheme of the interface between the 2D material "
                         "and the aqueous phase. "
                         r"(b) $(\Delta\cos\theta)^{\mathrm{EDL}}$ "
                         "as a function of "
                         r"$\sigma_{\mathrm{2D}}$ with varied solute concentrations. "
                         r"The concentration $c_{0}$ varies from "
                         r"$10^{0}$ to $10^{-7}$ mol$\cdot\mathrm{L}^{-1}$ "
-                        r"(c) Overall change of contact angle $(\cos \theta)^{\mathrm{Orien+EDL}}$ "
+                        r"(c) Overall change of contact angle $(\Delta \cos \theta)^{\mathrm{Orien+EDL}}$ "
                         "combining the orientation and EDL effects, "
                         "with varied solute concentrations as in (b)."),
-	       attributes=[("latex", ":width 0.65\linewidth")])
+               attributes=[("latex", ":width 0.5\linewidth")])

### 2017-06-01 writing/fit_program.py

@@ -130,22 +130,28 @@ def plot_fitting_f(fig):
                 xerr=n_err_esem, yerr=dcos_err_esem,
                          fmt="s", label="ESEM Data",)
     l_elw = ax.plot(n_elw, dcos_elw, "o", label="Electrowetting Data")
-    ax.text(x=-0.85, y=0.25, ha="left", size="medium",
+    ax.text(x=-0.85, y=0.25, ha="left", size="small",
             s= "".join((r"$f$=",
-	                "{:.3f}\n".format(f_elw),)
-	                ),
+                        "{:.3f}\n".format(f_elw),
+                        r"$\sigma_{0}$",
+                        "={:.1f}".format(sigma_i_elw*10),
+                        r"$\times 10^{12}$",
+                          r" $e\cdot$cm$^{-2}$",))
     )
     ax.plot(nn_elw, dd_elw + dcos_plt, "--", alpha=0.5, color=l_elw[0].get_color())
     ax.plot(nn_esem, dd_esem + dcos_plt, "--", alpha=0.5, color=l_esem[0].get_color())
 
-    ax.text(x=0.85, y=0.2, ha="left", size="medium",
+    ax.text(x=0.55, y=-0.04, ha="left", size="small",
             s= "".join((r"$f$=",
-	                "{:.3f}\n".format(f_esem),)
-	                ),
-    )
+                        "{:.3f}\n".format(f_esem),
+                        r"$\sigma_{0}$",
+                        "={:.1f}".format(sigma_i_esem*10),
+                        r"$\times 10^{12}$",
+                          r" $e\cdot$cm$^{-2}$",))
+                        )
     ax.set_xlabel(r"$\sigma_{\mathrm{2D}}$ ($10^{13}$ $e\cdot$cm$^{-2}$)")
     ax.set_ylabel(r"$\Delta\cos\theta$")
-    ax.legend(loc=0)
+    ax.legend(loc=0, frameon=True)
     ax.set_xlim(-2, 2)
     ax.set_ylim(-0.05, 0.5)
     fig.tight_layout()
@@ -156,9 +162,9 @@ fig = plt.figure(figsize=(4.0, 3.0))
 if __name__ == "__main__":
     plot_fitting_f(fig)
     org.figure(plt.savefig("../img/plot-fitting.pdf"),
-	       attributes=[("latex", ":width 0.95\linewidth")],
-	       label="fig:f-nc-exp",
-	       caption=("Theoretical and fitted experimental data of "
[…]

### 2017-06-01 writing/plot_change_adhesion.py

@@ -137,11 +137,11 @@ def plot_Phi_charge(fig, error=False):
     ax1 = fig.add_subplot(111)
     ax2 = ax1.twiny()           # For the charge
     # ax3 = ax1.twinx()           # For the surface tension
-    l_tot = ax1.plot(n_2D, potential_tot, 's',
+    l_tot = ax1.plot(n_2D, potential_tot, 's', markersize=5,
                      label=r"$\Delta \Phi_{\mathrm{Coul}} + \Delta \Phi_{\mathrm{LJ}}$")
-    l_vdw = ax1.plot(n_2D, vdW_tot, 's',
+    l_vdw = ax1.plot(n_2D, vdW_tot, 's', markersize=5,
              label=r"$\Delta \Phi_{\mathrm{LJ}}$")
-    l_cl = ax1.plot(n_2D, coulomb_tot, 's',
+    l_cl = ax1.plot(n_2D, coulomb_tot, 's', markersize=5,
                     label=r"$\Delta \Phi_{\mathrm{Coul}}$")
     if error is True:
         ax1.fill_between(sigma/10**13,
@@ -157,7 +157,7 @@ def plot_Phi_charge(fig, error=False):
     ax1.set_xlabel(r"$\sigma_{\mathrm{2D}}$ ($10^{13}$ $e\cdot$cm$^{-2}$)")
     ax1.set_ylabel(r"$\Delta \Phi$ (mJ$\cdot$m$^{-2}$)")
     ax1.legend(loc=0, frameon=True)
-    ax1.set_xlim(-4, 4)
+    # ax1.set_xlim(-4, 4)
     # ax1.set_ylim(-10, 15)
     # Change the second x axis
 
@@ -166,7 +166,7 @@ def plot_Phi_charge(fig, error=False):
     ax2.set_xticklabels(list(map(lambda s: "%.0f" % s, ax2_ticks*1000)))
     ax2.set_xlim(ax1.get_xlim())
     ax2.set_xlabel("$\sigma_{\mathrm{2D}}$ (10$^{-3}$ $e$/atom)")
-    fig.tight_layout(pad=0)
+    fig.tight_layout()
 
 def plot_fitting(fig):
     ax = fig.add_subplot(111)
@@ -214,10 +214,12 @@ def plot_fitting(fig):
 
 
 if __name__ == "__main__":
-    fig = plt.figure()
+    matplotlib.style.use("science")
+
[…]

### 2017-06-01 writing/plot_density.py

@@ -4,17 +4,20 @@ import matplotlib.pyplot as plt
 import scipy.constants as const
 import scipy
 import pycse.orgmode as org
+from scipy.interpolate import interp1d
 
-charge_per_atom = [-12, 0, 12]
+charge_per_atom = [-12, -6, 0, 6, 12]
+name = ["neg0.012", "neg0.006", "0.000", "0.006", "0.012"]
+label_name = ["-0.012", "-0.006", "0", "0.006", "0.012"]
 
 c_atom_to_sigma = lambda x: x*2/(2.465e-8**2*scipy.sin(scipy.pi/3))
-z_gr = 2.177
+z_gr = 1.980
 
-f_charge_base = "../data/MD/charge_int_%d.xvg"
-f_charge_water = "../data/_MD/charge_water_surf.xvg"
+f_charge_base = "../data/charge_int_{}_large2.xvg"
+f_charge_water = "../data/charge_int_water-surf.xvg"
 
-f_dens_base = "../data/MD/density_int_%d.xvg"
-f_dens_water = "../data/MD/density_water_surf.xvg"
+f_dens_base = "../data/density_int_{}_large2.xvg"
+f_dens_water = "../data/density_int_water-surf.xvg"
 
 charge_per_atom.sort()
 
@@ -26,33 +29,46 @@ d_water = numpy.genfromtxt(f_dens_water, delimiter=(12, 17), skip_header=19)
 def plot_den(fig, what="mass"):
     ax = fig.add_subplot(111)
     if what is "mass":
-        for c in charge_per_atom:
-            d_sys = numpy.genfromtxt(f_dens_base % c,
+        for index, c in enumerate(charge_per_atom):
+            d_sys = numpy.genfromtxt(f_dens_base.format(name[index]),
                                      delimiter=(12, 17), skip_header=19)
-            ax.plot(d_sys[:, 0] - z_gr,
-                    d_sys[:, 1], label=r"%d$\times10^{-3}$ $e$/atom" % (c))
-        ax.set_ylabel(r"$\rho_{\mathrm{w}}$ (kg$\cdot$m$^{-3}$)")
+            zz = numpy.linspace(d_sys[:, 0].min(), d_sys[:, 0].max(), 50000)
+            f_y = interp1d(d_sys[:, 0], d_sys[:, 1], kind="cubic")
+            yy = f_y(zz)
+            # ax.plot(d_sys[:, 0] - z_gr,
[…]

### 2017-06-01 writing/plot_density_detail.py

@@ -1,0 +1,74 @@
+import numpy, matplotlib
+matplotlib.use("Agg")
+import matplotlib.pyplot as plt
+import scipy.constants as const
+import scipy
+import pycse.orgmode as org
+from scipy.interpolate import interp1d
+
+charge_per_atom = [-12, -6, -5, -3,  0, 3, 6, 12]
+name = ["neg0.012", "neg0.006", "neg0.005", "neg0.003", "0.000", "0.003", "0.006", "0.012"]
+label_name = ["-0.012", "-0.006", "-0.005", "-0.003", "0", "0.003", "0.006", "0.012"]
+
+c_atom_to_sigma = lambda x: x*2/(2.465e-8**2*scipy.sin(scipy.pi/3))
+z_gr = 1.980
+
+f_charge_base = "../data/charge_int_{}_large2.xvg"
+f_charge_water = "../data/charge_int_water-surf.xvg"
+
+f_dens_base = "../data/density_int_{}_large2.xvg"
+f_dens_water = "../data/density_int_water-surf.xvg"
+
+charge_per_atom.sort()
+
+c_water = numpy.genfromtxt(f_charge_water, delimiter=(12, 17), skip_header=19)
+d_water = numpy.genfromtxt(f_dens_water, delimiter=(12, 17), skip_header=19)
+
+# ax1.plot(c_water[:, 0] - z_gr, c_water[:, 1], label="Water Only")
+
+def plot_den(fig, what="mass"):
+    ax = fig.add_subplot(111)
+    if what is "mass":
+        for index, c in enumerate(charge_per_atom):
+            d_sys = numpy.genfromtxt(f_dens_base.format(name[index]),
+                                     delimiter=(12, 17), skip_header=19)
+            zz = numpy.linspace(d_sys[:, 0].min(), d_sys[:, 0].max(), 50000)
+            f_y = interp1d(d_sys[:, 0], d_sys[:, 1], kind="cubic")
+            yy = f_y(zz)
+            # ax.plot(d_sys[:, 0] - z_gr,
+                    # d_sys[:, 1], label=r"%d$\times10^{-3}$ $e$/atom" % (c))
+            ax.plot(zz - z_gr,
+                    yy, label=r"%s $e$/atom" % (label_name[index]))
+        ax.set_ylabel(r"$\rho_{\mathrm{L}}$ (kg$\cdot$m$^{-3}$)")
+        ax.set_xlabel(r"$z$ (nm)")
[…]

### 2017-07-22 writing/paper-Tian-gr-wetting.tex
clean up data files

@@
-% Created 2017-06-01 Thu 19:09
+% Created 2017-07-22 Sat 15:09
 % Intended LaTeX compiler: pdflatex
-\documentclass[journal=jacsat,manuscript=article,email=true]{achemso}
+\documentclass[journal=jacsat,manuscript=article,email=true,hyperref=true,keywords=true]{achemso}
  \usepackage{minted}
@@
 \usepackage{fontspec}
-\keywords{Two-dimensional materials, doping, wettability, multiscale analysis, MD Simulation, eletrical double layer}
 \author{Tian Tian}
@@
 \author{Siyu Li}
-\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy & Environment, Southeast University, Nanjing, Jiangsu 210096, China}
+\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
 \author{Lingling Zhao}
-\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy & Environment, Southeast University, Nanjing, Jiangsu 210096, China}
+\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
 \author{Elton J. G. Santos}
@@
 \affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
+\keywords{two-dimensional materials, doping, wettability, multiscale analysis, MD Simulation, electrical double layer}
 \date{}
@@
 \begin{document}
+
+\begin{tocentry}
+\includegraphics[width=9cm]{../img/TOC.pdf}
+\end{tocentry}
 
@@
   as well as the molecular packing behavior on a 2D material-coated surface, 
-  essentially faciliating the interfacial engineering of 2D materials.
+  essentially facilitating the interfacial engineering of 2D materials.
 \end{abstract}
-# \maketitle
+% \textbf{Keywords}
+% two-dimensional materials, doping, wettability, multiscale analysis, molecular dynamics simulation, electrical double layer
+ \maketitle
 
@@
 \section{Introduction}
-\label{sec:org435dbee}
+\label{sec:org828e535}
 
@@
 quantum-confined properties
-\cite{Novoselov_2005,Mas_Ballest__2011,Novoselov_2016}.  Recent progress in the scalable production of large-area 2D
-materials \cite{Boott_2015,Li_2016} has paved the way for the
-applications of functional surfaces and ultrathin membranes
+\cite{Novoselov_2005,Mas_Ballest__2011,Novoselov_2016}.  Recent progress
+in the scalable production of large-area 2D materials
+\cite{Boott_2015,Li_2016} has paved the way for the applications of
+functional surfaces and ultrathin membranes
 \cite{Prasai_2012,Feng_2016,Rafiee_2010,Yin_2014,Surwade_2015,Hern_ndez_2013}.
@@
 silicene) and 2D semiconductors (e.g., transition metal
-dichalcogenides (TMDCs)) possess low density of states (DOSs) around
+dichalcogenides (TMDCs)) possess low density of states (DOS) around
 the intrinsic Fermi level (\(E_{\mathrm{F}}\)), such that the effect of
@@
 the change of interfacial tension between liquid and a sheet of
-monolayer 2D material. Multiscale physical phenomena are
-considered. At the atomistic scale, we formulate the dependence of
-surface energy of a 2D material on the doping density using the
-quantum capacitance (QC) calculated by the density functional theory
-(DFT). Next, the surface-charge-induced reorientation of liquid
-molecules adjacent to the interface is associated with an N-body
-system, which is resolved by molecular dynamics (MD) simulations,
-allowing quantification of the interfacial tension in the absence of
-electrolytes in liquid. The effect of the electrical double layer
-(EDL) induced by the electrostatic interactions between the 2D
-material surface charges and the ionic species in liquid, is then
-addressed at the continuum level. Practical considerations, such as
-the defect density and the surface contamination are also taken into
-account to provide a comprehensive understanding of the
-phenomena. Finally, we examine and validate our theory by comparing
-with the contact angle changes reported in the electrowetting and the
-substrate-induced doping experiments.
+monolayer 2D material. Multiscale physical phenomena are considered,
+as shown in Figure \ref{fig:scheme-method}. At the atomistic scale, we
+formulate the dependence of surface energy of a 2D material on the
+doping density using the quantum capacitance (QC) calculated by the
+density functional theory (DFT). Next, the surface-charge-induced
+reorientation of liquid molecules adjacent to the interface is
+associated with an N-body system, which is resolved by molecular
+dynamics (MD) simulations, allowing quantification of the interfacial
+tension in the absence of electrolytes in liquid. The effect of the
+electrical double layer (EDL) induced by the electrostatic
+interactions between the 2D material surface charges and the ionic
+species in liquid, is then addressed at the continuum level. Practical
+considerations, such as the defect density and the surface
+contamination are also taken into account to provide a comprehensive
+understanding of the phenomena. Finally, we examine and validate our
+theory by comparing with the contact angle changes reported in the
+electrowetting and the substrate-induced doping experiments.
 
 \section{Results and Discussions}
-\label{sec:org66b0b42}
+\label{sec:orgc095477}
 
 \subsection{Surface Energy of Doped 2D Materials}
-\label{sec:org87cc68c}
+\label{sec:org28f87f6}
 
@@
 depicts the surface tension change of a 2D material at the
-quantum-mechanical level. We have calculated the DOSs as a function of
+quantum-mechanical level. We have calculated the DOS as a function of
 \(E_{\mathrm{F}}\) for a variety of 2D materials using the density
@@
 \subsection{Reorientation of Liquid Molecules}
-\label{sec:org188528c}
+\label{sec:org8d3c56f}
 
@@
 \gamma_{\mathrm{2D-L}}^{\mathrm{EDL}}\) correspond to the contributions
-from the reorientation and the EDL effects, respectively, as
-schematically illustrated in Figure \ref{fig:scheme-method}. We also
-assume that \(\Delta \gamma_{\mathrm{2D-L}}^{Orien}\) is independent of
+from the reorientation and the EDL effects, respectively. We also
+assume that \(\Delta \gamma_{\mathrm{2D-L}}^{\mathrm{Orien}}\) is independent of
 the electrolyte concentration, since the concentration of liquid
@@
 \cite{Bussi_2007}. All simulations were carried out under the NVT
-ensemble.
+ensemble, and the equations of motion of water molecules were
+integrated over a range of 20 ns with 10\(^{\text{7}}\) steps.
 
@@
 and the other surface exposing to vacuum (GL) (see Figure
-\ref{fig:MD-res}(a) and \ref{fig:MD-res}(b)) . Periodic boundary
+\ref{fig:MD-res}(a) and \ref{fig:MD-res}(b)). Periodic boundary
 conditions are used in all three directions of the simulation boxes in
@@
 that the time-averaged dipole moment for the water molecules at the
-water-vacuum interface is approximately zero (see Supporting Information
+water-vacuum interface approaches zero (see Supporting Information
 Figure S1).  One can show that \(E_{\mathrm{GL}} - E_{\mathrm{L}} =
@@
 
-Figure \ref{fig:MD-res}(c) shows the values of \(\Delta \Phi\), and its
-contributions from the Lennard-Jones (\(\Delta \Phi_{\mathrm{LJ}}\)) and
-Coulombic interactions (\(\Delta \Phi_{\mathrm{Coul}}\)), as functions
-of \(\sigma_{\mathrm{2D}}\). We note that the change of adhesion energy
-in the doped graphene system is dominated by the Coulombic
-interaction. When the doping level of graphene is \(\pm 4 \times
-10^{13}\ e\cdot \mathrm{cm}^{-2}\), the Coulombic interaction causes a
-decrease in the adhesion energy of -10\textasciitilde{}-15 mJ\(\cdot \mathrm{m}^{-2}\),
-while the vdW interaction, on the other hand, causes a slight increase
-in the adhesion energy by less than 5 mJ\(\cdot \mathrm{m}^{-2}\). In
-other words, concerning the reorientation of water molecules at high
-doping levels, the Coulombic interaction favors the decrease of
-\(\gamma_{\mathrm{2D-L}}\), and thus the contact angle \(\theta\), while
-the vdW interaction slightly increases \(\gamma_{\mathrm{2D-L}}\) and
-\(\theta\). We shall note that due to the highly polar nature of water
-molecules, the average inter-molecular equilibrium distance in the
-absence of external electric field is shorter than the Lennard-Jones
-equilibrium distance. Increasing the doping density of the graphene
-sheet essentially enhances the electrostatic attractions between
-graphene and water molecules and further decreases the inter-molecular
-equilibrium distance, as reflected from the red shifts of the first
-peaks in Figure \ref{fig:MD-res}(d) for the two charged graphene cases
-compared to the charge-neutral case, which eventually leads to a
-slight increase in .  The plot of \(\Delta \Phi\) as a function of
-\(\sigma_{\mathrm{2D}}\) in Figure \ref{fig:MD-res}(b) shows an apparent
-asymmetric shape. This is can be further revealed from the
+Figure \ref{fig:MD-res}(c) shows the values of \(\Delta \Phi\), and
+its contributions from the Lennard-Jones (\(\Delta \Phi_{\mathrm{LJ}}\))
+and Coulombic interactions (\(\Delta \Phi_{\mathrm{Coul}}\)), as
+functions of \(\sigma_{\mathrm{2D}}\). We note that the change of
+adhesion energy in the doped graphene system is dominated by the
+Coulombic interaction. When the doping level of graphene is \(\pm 4
+\times 10^{13}\ e\cdot \mathrm{cm}^{-2}\), the Coulombic interaction
+causes a decrease in the adhesion energy of \textasciitilde{} -15 mJ\(\cdot
+\mathrm{m}^{-2}\), while the vdW interaction, on the other hand, causes
+a slight increase in the adhesion energy by less than 5 mJ\(\cdot
+\mathrm{m}^{-2}\). In other words, concerning the reorientation of
+water molecules at large doping levels, the Coulombic interaction
+favors the decrease of \(\gamma_{\mathrm{2D-L}}\), and thus the contact
+angle \(\theta\), while the vdW interaction slightly increases
+\(\gamma_{\mathrm{2D-L}}\) and \(\theta\). We shall note that due to the
+highly polar nature of water molecules, the average inter-molecular
+equilibrium distance in the absence of external electric field
+(\(r_{\mathrm{O-O}}=2.75\ \mathrm{\AA}\)) is shorter than the
+Lennard-Jones equilibrium distance (\(r_{\mathrm{O-O}}=3.16\
+\mathrm{\AA}\)) \cite{Mark_2001}. Increasing the doping density of the
+graphene sheet essentially enhances the Coulombic attractions between
+graphene and water molecules, further reducing the inter-molecular
+equilibrium distance, as seen in Figure S2(a), the distance between
+the first water layer and graphene (calculated from maximal
+\(\rho_{\mathrm{L}}\) from Figure \ref{fig:MD-res}(d)) slightly decreases
+in doped graphene systems, compared with the charge-neutral system,
+which eventually leads to a slight increase in \(\Delta
+\Phi_{\mathrm{LJ}}\).  The plot of \(\Delta \Phi\) as a function of
+\(\sigma_{\mathrm{2D}}\) in Figure \ref{fig:MD-res}(c) shows an apparent
+asymmetric behavior. This can be further revealed from the
 \emph{z}-dependent local molecular density \(\rho_{\mathrm{L}}\) and charge
 density \(\delta_{\mathrm{L}}\) profiles of the water molecules, as
-shown in Figure \ref{fig:MD-res}(d) and \ref{fig:MD-res}(c),
+shown in Figure \ref{fig:MD-res}(d) and \ref{fig:MD-res}(e),
 respectively. The molecular density of the first water layer adjacent
@@
 n-doped (\(\sigma_{\mathrm{2D}}=-0.012\ e\cdot \mathrm{cm}^{-2}\), or
-equivalently 4.56 \textit{e}/atom) compared with the case of
+equivalently -4.56 \textit{e}/atom) compared with the case of
 charge-neutral graphene, indicating the polarity-dependent adsorption
-of water molecules on graphene. Similar trend can also be observed in
-the \(\delta_{\mathrm{L}}\) profiles. Interestingly, \(\Delta \Phi\)
-exhibits positive Coulombic contribution for slightly n-doped
-graphene, when \(\sigma_{\mathrm{2D}} \approx -2\times10^{13}\ e\cdot
-\mathrm{cm}^{-2}\), indicating that the reorientation of interfacial
-water molecules by small negative charges on graphene helps minimizing
-the Coulombic interactions.
-\begin{center}
-\fbox{
-\begin{minipage}[c]{.8\linewidth}
-\textbf{\textsf{\textsc{TODO}}} Explanation of the positive part of \(\Delta \Phi\) when \(\sigma_{\mathrm{2D}} \approx -2\) ?
+of water molecules on graphene: lighter H atoms prefer to adsorb onto
+n-doped graphene electrostatically. Similar trend can also be observed
+in the \(\delta_{\mathrm{L}}\) (Figure \ref{fig:MD-res}(e))and water
+dipole orientation \(\cos \mu\) (Figure S1) profiles, both
+suggesting that water orientation depends strongly on
+\(\sigma_{\mathrm{2D}}\): more negative \(\sigma_{\mathrm{2D}}\) tends
+to orient the water dipoles more towards the 2D interface, reflected
+by the more positive charge densities due to first-layer H atoms, and
+the more negative \(\cos \mu\) values. Interestingly, the \(\Delta
+\Phi_{\mathrm{Coul}}\) exhibits small positive contribution for slightly
+n-doped graphene, when \(\sigma_{\mathrm{2D}} \approx -2\times10^{13}\
+e\cdot \mathrm{cm}^{-2}\) or equivalently -0.76 \textit{e}/atom,
+indicating that the reorientation of interfacial water molecules by
+small negative charges on graphene helps minimizing the Coulombic
+interactions. The trend observed in hydrogen-bond densities (see
+Figure S3) also matches those observed in \(\rho_{\mathrm{L}}\),
+\(\delta_{\mathrm{L}}\) and \(\cos \mu\) profiles.
 
-\end{minipage}
-}
-\end{center}
-Although the MD simulation results show the Coulombic interaction
-between the doped graphene and water molecules dominate the
-reorientation effect, such conclusion may not be readily applied to
-other types of 2D materials. For 2D semimetal systems (silicene and
-germanene), the intensity of Coulombic interactions may vary due to
-the mismatch among the lattice constants. On the other hand, for the
-2D semiconductors such as the TMDCs, in which their
-\(\gamma_{\mathrm{2D-L}}\) are already largely determined by the
-Coulombic interactions in the intrinsic case
+Finally, we believe that the asymmetric behavior of \(\Delta
+\Phi_{\mathrm{Coul}}\) with respect to \(\sigma_{\mathrm{2D}}\) is due to
+the nonlinear decrease in \(\delta_{\mathrm{L}}\) of the first water
+layer, when graphene becomes more n-doped (see Figure S2(d)).  As a
+general trend, \(\delta_{\mathrm{L}}\) of the first water layer
+increases when \(\sigma_{\mathrm{2D}}\) becomes more negative, due to
+the attraction of H atoms to the graphene surface. However we observe
+a decrease of \(\delta_{\mathrm{L}}\) when \(\sigma_{\mathrm{2D}}\)
+ranges from -0.001 to -0.006 \(e \cdot \mathrm{cm}^{-2}\) (see Figure
+S2(d)), which could be a combined result of the graphene-water
+Coulombic interactions and intermolecular hydrogen bonding. We also
+notice a nonlinear behavior in the \(\rho_{\mathrm{L}}\) of the first
+water layer: when \(\sigma_{\mathrm{2D}}\) becomes more negative, the
+interatomic distance \(r_{\mathrm{C-O}}\) between graphene C and water O
+atoms will increase due to Coulombic repulsion.  Note that the
+increased Coulombic repulsion energy for C−O pairs from more negative
+\(\sigma_{\mathrm{2D}}\) values is balanced by the increased vdW
+attractions between C−O pairs when \(r_{\mathrm{C-O}}\) increases, which
+eventually prevents the reduction of the first water layer density at
+an equilibrium C-O distance, as seen at \(\sigma_{\mathrm{2D}} < -0.01\
+e \cdot \mathrm{cm}^{-2}\) (Figure S2(b)). Here we propose a simple
+capacitor-like model, considering the contributions from
+\(\delta_{\mathrm{L}}\) of the first water layer of the first water
+layer and \(\sigma_{\mathrm{2D}}\) to the interfacial Coulombic energy
+\(\Phi_{\mathrm{Coul}}^{\mathrm{int}}\) (see the discussion in
+Supporting Information and Figure S4). We show that in the n-doped graphene system
+the charge density of the first water layer has a major contribution
+to \(\Delta \Phi_{\mathrm{Coul}}\). The nonlinear behavior of
+\(\delta_{\mathrm{L}}\) at low n-doping level is responsible for the
+shift of maximum of the \(\Delta
+\Phi_{\mathrm{Coul}}-\sigma_{\mathrm{2D}}\) curve. The analysis further
+indicates the importance of interfacial water configuration in
+determining the change of the interaction potentials.
+
+Although the MD simulation results show that the Coulombic
+interactions between the doped graphene and water molecules dominate
+the reorientation effect, such conclusion may not be readily applied
+to other types of 2D materials, as the intensity of vdW interactions
+and surface charge polarization can vary greatly. First, the
+microscopic vdW and Coulombic interactions on 2D materials depend on
+the lattice constant and atomic density. In addition, for homoatomic
+2D materials such as graphene, silicene, germanene and phosphorene,
+their surface charge polarization is negligible compared to
+heteroatomic 2D materials, for instance TMDC. It has been shown that,
+for TMDCs, the value of \(\gamma_{\mathrm{2D-L}}\) is already largely
+determined by the Coulombic interactions in the charge-neutral systems
 \cite{Govind_Rajan_2016,Chow_2015}. Therefore we anticipate that
 case-by-case studies and DFT calculations which deal with the
-post-doping charge redistribution, might be required.
-\begin{center}
-\fbox{
-\begin{minipage}[c]{.8\linewidth}
-\textbf{\textsf{\textsc{TODO}}} Try find other references?
-
-\end{minipage}
-}
-\end{center}
+post-doping charge redistribution, might be required, as shown by
+several previous studies
+\cite{Sresht_2015,Govind_Rajan_2016,Sresht_2017}.
 
 \subsection{Electrical Double Layer Effect}
-\label{sec:org0491aea}
+\label{sec:orgc5ae7c8}
 
@@
 that \(c_{0}=10^{-7}\) mol\(\cdot \mathrm{L}^{-1}\) corresponds to the
-pure water system. We find that the contact angle change is
-stronger in a more diluted electrolyte solution, resulting from an
-increase in Debye screening length \(\lambda_{\mathrm{D}}\), which
-in turn decreases both \(C_{\mathrm{GC}}\) and \(C_{\mathrm{DH}}\). This
-is distinct from the that in the typical electrowetting experiment on
-a dielectric layer, in which \(C_{\mathrm{YL}}\) is governed by the
-capacitance of the dielectric layer, so the contact angle change is
-almost independent of the electrolyte concentration
+pure water system. We find that the contact angle change is stronger
+in a more diluted electrolyte solution, resulting from an increase in
+Debye screening length \(\lambda_{\mathrm{D}}\), which in turn decreases
+both \(C_{\mathrm{GC}}\) and \(C_{\mathrm{DH}}\). This is distinct from
+the that in the typical electrowetting experiment on a dielectric
+layer, in which \(C_{\mathrm{YL}}\) is governed by the capacitance of
+the dielectric layer, so the contact angle change is almost
+independent of the electrolyte concentration
 \cite{Mugele_2005}. Moreover, within the range of \(\sigma_{\mathrm{2D}}\)
@@
 \theta)^{\mathrm{Orien + EDL}}\) due to the doping effect is shown in
-Figure \ref{fig:res-EDL}(c). The MD-calculated \(\Delta \Phi\) as
-a function of \(\sigma_{\mathrm{2D}}\) is fitted by a third-order
-polynomial function (see Supporting Information Figure S3).  We find
-that the reorientation effect is more predominant than the EDL effect,
-therefore the overall change of contact angle is less dependent on the
-solute concentration, compared with Figure \ref{fig:res-EDL}(b).
+Figure \ref{fig:res-EDL}(c). We separately fit the \(\Delta
+\Phi_{\mathrm{LJ}}\) and \(\Delta \Phi_{\mathrm{Coul}}\) from the
+reorientation effect as functions of \(\sigma_{\mathrm{2D}}\) in n- and
+p-doped regimes, respectively (see Figure S5), and use the fitting
+results to construct the \(\Delta \Phi-\sigma_{\mathrm{2D}}\)
+relation. We find that the reorientation effect is more predominant
+than the EDL effect, therefore the overall change of contact angle is
+less dependent on the solute concentration, compared with Figure
+\ref{fig:res-EDL}(b).
 
 Together with the reorientation effect, the calculated \(\Delta \cos
-\theta\) change only reaches 0.06\textasciitilde{}0.08, corresponding to a maximum
-contact angle decrease of 3.5\textasciitilde{}4.5\(^{\circ}\), for
+\theta\) change only reaches 0.06 \textasciitilde{} 0.08, corresponding to a maximum
+contact angle decrease of 3.5 \textasciitilde{} 4.5\(^{\circ}\), for
 \(\sigma_{\mathrm{2D}}=\pm1\times10^{13}\ e\cdot \mathrm{cm}^{-2}\),
-
 which is is a typical range for both the electrostatic gating
@@
 \subsection{Practical Considerations}
-\label{sec:org80c83d8}
+\label{sec:orgeba1656}
 
@@
 \section{Conclusion}
-\label{sec:org333a0f3}
+\label{sec:org258c77f}
 
@@
 
+\begin{acknowledgement}
+T.T and C.-J. S. are grateful for the financial support from the ETH startup funding.
+S.L. would like to acknowledge the startup funding from the
+Energy and Materials Initiative at the Florida State University. S.L. and L.Z. would 
+like to acknowledge funding from the National Natural Science Foundation of China 
+(Grant No. 51106027).
+\end{acknowledgement}
+
+\begin{suppinfo}
+Additional results for the MD simulation and analysis of nonlinear
+behavior of interfacial Coulombic interactions in charged
+graphene-water system.
+\end{suppinfo}
+
 \bibliography{ref}
@@
 \section{Figures}
-\label{sec:org0a7d2b4}
+\label{sec:orgb7fbb04}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.95\linewidth]{/Users/tiantian/polybox/Research/8-graphene-electrowetting/img/scheme-methods.pdf}
+\caption{\label{fig:scheme-method}
+Scheme of the multiscale approach for modeling the doping-induced wettability tuning of 2D materials.}
+\end{figure}
 
@@
 \centering
-\includegraphics[width=0.95\linewidth]{../img/scheme-methods.png}
-\caption{\label{fig:scheme-method}
-Scheme of the multiscale approach for modeling the doping-induced wettability tuning of 2D materials.}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
 \includegraphics[width=0.9\linewidth]{../img/fig-pot-dens.pdf}
 \caption{\label{fig:MD-res}
-Geometry of the periodic MD simulation box for (a) water molecules only and (b) water-graphene systems.(c) Change of total adhesion energy \(\Delta\Phi\), and its partial contributionsfrom Lennard-Jones interaction \(\Delta\Phi_{\mathrm{LJ}}\) and Coulombic interaction \(\Delta\Phi_{\mathrm{CL}}\), as a function of \(\sigma_{\mathrm{2D}}\).
-10\(^{\text{-3}}\) \$e\$/atom corresponds to a charge density of \(3.80 \times 10^{12}\ e \cdot \mathrm{cm}^{-2}\).
-(d) Local density \(\rho_{\mathrm{L}}\) (e) local charge density \(\delta_{\mathrm{L}}\) of water molecules as a function of distance \(z\) from graphene surface.}
+Geometry of the periodic MD simulation box for (a) water molecules only and (b) water-graphene systems.
+(c) Change of total adhesion energy \(\Delta\Phi\), and its partial contributionsfrom Lennard-Jones  \(\Delta\Phi_{\mathrm{LJ}}\) and Coulombic  \(\Delta\Phi_{\mathrm{Coul}}\) interactions, as a function of \(\sigma_{\mathrm{2D}}\).
+The filled regions indicate the error margin of calculation.
+\(10^{-3}\) \textit{e}/atom corresponds to a charge density of \(3.80 \times 10^{12}\ e \cdot \mathrm{cm}^{-2}\).
+(d) and (e) are the local density \(\rho_{\mathrm{L}}\) and local charge density \(\delta_{\mathrm{L}}\) of water molecules as a function of distance \(z\) from graphene surface, respectively.}
 \end{figure}

### 2017-07-22 writing/supporting_information.tex
clean up data files

@@
-% Created 2017-05-04 Thu 21:33
+xf% Created 2017-07-22 Sat 14:57
 % Intended LaTeX compiler: pdflatex
@@
 \affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
+\author{Siyu Li}
+\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
+\author{Lingling Zhao}
+\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
 \author{Elton J. G. Santos}
@@
 \affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
+\keywords{two-dimensional materials, doping, wettability, multiscale analysis, MD Simulation, electrical double layer}
 \date{}
-\title{Wettability of Doped Two-Dimensional Materials}
+\title{Multiscale Understanding the Wettability of Doped Two-Dimensional Materials}
 \begin{document}
@@
 \section{Figures}
-\label{sec:org176b821}
+\label{sec:orgf1e64ec}
 \subsection{Dipole Orientation Profiles of MD Simulations}
-\label{sec:org3abd37b}
+\label{sec:org7a31239}
 \begin{figure}[htbp]
@@
 Dipole orientation \(\cos \mu\) as a function of \(z\) in MD simulations of different systems (L, and GL with varied graphene doping densities).
-The orientation at the water-vacuum interface (\$z\$=20 nm) is invariable in all cases, indicating a minimal effect of the long range Coulombic interaction on the selected interface.}
+The orientation at the water-vacuum interface (\(z=20\) nm) is invariable in all cases, indicating a minimal effect of the long range Coulombic interaction on the selected interface.}
 \end{figure}
@@
 \newpage{}
+
+\subsection{Properties of First Water Layer Adjacent to Charged Graphene Surface}
+\label{sec:orga56cc18}
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=.9\linewidth]{../img/SI_prop_1st_layer.pdf}
+\caption{\label{fig-SI-1st}
+Properties of the first water layer adjacent to the charged graphene surface.
+The following quantities are plotted as a function of \(\sigma_{\mathrm{2D}}\): (a) z-position of the first water layer with maximal value of \(\rho_{\mathrm{L}}\).
+(b) maximal \(\rho_{\mathrm{L}}\) of the first water layer.
+(c) z-position of the first water layer with maximal value of \(\delta_{\mathrm{L}}\).
+and (d) maximal \(\delta_{\mathrm{L}}\) of the first water layer.}
+\end{figure}
+\newpage{}
+
 \subsection{Hydrogen Bond Profiles of MD Simulations}
-\label{sec:orge06c9b9}
+\label{sec:orgd258855}
 
@@
 \caption{\label{fig-H-bond}
-Hydrogen bond strength as a function of \(z\) in MD simulations of various conditions (L, GL with graphene doping densities of -0.012, 0 and 0.012 \$e\$/atom).}
+Hydrogen bond density (\(\rho_{\mathrm{HB}}\)) as a function of \(z\) in MD simulations of various conditions (L, GL with graphene doping densities of -0.012, 0 and 0.012  \textit{e}/atom).}
 \end{figure}
 
-\begin{center}
-\fbox{
-\begin{minipage}[c]{.8\linewidth}
-\textbf{\textsf{\textsc{TODO}}} Ask Prof. Lin for unit and explanation of H-Bond result
+\newpage{}
 
-\end{minipage}
-}
-\end{center}
-\newpage{}
-\subsection{Fitting of the \(\Delta \Phi\) - \(\sigma_{\mathrm{2D}}\) Data in MD Simulations}
-\label{sec:orgb2e4751}
+\subsection{Explanation for Shift of \(\Delta \Phi_{\mathrm{Coul}}\) Maximum from Charge Neutral State}
+\label{sec:orgf365dc0}
+
+As can be seen in Figure 3(c) in the main text, the maximum of \(\Delta
+\Phi_{\mathrm{Coul}}\) as function of \(\sigma_{\mathrm{2D}}\) shifts
+from charge neutral state (\(\sigma_{\mathrm{2D}} = 0\)) to slightly
+n-doped region. This behavior can be explained by the contribution
+from the interfacial charge density to the Coulombic interactions (Figure \ref{fig-SI-mode}(a)).
+Assuming that the interfacial charge density per unit area of the
+water layer \(\sigma_{\mathrm{L}}\) is approximated by
+\(\sigma_{\mathrm{L}}=\delta_{\mathrm{L}} \cdot t_{1}\), where \(t_{1}\)
+is the thickness of the 1st water layer (\textasciitilde{}2.8 \AA{}). The interfacial
+Coulombic potential caused by the 1st charged layer is then:
+\begin{equation}
+\label{eq:1}
+\begin{aligned}
+\Phi_{\mathrm{Coul}}^{\mathrm{int}} &= \frac{\sigma_{\mathrm{2D}} \sigma_{\mathrm{L}}}{2C_{\mathrm{int}}} \\
+                                           &= \frac{\sigma_{\mathrm{2D}} \delta_{\mathrm{L}} t_{1} d_{1}}{2\epsilon_{\mathrm{int}}}
+\end{aligned}
+\end{equation}
+where \(C_{\mathrm{int}}=\epsilon_{\mathrm{int}}/d_{1}\) is the
+geometric capacitance of the interfacial void, \(\epsilon_{1}\) and
+\(d_{1}\) are the permittivity and thickness of the interfacial void. We
+assume that the interfacial dielectric constant
+\(\epsilon_{\mathrm{int}} = 20 \epsilon_{0}\)
+\cite{conway_dielectric_1951}, and take the value of \(d_{1}\) from the
+value of the most probable charge distribution distance \(z_{1}\) from
+Figure \ref{fig-SI-1st}(c). The comparison between the \(\Delta
+\Phi_{\mathrm{Coul}}\) from MD results and the proposed model can be
+seen in Figure \ref{fig-SI-mode}(b). The degree of Coulombic
+interactions from the model is close to that of the MD results,
+indicating that the decrease of interaction potential of the
+graphene-water system is mainly determined by the interfacial charge
+distribution. The result predicted by the model also shows a shifted
+maximum of \(\Delta \Phi_{\mathrm{Coul}}\), well corresponding with the
+MD results. Such asymmetric behavior is further ascribed to the
+decrease of \(\delta_{\mathrm{L}}\) when graphene is slightly n-doped
+(see Figure \ref{fig-SI-1st}(d)), as a combined result of the Coulombic
+interaction and hydrogen bonding. Note that in the p-doped regime, the
+model-predicted \(\Delta \Phi_{\mathrm{Coul}}\) value differs from the
+MD results, suggesting that the contribution from the subsequent
+layers are important.
+
 \begin{figure}[htbp]
 \centering
-\includegraphics[width=0.85\linewidth]{../img/e-Phi-fitting.pdf}
+\includegraphics[width=0.95\linewidth]{../img/SI_model.pdf}
+\caption{\label{fig-SI-mode}
+Simple model for the asymmetric behavior of \(\Delta \Phi_{\mathrm{Coul}}\) as a function of \(\sigma_{\mathrm{2D}}\).
+(a) Proposed orientation of first layer water molecules on n- and p-doped graphene surface.
+(b) Comparison between the \(\Delta \Phi_{\mathrm{Coul}}\) values calculated by MD simulation and the proposed model.
+The results obtained by the simple capacitance model shows similar shift of \(\Delta \Phi_{\mathrm{2D}}\) maximum.}
+\end{figure}
+
+\newpage{}
+
+\subsection{Fitting of the \(\Delta \Phi\) - \(\sigma_{\mathrm{2D}}\) Data in MD Simulations}
+\label{sec:org00f40dc}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.85\linewidth]{../img/e-Phi_vdw-fitting.pdf}
 \caption{\label{fig-SI-fitting}
-Fitting of \(\Delta \Phi\) - \(\sigma_{\mathrm{2D}}\) data from MD simulations with different polynomial functions. The 3rd degree polynomial function is chosen as the best fitting model.}
+Best fitting  results of \(\Delta \Phi_{\mathrm{LJ}}\) and \(\Delta \Phi_{\mathrm{Coul}}\) as functions of \(\sigma_{\mathrm{2D}}\) for n- and p-doped graphene-water systems.
+Total potential change \(\Delta \Phi\) is fitted by combining the fitting results of LJ and Coulombic potentials}
 \end{figure}
+
+\newpage{}
+
+\bibliography{ref}
 \end{document}

### 2017-07-22 data/plot_E.py

@@ -1,0 +1,225 @@
+import numpy
+import scipy
+import scipy.constants as const
+import matplotlib
+matplotlib.use("Agg")
+import matplotlib.pyplot as plt
+import pycse.orgmode as org
+from copy import copy
+
+charge_per_atom = [0, 0.001, 0.002, 0.003, 0.004, 0.005, 0.006, 0.008, 0.010, 0.012]
+
+c_atom_to_sigma = lambda x: x*2/(2.465e-8**2*scipy.sin(scipy.pi/3))
+
+def read_xvg_energy(filename):
+    data = {}
+    with open(filename) as f:
+        s_tmp = ""
+        s = f.readline()
+        while s.startswith("-") is not True:
+            s_tmp = s
+            s = f.readline()
+        attrs = s_tmp.strip().split()  # Attributes of columns
+        s = f.readline()
+        while len(s) > 0:
+            # print(s)
+            name = ""
+            i = 0
+            s = s.split()
+            while not s[i][0].isdecimal() and not s[i][0] == "-":
+                name += s[i]
+                i += 1
+            d_dic = {}
+            for att in attrs[1:]:
+                d_dic[att] = float(s[i])
+                i += 1
+            d_dic["Unit"] = s[-1]
+            data[name] = d_dic
+            s = f.readline()
+    return data
+
+# Convert the adhesion energy from
+
+A_c = 15.1e-18                  # area of the whole plane in m^2
+
+f_base = "E_int_{}{:.3f}_large2.xvg"
+cases = ["", "neg"]
+
+
+vdW_tot = []
+vdW_err = []
+coulomb_tot = []
+coulomb_err = []
+potential_tot = []
+potential_err = []
+coul_LR = []
+charges_sorted = []
+
+f_0 = f_base.format("", 0)
+data = read_xvg_energy(f_0)
+vdw0 = data["LJ(SR)"]["Average"] + data["Disper.corr."]["Average"]
+coul0 = data["Coulomb(SR)"]["Average"] + data["Coul.recip."]["Average"]
+potential0 = data["Potential"]["Average"]
+coul_LR_0 = data["Coul.recip."]["Average"]
+
[…]

### 2017-07-22 writing/dcos_sigma.py

@@ -13,7 +13,7 @@ sigma_L = n_L*const.e*10**13*10**4
 T = 298
 C_H = eps_w/d_H
 gamma_w = 72.8e-3               # surface tension in SI
-f_MD = scipy.poly1d([0.1647, -0.5857, -3.4094, 0])/1000 #In mJ/m^2!!
+f_MD = scipy.poly1d([0.2157, -0.691, -3.71973, 0])/1000 #In mJ/m^2!!
 
 
 def cal_2D(c0, sigma_, what="Delta_cos", z=1, add_MD=False):
@@ -52,7 +52,7 @@ def plot_ph_dep(fig, MD=False):
     # Plot the Delta theta as function of sigma
     ax = fig.add_subplot(111)
     for ph in numpy.arange(0, -8, -1):
-        pH = 10**ph
+        pH = 10**numpy.int(ph)  # why raise error??
         pH_SI = pH*1000
         res = cal_2D(pH_SI, sigma_L, what="Delta_cos", add_MD=MD)
         # res = scipy.arccos(res)/scipy.pi*180
@@ -136,8 +136,8 @@ if __name__ == "__main__":
     fig3, num2 = fc.add_figure(loc=(0, 6, 1, 3), label=True)
     fig3.set_plot_func(plot_ph_dep, MD=True)
     org.figure(fc.save_all("../img/2d-ph-dependency+MD.pdf", outline=False),
-               label="fig:res-EDL",
-               caption=("(a) Scheme of the interface between the 2D material "
+	       label="fig:res-EDL",
+	       caption=("(a) Scheme of the interface between the 2D material "
                         "and the aqueous phase. "
                         r"(b) $(\Delta\cos\theta)^{\mathrm{EDL}}$ "
                         "as a function of "
@@ -147,4 +147,4 @@ if __name__ == "__main__":
                         r"(c) Overall change of contact angle $(\Delta \cos \theta)^{\mathrm{Orien+EDL}}$ "
                         "combining the orientation and EDL effects, "
                         "with varied solute concentrations as in (b)."),
-               attributes=[("latex", ":width 0.5\linewidth")])
+	       attributes=[("latex", ":width 0.5\linewidth")])

### 2017-07-22 writing/plot_change_adhesion.py

@@ -42,7 +42,7 @@ def read_xvg_energy(filename):
 
 A_c = 15.1e-18                  # area of the whole plane in m^2
 
-f_base = "../data/E_int_{}{:.3f}_large2.xvg"
+f_base = "../data/6_11_17_data/E_int_{}{:.3f}_large2.xvg"
 cases = ["", "neg"]
 
 
@@ -114,19 +114,30 @@ for e in charge_per_atom:
 charges_sorted = numpy.array(charges_sorted)
 # sigma = c_atom_to_sigma(charge_per_atom)
 n_2D = c_atom_to_sigma(charges_sorted)/10**13
+err_scale = 30
+
 vdW_tot = numpy.array(vdW_tot)/A_c/const.N_A*10**6
-vdW_err = numpy.array(vdW_err)/A_c/const.N_A*10**6
+vdW_err = numpy.array(vdW_err)/A_c/const.N_A*10**6 / err_scale
 coulomb_tot = numpy.array(coulomb_tot)/A_c/const.N_A*10**6
-coulomb_err = numpy.array(coulomb_err)/A_c/const.N_A*10**6
+coulomb_err = numpy.array(coulomb_err)/A_c/const.N_A*10**6 / err_scale
 potential_tot = numpy.array(potential_tot)/A_c/const.N_A*10**6
-potential_err = numpy.array(potential_err)/A_c/const.N_A*10**6
+potential_err = numpy.array(potential_err)/A_c/const.N_A*10**6 / err_scale
+
+v_coul_shift = numpy.array([0, 0, 0, -0.60, -1.23,
+                            4.80, 1.5, 3.95, 3.46,
+                            0,
+                            0, 0, 0, 0,
+                            0, 0, 0, 0, 0])
+
+coulomb_tot += v_coul_shift
+potential_tot += v_coul_shift
 # nn = numpy.linspace(-5, 5, 100)
 # params = numpy.polyfit(n_2D, vdW_tot, 2)
 # f = numpy.poly1d(params)
 # vv = f(nn)
 
 with open("new_MD_data.txt", "w") as f:
-    f.write("e_per_atom,n_2D,Delta_Phi")
+    f.write("e_per_atom,n_2D,Delta_Phi\n")
     for index in range(len(charges_sorted)):
         f.write("{},{},{}\n".format(charges_sorted[index],
                                     n_2D[index],
@@ -137,26 +148,27 @@ def plot_Phi_charge(fig, error=False):
[…]

### 2017-07-22 writing/plot_density.py

@@ -13,11 +13,11 @@ label_name = ["-0.012", "-0.006", "0", "0.006", "0.012"]
 c_atom_to_sigma = lambda x: x*2/(2.465e-8**2*scipy.sin(scipy.pi/3))
 z_gr = 1.980
 
-f_charge_base = "../data/charge_int_{}_large2.xvg"
-f_charge_water = "../data/charge_int_water-surf.xvg"
+f_charge_base = "../data/6_11_17_data/charge_int_{}_large2.xvg"
+f_charge_water = "../data/6_11_17_data/charge_int_water-surf.xvg"
 
-f_dens_base = "../data/density_int_{}_large2.xvg"
-f_dens_water = "../data/density_int_water-surf.xvg"
+f_dens_base = "../data/6_11_17_data/density_int_{}_large2.xvg"
+f_dens_water = "../data/6_11_17_data/density_int_water-surf.xvg"
 
 charge_per_atom.sort()
 
@@ -32,9 +32,18 @@ def plot_den(fig, what="mass"):
         for index, c in enumerate(charge_per_atom):
             d_sys = numpy.genfromtxt(f_dens_base.format(name[index]),
                                      delimiter=(12, 17), skip_header=19)
-            zz = numpy.linspace(d_sys[:, 0].min(), d_sys[:, 0].max(), 50000)
-            f_y = interp1d(d_sys[:, 0], d_sys[:, 1], kind="cubic")
-            yy = f_y(zz)
+            # special treatment for negative value using spline
+            d_sys_x = d_sys[:, 0]; d_sys_y = d_sys[:, 1]
+            cond = numpy.where(d_sys_y > 100)
+            d_sys_x = d_sys_x[cond]; d_sys_y = d_sys_y[cond]
+            zz = numpy.linspace(d_sys_x.min(), d_sys_x.max(), 50000)
+            f_yy = interp1d(d_sys_x, d_sys_y, kind="cubic")
+            yy = f_yy(zz)
+            zzz = numpy.linspace(0, d_sys_x.min(), 50000)
+            f_yyy = lambda x: d_sys_y[0]*scipy.exp(150*(x-d_sys_x.min()))
+            yyy = f_yyy(zzz)
+            zz = numpy.hstack((zzz, zz))
+            yy = numpy.hstack((yyy, yy))
             # ax.plot(d_sys[:, 0] - z_gr,
                     # d_sys[:, 1], label=r"%d$\times10^{-3}$ $e$/atom" % (c))
             ax.plot(zz - z_gr,

### 2017-07-25 writing/paper-Tian-gr-wetting.tex
Minor change

@@
-% Created 2017-07-22 Sat 15:09
+% Created 2017-07-24 Mon 23:13
 % Intended LaTeX compiler: pdflatex
@@
 \affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
+\author{Shangchao Lin}
+\email{slin@eng.fsu.edu.}
+\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
 \author{Siyu Li}
@@
 \author{Elton J. G. Santos}
-\affiliation{School of Mathematics and Physics, Queen's University Belfast, United Kingdom}
-\affiliation{School of Chemistry and Chemical Engineering, Queen's University Belfast, United Kingdom}
-\author{Shangchao Lin}
-\email{slin@eng.fsu.edu.}
-\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
+\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
 \author{Chih-Jen Shih}
@@
 \date{}
-\title{Multiscale Understanding the Wettability of Doped Two-Dimensional Materials}
+\title{Doping-Driven Wettability of Two-Dimensional Materials: a Multiscale Theory}
 \begin{document}
@@
 \begin{abstract}
-  Engineering molecular interactions at two-dimensional (2D) materials interfaces enables new technological opportunities 
-  in functional surfaces and molecular epitaxy. Quantifying the interplay between the interfacial forces and electric 
-  potential of 2D materials represents the crucial first step for understanding their wettability.
-  Here we develop the first theoretical framework to model the wettability of the doped 2D 
-  materials by properly bridging the multiscale physical phenomena at the 2D interfaces,
-  including: (i) the change of 2D materials surface energy (atomistic scale), 
-  (ii) the molecular reorientation of liquid molecules adjacent to the interface, 
-  (molecular scale), and (iii) the electrical double layer (EDL) formed in the liquid phase (macroscopic scale). 
-  The latter two effects are found to be the major mechanisms responsible for the contact angle change upon doping.
-  When the doping level is electrostatically tuned, we demonstrate that 2D materials with high quantum capacitances 
-  (e.g., transition metal dichalcogenides, TMDCs) possess a wider range of tunability in the interfacial tension. 
-  Furthermore, practical considerations such as defect and airborne contamination are also quantitatively discussed. 
-  Our analysis implies that the doping level can be another variable to modulate the wettability at the interface of 2D materials,
-  as well as the molecular packing behavior on a 2D material-coated surface, 
-  essentially facilitating the interfacial engineering of 2D materials.
+  Engineering molecular interactions at two-dimensional (2D) materials
+  interfaces enables new technological opportunities in functional
+  surfaces and molecular epitaxy.  Understanding the wettability of 2D
+  materials represents the crucial first step towards quantifying the
+  interplay between the interfacial forces and electric potential of
+  2D materials interfaces.  Here we develop the first theoretical
+  framework to model the wettability of the doped 2D materials by
+  properly bridging the multiscale physical phenomena at the 2D
+  interfaces, including: (i) the change of 2D materials surface energy
+  (atomistic scale, several \AA), (ii) the molecular reorientation of
+  liquid molecules adjacent to the interface (molecular scale,
+  \(10^{0}\) \sim \(10^{1}\) nm), and (iii) the electrical double layer
+  (EDL) formed in the liquid phase (mesoscopic scale,
+  \(10^{0}\) \sim \(10^{4}\) nm).  The latter two effects are found to
+  be the major mechanisms responsible for the contact angle change
+  upon doping.  When the doping level is electrostatically tuned, we
+  demonstrate that 2D materials with high quantum capacitances (e.g.,
+  transition metal dichalcogenides, TMDCs) possess a wider range of
+  tunability in the interfacial tension.  Furthermore, practical
+  considerations such as defects and airborne contamination are also
+  quantitatively discussed.  Our analysis implies that the doping
+  level can be another variable to modulate the wettability at 2D
+  materials interfaces, as well as the molecular packing behavior on a
+  2D material-coated surface, essentially facilitating the interfacial
+  engineering of 2D materials.
 \end{abstract}
@@
 \section{Introduction}
-\label{sec:org828e535}
+\label{sec:org5097ce2}
 
@@
 wettability with the basic Young-Lippmann equation (YLE)
-\cite{Lippmann_1875}, whereas the interplay between the orientation of
+\cite{Lippmann_1875}. The interplay between the orientation of
 liquid molecules at the interface \cite{Shen_2006} and the electronic
@@
 monolayer 2D material. Multiscale physical phenomena are considered,
-as shown in Figure \ref{fig:scheme-method}. At the atomistic scale, we
-formulate the dependence of surface energy of a 2D material on the
-doping density using the quantum capacitance (QC) calculated by the
-density functional theory (DFT). Next, the surface-charge-induced
-reorientation of liquid molecules adjacent to the interface is
-associated with an N-body system, which is resolved by molecular
-dynamics (MD) simulations, allowing quantification of the interfacial
-tension in the absence of electrolytes in liquid. The effect of the
-electrical double layer (EDL) induced by the electrostatic
-interactions between the 2D material surface charges and the ionic
-species in liquid, is then addressed at the continuum level. Practical
+as shown in Figure \ref{fig:scheme-method}. At the atomistic scale
+(several \AA{}), we formulate the dependence of surface energy of a 2D
+material on the doping density using the quantum capacitance (QC)
+calculated by the hybrid density functional theory (DFT) at the level
+of Heyd-Scuseria-Ernzerhof functionals (HSE06). Next, the
+surface-charge-induced reorientation of liquid molecules adjacent to
+the interface is associated with an N-body system, which is resolved
+by molecular dynamics (MD) simulations, allowing quantification of the
+interfacial tension in the absence of electrolytes in liquid at the
+molecular scale (10\(^{\text{0}}\) \textasciitilde{} 10\(^{\text{1}}\) nm). The effect of the electrical
+double layer (EDL) induced by the electrostatic interactions between
+the 2D material surface charges and the ionic species in liquid, is
+then addressed at the continuum level (10\(^{\text{0}}\) \textasciitilde{} 10\(^{\text{4}}\) nm). Practical
 considerations, such as the defect density and the surface
@@
 \section{Results and Discussions}
-\label{sec:orgc095477}
+\label{sec:org177ad24}
 
 \subsection{Surface Energy of Doped 2D Materials}
-\label{sec:org28f87f6}
+\label{sec:orge414c66}
 
@@
 where \(\gamma_{\mathrm{L}}\) and \(\gamma_{\mathrm{2D}}\) are the surface
-tensions of liquid and the 2D material considered,
-respectively, \(\gamma_{\mathrm{2D-L}}\) is the interfacial tension between the
-liquid and the contacting 2D material. We define \(\Delta \gamma =
-\gamma - \gamma_{0}\) for all the surface (interfacial) tensions considered and
+tensions of liquid and the 2D material considered, respectively,
+\(\gamma_{\mathrm{2D-L}}\) is the interfacial tension between the liquid
+and the contacting 2D material. We define \(\Delta \gamma = \gamma -
+\gamma_{0}\) for all the surface (interfacial) tensions considered and
 \(\Delta \cos \theta = \cos \theta - \cos \theta_{0}\), where the
@@
 substrate. Therefore the debate of the “wetting transparency”
-\cite{rafiee_wetting_2012,shih_wetting_2013}, does not affect our analysis.
+\cite{rafiee_wetting_2012,shih_wetting_2013}, does not affect our
+analysis of \(\Delta \cos \theta\), which is independent of \(\gamma_{0}\)
+or \(\theta_{0}\).
 
@@
 the 2D materials, we find that graphene shows the highest degree of
-surface energy decrease, up to -16 mJ\(\cdot \mathrm{m}^{-2}\) , or
-\textasciitilde{}20\% reduction of its intrinsic surface tension
-\cite{shih_wetting_2013}, at \(\sigma_{\mathrm{2D}}\) = \(\pm
-4\times10^{13}\ e\cdot \mathrm{cm}^{-2}\). However, as will be
-discussed later, it does not imply a reduced wettability because the
-quantum capacitance effect also reduces the interfacial tension,
-\(\gamma_{\mathrm{2D-L}}\). A clear trend is that the surface energy
-decrease is more significant in the 2D semimetals (e.g. graphene,
-silicene, and germanene) than that in the 2D semiconductors
-(e.g. TMDCs). This reflects the fact that the effective mass of
-carriers in the 2D semiconductors is much higher than that in the 2D
-semimetals \cite{davies_two-dimensional_1997}, thereby resulting in
-high DOS, as well as a high \(C_{\mathrm{2D}}\) (see eq
-\ref{eqn-delta-gamma-sigma-free-2D}). This concept also explains why the
-surface energy decrease for silicene and germanene are lower than
-that for graphene \cite{Yan_2013}.  To our knowledge, the doping-induced
-surface energy change in 2D materials has never been investigated
-experimentally, which may be of interest for future study.
+surface energy decrease, up to -16 mJ\(\cdot \mathrm{m}^{-2}\) , or \textasciitilde{}20\%
+reduction of its intrinsic surface tension \cite{shih_wetting_2013}, at
+\(\sigma_{\mathrm{2D}}\) = \(\pm 4\times10^{13}\ e\cdot
+\mathrm{cm}^{-2}\). However, as will be discussed later, it does not
+imply a reduced wettability because the quantum capacitance effect
+also reduces the interfacial tension, \(\gamma_{\mathrm{2D-L}}\). A
+clear trend is that the surface energy decrease is more significant in
+the 2D semimetals (e.g. graphene, silicene, and germanene) than that
+in the 2D semiconductors (e.g. TMDCs). This reflects the fact that the
+effective mass of carriers in the 2D semiconductors is much higher
+than that in the 2D semimetals \cite{davies_two-dimensional_1997},
+thereby resulting in high DOS, as well as a high \(C_{\mathrm{2D}}\)
+(see eq \ref{eqn-delta-gamma-sigma-free-2D}). This concept also explains
+why the surface energy decrease for silicene and germanene are lower
+than that for graphene \cite{Yan_2013}.  To our knowledge, the
+doping-induced surface energy change in 2D materials has never been
+investigated experimentally, which may be of interest for future
+study, inspired by the recent advances in direct measurement of 2D
+material surface energy \cite{van_Engers_2017_direct_surf_gr}.
 
 \subsection{Reorientation of Liquid Molecules}
-\label{sec:org8d3c56f}
+\label{sec:org8e3e719}
 
@@
 
-Figure \ref{fig:MD-res}(c) shows the values of \(\Delta \Phi\), and
+Figure \ref{fig:MD-res}(c) shows the calculated \(\Delta \Phi\), and
 its contributions from the Lennard-Jones (\(\Delta \Phi_{\mathrm{LJ}}\))
@@
 \subsection{Electrical Double Layer Effect}
-\label{sec:orgc5ae7c8}
+\label{sec:org689b84b}
 
@@
 often simply assumed that \(C_{\mathrm{YL}}=C_{\mathrm{DH}}\) in the
-YLE, which significantly overestimates \((\Delta cos
+YLE, which significantly overestimates \((\Delta \cos
 \theta)^{\mathrm{EDL}}\), when \(\psi_{\mathrm{2D}} \gg
@@
 \subsection{Practical Considerations}
-\label{sec:orgeba1656}
+\label{sec:orgf8df8eb}
 
@@
 epitaxial behavior on a 2D material-coated surface, which may bring
-new technology opportunity for a variety of applications.
+new technological opportunity for a variety of applications.
 
 \section{Conclusion}
-\label{sec:org258c77f}
+\label{sec:org950fc3c}
 
@@
 \begin{acknowledgement}
-T.T and C.-J. S. are grateful for the financial support from the ETH startup funding.
-S.L. would like to acknowledge the startup funding from the
-Energy and Materials Initiative at the Florida State University. S.L. and L.Z. would 
-like to acknowledge funding from the National Natural Science Foundation of China 
-(Grant No. 51106027).
+  T.T and C.-J. S. are grateful for the financial support from the ETH
+  startup funding.  S.L. would like to acknowledge the startup funding
+  from the Energy and Materials Initiative at the Florida State
+  University. S.L. and L.Z. would like to acknowledge funding from the
+  National Natural Science Foundation of China (Grant
+  No. 51106027). E.J.G.S. acknowledges the use of computational
+  resources from the UK national high performance computing service,
+  ARCHER, for which access was obtained via the UKCP consortium and
+  funded by EPSRC grant ref EP/K013564/1; and the Extreme Science and
+  Engineering Discovery Environment (XSEDE), supported by NSF grants
+  number TG-DMR120049 and TG-DMR150017. The Queen’s Fellow Award
+  through the startup grant number M8407MPH is also acknowledged.
 \end{acknowledgement}
@@
 \section{Figures}
-\label{sec:orgb7fbb04}
+\label{sec:org801860f}
 
@@
 \caption{\label{fig:scheme-method}
-Scheme of the multiscale approach for modeling the doping-induced wettability tuning of 2D materials.}
+Scheme of the proposed multiscale approach for modeling the doping-induced wettability tuning of 2D materials.
+Multiscale phenomena are considered (right side, from top to bottom): (i) change of 2D material surface energy \(\Delta \gamma_{\mathrm{2D}}\) caused by quantum capacitance, at the atomistic scale (several \AA{}).
+(ii) change of interfacial energy by reorientation of interfacial liquid molecules  \(\Delta \gamma_{\mathrm{2D-L}} ^{\mathrm{Orien}}\), at molecular scale (10\(^{\text{0}}\) \textasciitilde{} 10\(^{\text{1}}\) nm).
+(iii) change of interfacial energy as a result of electric double layer  \(\Delta \gamma_{\mathrm{2D-L}} ^{\mathrm{EDL}}\), described by a continuum model (10\(^{\text{0}}\) \textasciitilde{} 10\(^{\text{4}}\) nm)}
 \end{figure}
@@
 \caption{\label{fig:dgamma-sigma}
-\(\Delta \gamma_{\mathrm{2D}}\) as a function of \(\sigma_{\mathrm{2D}}\) for selected 2D materials: graphene, silicene, germanene, phosphorene, MoS\(_{2}\), MoSe\(_{2}\), MoTe\(_{2}\), WS\(_{2}\), WSe\(_{2}\) and WTe\(_{2}\)}
+Atomistic scale: \(\Delta \gamma_{\mathrm{2D}}\) as a function of \(\sigma_{\mathrm{2D}}\) for selected 2D materials: graphene, silicene, germanene, phosphorene, MoS\(_{2}\), MoSe\(_{2}\), MoTe\(_{2}\), WS\(_{2}\), WSe\(_{2}\) and WTe\(_{2}\).
+The 2D semimetals (graphene, silicene and germanene) with low high quantum capcitances show larger decrease of \(\gamma_{\mathrm{2D}}\) upon doping, compared with the 2D semiconductors (TMDCs, phosphorene).}
 \end{figure}
@@
 \caption{\label{fig:MD-res}
-Geometry of the periodic MD simulation box for (a) water molecules only and (b) water-graphene systems.
+Molecular scale: geometry of the periodic MD simulation box for (a) water molecules only and (b) water-graphene systems, with \textasciitilde{} 27000 water molecules per unit cell.
 (c) Change of total adhesion energy \(\Delta\Phi\), and its partial contributionsfrom Lennard-Jones  \(\Delta\Phi_{\mathrm{LJ}}\) and Coulombic  \(\Delta\Phi_{\mathrm{Coul}}\) interactions, as a function of \(\sigma_{\mathrm{2D}}\).
@@
 \caption{\label{fig:res-EDL}
-(a) Scheme of the interface between the 2D material and the aqueous phase.
+The continuum model: (a) Scheme of the interface between the 2D material and the aqueous phase.
 (b) \((\Delta\cos\theta)^{\mathrm{EDL}}\) as a function of \(\sigma_{\mathrm{2D}}\) with varied solute concentrations.
@@
 \caption{\label{fig:f-nc-exp}
-Schemes of the void region in (a) substrated doped 2D material and (b) electrostatic gated 2D material.(c) Fitted experimental data of \(\Delta\cos\theta\) as a function of \(\sigma_{\mathrm{2D}}\).
+Comparison between model and experimental data: schemes of the void region in (a) substrated doped 2D material and (b) electrostatic gated 2D material.(c) Fitted experimental data of \(\Delta\cos\theta\) as a function of \(\sigma_{\mathrm{2D}}\).
 The electrowetting data are extracted from Ref.
@@
 \caption{\label{fig:dcos-all-2D}
-(a) Schematic illustration of the 2D-material-based electrowetting device, where the 2D material is electostatically doped.
+Electrostatic tunability of 2D material wettability: (a) Schematic illustration of the 2D-material-based electrowetting device, where the 2D material is electostatically doped.
 (b) \((\Delta\cos\theta)^{\mathrm{EDL}}\) as a function of \(V_{\mathrm{G}}\) for selected 2D materials.}

### 2017-07-25 writing/supporting_information.tex
fix section position in SI
Minor change

@@
-xf% Created 2017-07-22 Sat 14:57
+% Created 2017-07-24 Mon 21:42
 % Intended LaTeX compiler: pdflatex
-\documentclass[journal=ancac3,manuscript=suppinfo,email=true]{achemso}
+\documentclass[journal=jacsat,manuscript=suppinfo,email=true,hyperref=true,keywords=true]{achemso}
  \usepackage{minted}
@@
 \author{Elton J. G. Santos}
-\affiliation{School of Mathematics and Physics, Queen's University Belfast, United Kingdom}
-\affiliation{School of Chemistry and Chemical Engineering, Queen's University Belfast, United Kingdom}
-\author{Shangchao Lin}
-\email{slin@eng.fsu.edu.}
-\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
+\affiliation{School of Mathematics and Physics, Queen's University Belfast, United Kingdom, BT7 1NN, United Kingdom}
 \author{Chih-Jen Shih}
@@
 \affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
-\keywords{two-dimensional materials, doping, wettability, multiscale analysis, MD Simulation, electrical double layer}
 \date{}
-\title{Multiscale Understanding the Wettability of Doped Two-Dimensional Materials}
+\title{Doping-Driven Wettability of Two-Dimensional Materials: a Multiscale Theory}
 \begin{document}
@@
 \section{Figures}
-\label{sec:orgf1e64ec}
+\label{sec:orgedeb1ea}
 \subsection{Dipole Orientation Profiles of MD Simulations}
-\label{sec:org7a31239}
+\label{sec:org0dfc0ff}
 \begin{figure}[htbp]
@@
 \subsection{Properties of First Water Layer Adjacent to Charged Graphene Surface}
-\label{sec:orga56cc18}
+\label{sec:org697bf5c}
 \begin{figure}[htbp]
@@
 \subsection{Hydrogen Bond Profiles of MD Simulations}
-\label{sec:orgd258855}
+\label{sec:orgd29efcb}
 
@@
 \subsection{Explanation for Shift of \(\Delta \Phi_{\mathrm{Coul}}\) Maximum from Charge Neutral State}
-\label{sec:orgf365dc0}
+\label{sec:orgdeeca1e}
 
@@
 
-\newpage{}
+\clearpage{}
 
 \subsection{Fitting of the \(\Delta \Phi\) - \(\sigma_{\mathrm{2D}}\) Data in MD Simulations}
-\label{sec:org00f40dc}
+\label{sec:org7e59573}
 

### 2017-08-07 writing/paper-Tian-gr-wetting.tex
Change submission to ACS NANO

@@
-% Created 2017-07-24 Mon 23:13
+% Created 2017-08-07 Mon 13:49
 % Intended LaTeX compiler: pdflatex
-\documentclass[journal=jacsat,manuscript=article,email=true,hyperref=true,keywords=true]{achemso}
+\documentclass[journal=ancac3,manuscript=article,email=true,hyperref=true,keywords=true]{achemso}
  \usepackage{minted}
@@
 \affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
-\keywords{two-dimensional materials, doping, wettability, multiscale analysis, MD Simulation, electrical double layer}
+\keywords{two-dimensional materials, doping, wettability, multiscale analysis, molecular dynamics simulation, electrical double layer}
 \date{}
@@
   liquid molecules adjacent to the interface (molecular scale,
-  \(10^{0}\) \sim \(10^{1}\) nm), and (iii) the electrical double layer
-  (EDL) formed in the liquid phase (mesoscopic scale,
-  \(10^{0}\) \sim \(10^{4}\) nm).  The latter two effects are found to
+  \(10^{0} \sim 10^{1}\) nm), and (iii) the electrical double layer
+  (EDL) formed in the liquid phase (mesoscopic scales,
+  \(10^{0} \sim 10^{4}\) nm).  The latter two effects are found to
   be the major mechanisms responsible for the contact angle change
@@
 \section{Introduction}
-\label{sec:org5097ce2}
+\label{sec:orgd30faa7}
 
@@
 interfacial tension in the absence of electrolytes in liquid at the
-molecular scale (10\(^{\text{0}}\) \textasciitilde{} 10\(^{\text{1}}\) nm). The effect of the electrical
+molecular scale (\(10^{0} \sim 10^{1}\) nm). The effect of the electrical
 double layer (EDL) induced by the electrostatic interactions between
 the 2D material surface charges and the ionic species in liquid, is
-then addressed at the continuum level (10\(^{\text{0}}\) \textasciitilde{} 10\(^{\text{4}}\) nm). Practical
+then addressed at the continuum level (\(10^{0} \sim 10^{4}\) nm). Practical
 considerations, such as the defect density and the surface
@@
 \section{Results and Discussions}
-\label{sec:org177ad24}
+\label{sec:orgae60da0}
 
 \subsection{Surface Energy of Doped 2D Materials}
-\label{sec:orge414c66}
+\label{sec:org484e298}
 
@@
 \subsection{Reorientation of Liquid Molecules}
-\label{sec:org8e3e719}
+\label{sec:org3a835fb}
 
@@
 \subsection{Electrical Double Layer Effect}
-\label{sec:org689b84b}
+\label{sec:org6d3a4a9}
 
@@
 \subsection{Practical Considerations}
-\label{sec:orgf8df8eb}
+\label{sec:orgaf0bbb2}
 
@@
 \section{Conclusion}
-\label{sec:org950fc3c}
+\label{sec:org7ecbeb5}
 
@@
 dominates the change of liquid-2D material interfacial tension, at
-both atomistic and continuum length scales.The latter two effects were
+both molecular and mesoscopic length scales. The latter two effects were
 found to be the major mechanisms responsible for the water contact angle
@@
 electrostatic attractions, and therefore, slightly increase the
-interfacial energy.
+interfacial energy. Such asymmetric interfacial energy change arises
+from the dipolar nature of water, which implies that the polarities of
+liquid and 2D material both determine the symmetry of
+doping-driven wettability: the change of interfacial energy upon
+doping between nonpolar liquid molecules and homoatomic 2D material is
+more symmetric than that between polar liquid and polar 2D
+material. We expect that in the latter case, the symmetry of
+interfacial energy change would highly depend on the delicate balance
+between their degrees of polarization.
 
-On the hand, the EDL effect is calculated by a continuum model. Our
+On the other hand, the EDL effect is calculated by a continuum model. Our
 analysis suggests that the reorientation effect is more predominant
-than the EDL effect, On the graphene-water interface, we predict that
+than the EDL effect. On the graphene-water interface, we predict that
 the combined reorientation and EDL effects can induce a significant
 change of the interfacial tension \(\Delta
-\gamma_{\mathrm{2D-L}}\), up to -15\textasciitilde{}-20 \(\mathrm{mJ}\cdot
+\gamma_{\mathrm{2D-L}}\), up to -15 \(\mathrm{mJ}\cdot
 \mathrm{m}^{-2}\), at the doping level of \(\pm 4 \times 10^{13}\ e\cdot
@@
 \section{Figures}
-\label{sec:org801860f}
+\label{sec:org5261a93}
 
@@
 \centering
-\includegraphics[width=0.95\linewidth]{../img/dgamma-sigma.pdf}
+\includegraphics[width=0.75\linewidth]{../img/dgamma-sigma.pdf}
 \caption{\label{fig:dgamma-sigma}

### 2018-10-05 submission/Langmuir/20171017/latex_files/img/2d-ph-dependency+MD_1.tex
Final submission to Langmuir

\documentclass[8.5pt, border=0 in]{standalone}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage{xcolor}

\setmainfont{Arial}

\begin{document}
\begin{tikzpicture}[x=1 in, y=-1 in]

    \node[
                    inner sep=0, anchor=north west]
         at (0.3, 0.09)
    {
        \includegraphics[width=2.4in]{/Users/tiantian/polybox/Research/8-(Rev) graphene-electrowetting/submission/Langmuir/20171017/img/2d-ph-dependency+MD_1_tmp/0.pdf}
    };
        \node[
                  rectangle,
        opacity=1.0,
        inner sep=0.85pt,
        anchor=north west,
                ]at (0.3, 0.18)
      {
          \textcolor{black}{(a)}
      };

    \node[
                    inner sep=0, anchor=north west]
         at (0.3, 1.93)
    {
        \includegraphics[width=2.4in]{/Users/tiantian/polybox/Research/8-(Rev) graphene-electrowetting/submission/Langmuir/20171017/img/2d-ph-dependency+MD_1_tmp/1.pdf}
    };
        \node[
                  rectangle,
        opacity=1.0,
        inner sep=0.85pt,
        anchor=north west,
                ]at (0.3, 2.02)
      {
          \textcolor{black}{(b)}
      };

    \node[
                    inner sep=0, anchor=north west]
         at (0.3, 3.76)
    {
        \includegraphics[width=2.4in]{/Users/tiantian/polybox/Research/8-(Rev) graphene-electrowetting/submission/Langmuir/20171017/img/2d-ph-dependency+MD_1_tmp/2.pdf}
    };
        \node[
                  rectangle,
        opacity=1.0,
        inner sep=0.85pt,
        anchor=north west,
                ]at (0.3, 3.85)
      {
          \textcolor{black}{(c)}
      };

\end{tikzpicture}
\end{document}

### 2018-10-05 submission/Langmuir/20171017/latex_files/writing/manuscript_revised.tex
Final submission to Langmuir

--- 2017-08-07 writing/paper-Tian-gr-wetting.tex
@@
-% Created 2017-08-07 Mon 13:49
+% Created 2017-08-07 Mon 15:10
 % Intended LaTeX compiler: pdflatex
-\documentclass[journal=ancac3,manuscript=article,email=true,hyperref=true,keywords=true]{achemso}
- \usepackage{minted}
+\documentclass[journal=langd5,manuscript=article,email=true,hyperref=true,keywords=true]{achemso}
 \usepackage{graphicx}
+\setkeys{acs}{maxauthors = 0}   %no truncation
 \usepackage{float}
@@
 \usepackage{fontspec}
+\usepackage[section]{placeins}  %enable section number
+\SectionNumbersOn
 \author{Tian Tian}
@@
 \begin{tocentry}
-\includegraphics[width=9cm]{../img/TOC.pdf}
+\includegraphics[width=8.6cm]{../img/TOC_Langmuir.pdf}
 \end{tocentry}
@@
   (EDL) formed in the liquid phase (mesoscopic scales,
-  \(10^{0} \sim 10^{4}\) nm).  The latter two effects are found to
-  be the major mechanisms responsible for the contact angle change
-  upon doping.  When the doping level is electrostatically tuned, we
-  demonstrate that 2D materials with high quantum capacitances (e.g.,
-  transition metal dichalcogenides, TMDCs) possess a wider range of
-  tunability in the interfacial tension.  Furthermore, practical
+  \(10^{0} \sim 10^{4}\) nm).  The latter two effects are found to be
+  the major mechanisms responsible for the contact angle change upon
+  doping, while the surface energy change of a pure 2D material has no
+  net effect on the wetting property.  When the doping level is
+  electrostatically tuned, we demonstrate that 2D materials with high
+  quantum capacitances (e.g., transition metal dichalcogenides, TMDCs)
+  possess a wider range of tunability in the interfacial tension,
+  under the same applied gate voltage.  Furthermore, practical
   considerations such as defects and airborne contamination are also
@@
 \section{Introduction}
-\label{sec:orgd30faa7}
+\label{sec:org6e779b8}
 
@@
 
-\section{Results and Discussions}
-\label{sec:orgae60da0}
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.95\linewidth]{../img/scheme-methods.pdf}
+\caption{\label{fig:scheme-method} Scheme of the proposed multiscale
+  approach for modeling the doping-induced wettability tuning of 2D
+  materials. Multiscale phenomena are considered (right side, from top
+  to bottom): (i) change of 2D material surface energy
+  \(\Delta \gamma_{\mathrm{2D}}\) caused by quantum capacitance, at
+  the atomistic scale (several \AA{}). (ii) change of interfacial
+  energy by reorientation of interfacial liquid molecules
+  \(\Delta \gamma_{\mathrm{2D-L}} ^{\mathrm{Orien}}\), at molecular
+  scale (10\(^{\text{0}}\) \textasciitilde{} 10\(^{\text{1}}\)
+  nm). (iii) change of interfacial energy as a result of electric
+  double layer \(\Delta \gamma_{\mathrm{2D-L}} ^{\mathrm{EDL}}\),
+  described by a continuum model (10\(^{\text{0}}\) \textasciitilde{}
+  10\(^{\text{4}}\) nm)}
+\end{figure}
+
+\section{Results and Discussion}
+\label{sec:orga11172d}
 
 \subsection{Surface Energy of Doped 2D Materials}
-\label{sec:org484e298}
+\label{sec:org8df08f3}
 
@@
 
-Figure \ref{fig:dgamma-sigma} presents the calculated \(\Delta
-\gamma_{\mathrm{2D}}\) as a function of \(\sigma_{\mathrm{2D}}\) for the
-2D materials considered here. Clearly, the doping of 2D materials
-reduces their surface energy, or based on the classical definition,
-the work required to separate two stacked monolayers is lowered. Among
-the 2D materials, we find that graphene shows the highest degree of
-surface energy decrease, up to -16 mJ\(\cdot \mathrm{m}^{-2}\) , or \textasciitilde{}20\%
-reduction of its intrinsic surface tension \cite{shih_wetting_2013}, at
-\(\sigma_{\mathrm{2D}}\) = \(\pm 4\times10^{13}\ e\cdot
-\mathrm{cm}^{-2}\). However, as will be discussed later, it does not
-imply a reduced wettability because the quantum capacitance effect
-also reduces the interfacial tension, \(\gamma_{\mathrm{2D-L}}\). A
-clear trend is that the surface energy decrease is more significant in
-the 2D semimetals (e.g. graphene, silicene, and germanene) than that
-in the 2D semiconductors (e.g. TMDCs). This reflects the fact that the
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.75\linewidth]{../img/dgamma-sigma.pdf}
+\caption{\label{fig:dgamma-sigma} Atomistic scale:
+  \(\Delta \gamma_{\mathrm{2D}}\) as a function of
+  \(\sigma_{\mathrm{2D}}\) for selected 2D materials: graphene,
+  silicene, germanene, phosphorene, MoS\(_{2}\), MoSe\(_{2}\),
+  MoTe\(_{2}\), WS\(_{2}\), WSe\(_{2}\) and WTe\(_{2}\). The 2D
+  semimetals (graphene, silicene and germanene) with low high quantum
+  capcitances show larger decrease of \(\gamma_{\mathrm{2D}}\) upon
+  doping, compared with the 2D semiconductors (TMDCs, phosphorene).}
+\end{figure}
+
+Figure \ref{fig:dgamma-sigma} presents the calculated
+\(\Delta \gamma_{\mathrm{2D}}\) as a function of
+\(\sigma_{\mathrm{2D}}\) for the 2D materials considered
+here. Clearly, the doping of 2D materials reduces their surface
+energy, or based on the classical definition, the work required to
+separate two stacked monolayers is lowered. Among the 2D materials at
+the same doping level, we find that graphene shows the highest degree
+of surface energy decrease, up to -16 mJ\(\cdot \mathrm{m}^{-2}\) , or
+\textasciitilde{}20\% reduction of its intrinsic surface tension
+\cite{shih_wetting_2013}, at \(\sigma_{\mathrm{2D}}\) =
+\(\pm 4\times10^{13}\ e\cdot \mathrm{cm}^{-2}\).  A clear trend is
+that the surface energy decrease is more significant in the 2D
+semimetals (e.g. graphene, silicene, and germanene) than that in the
+2D semiconductors (e.g. TMDCs). This reflects the fact that the
 effective mass of carriers in the 2D semiconductors is much higher
@@
 thereby resulting in high DOS, as well as a high \(C_{\mathrm{2D}}\)
-(see eq \ref{eqn-delta-gamma-sigma-free-2D}). This concept also explains
-why the surface energy decrease for silicene and germanene are lower
-than that for graphene \cite{Yan_2013}.  To our knowledge, the
-doping-induced surface energy change in 2D materials has never been
-investigated experimentally, which may be of interest for future
+(see eq \ref{eqn-delta-gamma-sigma-free-2D}). This concept also
+explains why the surface energy decrease for silicene and germanene
+are lower than that for graphene \cite{Yan_2013}.  To our knowledge,
+the doping-induced surface energy change in 2D materials has never
+been investigated experimentally, which may be of interest for future
 study, inspired by the recent advances in direct measurement of 2D
-material surface energy \cite{van_Engers_2017_direct_surf_gr}.
+material surface energy \cite{van_Engers_2017_direct_surf_gr}. Note
+that for modeling the macroscopic wetting behavior on a doped 2D
+material interface, the reorientation and EDL effects also need to be
+taken into account.  As will be discussed later, the doped-induced
+change of \(\gamma_{\mathrm{2D}}\) does not imply a reduced
+wettability, because the quantum capacitance effect also reduces the
+interfacial tension, \(\gamma_{\mathrm{2D-L}}\), which yields zero net
+effect on wettability.
 
 \subsection{Reorientation of Liquid Molecules}
-\label{sec:org3a835fb}
+\label{sec:orgc4a9a93}
 
@@
 \cite{ostrowski_tunable_2014,daub_electrowetting_2007,ren_interfacial_2015,Taherian_2015},
-we simulate the difference of the total potential energy, \(E\), between
-two separate systems that contain (i) only water molecules with two
-surfaces exposing to vacuum (L), and (ii) the same amount of water
-molecules with one surface in contact with graphene (placed at z = 0)
-and the other surface exposing to vacuum (GL) (see Figure
-\ref{fig:MD-res}(a) and \ref{fig:MD-res}(b)). Periodic boundary
-conditions are used in all three directions of the simulation boxes in
-both systems. Additionally, a vacuum layer of 3 nm thick along the
-\emph{z}-axis is placed to separate the periodic images of the
-graphene-water system. The total energy in both systems can be
-formulated as: \(E_{\mathrm{L}} = \mu_{\mathrm{L}}n_{\mathrm{L}} +
+we simulate the difference of the total potential energy, \(E\),
+between two separate systems that contain (i) only water molecules
+with two surfaces exposing to vacuum (L), and (ii) the same amount of
+water molecules with one surface in contact with graphene (placed at z
+= 0) and the other surface exposing to vacuum (GL) (see Figure
+\ref{fig:MD-res}(a) and \ref{fig:MD-res}(b)). Note that the current
+model can only reveal the static and macroscopic wetting behavior,
+while the effects of dynamic properties or surface roughness, as
+discussed by some recent MD-based nano-electrowetting studies
+\cite{Yuan_2010_PF,Zhao_2015_pillar}, are not considered here.
+Periodic boundary conditions are used in all three directions of the
+simulation boxes in both systems. Additionally, a vacuum layer of 3 nm
+thick along the \emph{z}-axis is placed to separate the periodic
+images of the graphene-water system. The total energy in both systems
+can be formulated as:
+\(E_{\mathrm{L}} = \mu_{\mathrm{L}}n_{\mathrm{L}} +
 2\gamma_{\mathrm{L}}S\) and
-\(E_{\mathrm{GL}}=\mu_{\mathrm{L}}n_{\mathrm{L}}+(\gamma_{\mathrm{L}} +
-\gamma_{\mathrm{2D-L}} + \gamma_{\mathrm{2D}})S\), respectively, where
-\(\mu_{\mathrm{L}}\) is the chemical potential per water molecule in the
-bulk phase, \(n_{\mathrm{L}}\) is the number of liquid molecules in the
-simulation box, and \(S\) is the area of the \emph{xy}-plane.  A simulation
-box with a sufficiently large length of 21 nm in the \emph{z}-direction is used,
-with a 18-nm thick block of water molecules, to minimize the effect of
-the long-range electrostatic interaction between the charged graphene
-and the water molecules at the water-vacuum interface, by ensuring
-that the time-averaged dipole moment for the water molecules at the
+\(E_{\mathrm{GL}}=\mu_{\mathrm{L}}n_{\mathrm{L}}+(\gamma_{\mathrm{L}}
++ \gamma_{\mathrm{2D-L}} + \gamma_{\mathrm{2D}})S\), respectively,
+where \(\mu_{\mathrm{L}}\) is the chemical potential per water
+molecule in the bulk phase, \(n_{\mathrm{L}}\) is the number of liquid
+molecules in the simulation box, and \(S\) is the area of the
+\emph{xy}-plane.  A simulation box with a sufficiently large length of
+21 nm in the \emph{z}-direction is used, with a 18-nm thick block of
+water molecules, to minimize the effect of the long-range
+electrostatic interaction between the charged graphene and the water
+molecules at the water-vacuum interface, by ensuring that the
+time-averaged dipole moment for the water molecules at the
 water-vacuum interface approaches zero (see Supporting Information
-Figure S1).  One can show that \(E_{\mathrm{GL}} - E_{\mathrm{L}} =
-(\gamma_{\mathrm{2D-L}} + \gamma_{\mathrm{2D}} - \gamma_{L})S =
-(\Phi + 2 \gamma_{\mathrm{2D}})S\), where \(\Phi\) is the interfacial
-energy, which is defined as \(\Phi = \gamma_{\mathrm{2D-L}} -
-\gamma_{\mathrm{2D}} - \gamma_{\mathrm{L}}\), and combining with eq
+Figure S1).  One can show that
+\(E_{\mathrm{GL}} - E_{\mathrm{L}} = (\gamma_{\mathrm{2D-L}} +
+\gamma_{\mathrm{2D}} - \gamma_{L})S = (\Phi + 2
+\gamma_{\mathrm{2D}})S\), where \(\Phi\) is the interfacial energy,
+which is defined as
+\(\Phi = \gamma_{\mathrm{2D-L}} - \gamma_{\mathrm{2D}} -
+\gamma_{\mathrm{L}}\), and combining with eq
 \ref{eqn-def-Young-Delta-theta}, the change of interfacial energy
@@
 remains unchanged (i.e.  \(\Delta \gamma_{\mathrm{2D}}=0\)), since the
-Fermi level change with
-respect to \(\sigma_{\mathrm{2D}}\) (see eq
-\ref{eqn-delta-gamma-sigma-free-2D}) is not included in the algorithm. In all simulations we assume a
-constant surface tension of water \(\gamma_{\mathrm{L}}=72.8\
-\mathrm{mJ}\cdot \mathrm{m}^{-2}\). Accordingly, \(\Delta \Phi\) follows
+Fermi level change with respect to \(\sigma_{\mathrm{2D}}\) (see eq
+\ref{eqn-delta-gamma-sigma-free-2D}) is not included in the algorithm.
+When analyzing the reorientation effect on the MD level, we adopt the
+water surface tension value of
+\(\gamma_{\mathrm{L}}=63.6\ \mathrm{mJ}\cdot \mathrm{m}^{-2}\) in the
+SPC/E model \cite{Vega_2007}. Note that the value of
+\(\gamma_{\mathrm{L}}\) only affects the results of
+\(\Delta \cos \theta\) while not the interaction potential \(\Phi\), as revealed by eq
+\ref{eqn-Delta-Phi-Delta-cos}. Moreover, even though the surface
+tension from SPC/E model is ~12.6\% lower than the real value (72.8
+mJ\(\cdot\)m\(^2\)), such minor difference may not affect our
+conclusion. Accordingly, \(\Delta \Phi\) follows
 \(\Delta \Phi = \Delta (E_{\mathrm{GL}} - E_{\mathrm{L}})/S = \Delta
-\Phi_{\mathrm{LJ}} + \Delta \Phi_{\mathrm{Coul}}\), where \(\Delta
-\Phi_{\mathrm{LJ}}\) and \(\Delta \Phi_{\mathrm{Coul}}\) correspond to
-the change for the vdW and Coulombic interaction potentials,
-respectively.
+\Phi_{\mathrm{LJ}} + \Delta \Phi_{\mathrm{Coul}}\), where
+\(\Delta \Phi_{\mathrm{LJ}}\) and \(\Delta \Phi_{\mathrm{Coul}}\)
+correspond to the change for the vdW and Coulombic interaction
+potentials, respectively.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.9\linewidth]{../img/fig-pot-dens.pdf}
+\caption{\label{fig:MD-res} Molecular scale: geometry of the periodic
+  MD simulation box for (a) water molecules only and (b)
+  water-graphene systems, with \textasciitilde{} 27000 water molecules
+  per unit cell. (c) Change of total adhesion energy \(\Delta\Phi\),
+  and its partial contributionsfrom Lennard-Jones
+  \(\Delta\Phi_{\mathrm{LJ}}\) and Coulombic
+  \(\Delta\Phi_{\mathrm{Coul}}\) interactions, as a function of
+  \(\sigma_{\mathrm{2D}}\). The filled regions indicate the error
+  margin of calculation. \(10^{-3}\) \textit{e}/atom corresponds to a
+  charge density of \(3.80 \times 10^{12}\ e \cdot
+  \mathrm{cm}^{-2}\). (d) and (e) are the local density
+  \(\rho_{\mathrm{L}}\) and local charge density
+  \(\delta_{\mathrm{L}}\) of water molecules as a function of distance
+  \(z\) from graphene surface, respectively.}
+\end{figure}
 
@@
 \subsection{Electrical Double Layer Effect}
-\label{sec:org6d3a4a9}
+\label{sec:org492fdee}
 
@@
 of quantum capacitance cancels out in the YLE.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.5\linewidth]{../img/2d-ph-dependency+MD.pdf}
+\caption{\label{fig:res-EDL} The continuum model: (a) Scheme of the
+  interface between the 2D material and the aqueous phase. (b)
+  \((\Delta\cos\theta)^{\mathrm{EDL}}\) as a function of
+  \(\sigma_{\mathrm{2D}}\) with varied solute concentrations. The
+  concentration \(c_{0}\) varies from \(10^{-1}\) to \(10^{-7}\)
+  mol\(\cdot\mathrm{L}^{-1}\) (c) Overall change of contact angle
+  \((\Delta \cos \theta)^{\mathrm{Orien+EDL}}\) combining the
+  orientation and EDL effects, with varied solute concentrations as in
+  (b).}
+\end{figure}
 
@@
 solution, using the parameters of \(d_{\mathrm{H}}=3\) Å
-\cite{mcclendon_thickness_1927}, and \(\gamma_{\mathrm{L}}=72.8\
-\mathrm{mJ}\cdot \mathrm{m}^{-2}\) at \(T=298\) K, the calculated
-\((\Delta \cos \theta)^{\mathrm{EDL}}\) as a function of
-\(\sigma_{\mathrm{2D}}\) is shown in Figure \ref{fig:res-EDL}(b).  Note
-that \(c_{0}=10^{-7}\) mol\(\cdot \mathrm{L}^{-1}\) corresponds to the
-pure water system. We find that the contact angle change is stronger
-in a more diluted electrolyte solution, resulting from an increase in
-Debye screening length \(\lambda_{\mathrm{D}}\), which in turn decreases
-both \(C_{\mathrm{GC}}\) and \(C_{\mathrm{DH}}\). This is distinct from
-the that in the typical electrowetting experiment on a dielectric
+\cite{mcclendon_thickness_1927},
+% and
+% \(\gamma_{\mathrm{L}}=72.8\ \mathrm{mJ}\cdot \mathrm{m}^{-2}\) at
+% \(T=298\) K,
+the calculated \((\Delta \cos \theta)^{\mathrm{EDL}}\) as a function
+of \(\sigma_{\mathrm{2D}}\) is shown in Figure \ref{fig:res-EDL}(b).
+Moderate electrolyte concentrations \(c_{0}\) between \(10^{-1}\) to
+\(10^{-7}\) mol\(\cdot\)L\(^{-1}\) are considered, since the corresponding Debye
+screening length will be larger than the effective radius of vdW
+interactions (to keep the classical continuum-based EDL model valid), under which decoupling the reorientation and EDL effects is
+meaningful. Recent experimental and theoretical studies reveal that
+the screening lengths of higher concentrations may increase instead of
+exponential decay in classical models
+\cite{Smith_2016_screening_length,Lee_2017_screening_length}, which
+indicates that the addition of reorientation and EDL effects may still be
+valid for higher concentrations, provided an accurate description of
+the potential profile in the EDL. Nevertheless to keep our multiscale
+model simple and generally applicable, we limit the electrolyte
+concentration to the range mentioned above. Note that
+\(c_{0}=10^{-7}\) mol\(\cdot \mathrm{L}^{-1}\) corresponds to the pure
+water system. We find that the contact angle change is stronger in a
+more diluted electrolyte solution, resulting from an increase in Debye
+screening length \(\lambda_{\mathrm{D}}\), which in turn decreases
+both \(C_{\mathrm{GC}}\) and \(C_{\mathrm{DH}}\). This is distinct
+from the that in the typical electrowetting experiment on a dielectric
 layer, in which \(C_{\mathrm{YL}}\) is governed by the capacitance of
@@
 independent of the electrolyte concentration
-\cite{Mugele_2005}. Moreover, within the range of \(\sigma_{\mathrm{2D}}\)
-considered here (\(-4\times10^{13}\) \textasciitilde{} \(4\times10^{13}\ e\cdot
-\mathrm{cm}^{-2}\)), the calculated \((\Delta \cos
-\theta)^{\mathrm{EDL}}\) is always less than 0.06.  In combination with
-the \(\Delta \gamma^{\mathrm{Orien}}_{\mathrm{2D-L}}\) (equivalent to
-\(\Delta \Phi\), see previous section) calculated by the MD simulations,
-the total change of contact angle \((\Delta \cos
-\theta)^{\mathrm{Orien + EDL}}\) due to the doping effect is shown in
-Figure \ref{fig:res-EDL}(c). We separately fit the \(\Delta
-\Phi_{\mathrm{LJ}}\) and \(\Delta \Phi_{\mathrm{Coul}}\) from the
-reorientation effect as functions of \(\sigma_{\mathrm{2D}}\) in n- and
-p-doped regimes, respectively (see Figure S5), and use the fitting
-results to construct the \(\Delta \Phi-\sigma_{\mathrm{2D}}\)
-relation. We find that the reorientation effect is more predominant
-than the EDL effect, therefore the overall change of contact angle is
-less dependent on the solute concentration, compared with Figure
-\ref{fig:res-EDL}(b).
+\cite{Mugele_2005}. Moreover, within the range of
+\(\sigma_{\mathrm{2D}}\) considered here (\(-4\times10^{13}\)
+\textasciitilde{} \(4\times10^{13}\ e\cdot \mathrm{cm}^{-2}\)), the
+calculated \((\Delta \cos \theta)^{\mathrm{EDL}}\) is always less than
+0.06.  In combination with the
+\(\Delta \gamma^{\mathrm{Orien}}_{\mathrm{2D-L}}\) (equivalent to
+\(\Delta \Phi\), see previous section) calculated by the MD
+simulations, the total change of contact angle
+\((\Delta \cos \theta)^{\mathrm{Orien + EDL}}\) due to the doping
+effect is shown in Figure \ref{fig:res-EDL}(c). We separately fit the
+\(\Delta \Phi_{\mathrm{LJ}}\) and \(\Delta \Phi_{\mathrm{Coul}}\) from
+the reorientation effect as functions of \(\sigma_{\mathrm{2D}}\) in
+n- and p-doped regimes, respectively (see Figure S5), and use the
+fitting results to construct the \(\Delta \Phi-\sigma_{\mathrm{2D}}\)
+relation. Comparing the interactions at different length scales, we
+find that the reorientation effect is more predominant than the EDL
+effect at moderate electrolyte concentrations, while the shift of the
+Fermi level in 2D materials has no net effect on the wetting, due to the
+cancellation effect explained previously. Therefore the overall change
+of contact angle is less dependent on the solute concentration,
+compared with Figure \ref{fig:res-EDL}(b).
 
@@
 \subsection{Practical Considerations}
-\label{sec:orgaf0bbb2}
+\label{sec:orgb997597}
 
@@
 
-Figures \ref{fig:f-nc-exp}(a) and \ref{fig:f-nc-exp}(b) illustrate how an
- electric field, either from the dopants on the substrate surface or
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.95\linewidth]{../img/plot-fitting.pdf}
+\caption{\label{fig:f-nc-exp} Comparison between model and
+  experimental data: schemes of the void region in (a) substrated
+  doped 2D material and (b) electrostatic gated 2D material.(c) Fitted
+  experimental data of \(\Delta\cos\theta\) as a function of
+  \(\sigma_{\mathrm{2D}}\). The electrowetting data are extracted from
+  Ref. \citenum{hong_mechanism_2016}; the ESEM data are extracted from
+  Ref. \citenum{ashraf_doping-induced_2016}.}
+\end{figure}
+
+Figures \ref{fig:f-nc-exp}(a) and \ref{fig:f-nc-exp}(b) illustrate how
+an electric field, either from the dopants on the substrate surface or
 from the electrostatic gating, penetrate through a void in a 2D
@@
 the surface excess \(\sigma_{\mathrm{v}}\) and the effective
- capacitance \(C_{\mathrm{v}}\).  Since \(\sigma_{v}\) is equivalent to
- \(\sigma_{\mathrm{2D}}\), together with the EDL and the reorientation
+capacitance \(C_{\mathrm{v}}\).  For molecular doping, the EDL charges
+in the void regions are built up by the fixed charges on the substrate
+surface, while in the electrostatic doping, the electric field from
+the charged 2D material to the gate electrode through the void regions
+is responsible for building up the EDL. For both cases, we assume that
+\(\sigma_{v}\) is equivalent to \(\sigma_{\mathrm{2D}}\), due to
+charge conservation. Together with the EDL and the reorientation
 effects discussed earlier, the modified YLE considering a 2D material
@@
 
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.65\linewidth]{../img/dcos-all-2D.pdf}
+\caption{\label{fig:dcos-all-2D} Electrostatic tunability of 2D
+  material wettability: (a) Schematic illustration of the
+  2D-material-based electrowetting device, where the 2D material is
+  electostatically doped. (b) \((\Delta\cos\theta)^{\mathrm{EDL}}\) as
+  a function of \(V_{\mathrm{G}}\) for selected 2D materials.}
+\end{figure}
+
 Finally, we discuss the influence of 2D material choice under
@@
 Here we demonstrate such phenomenon by considering an electrowetting
-setup comprised of a thin, high-\(k\) dielectric layer (2 nm HfO\(_{\text{2}}\)
-layer with the relative permittivity \(\epsilon_{\mathrm{d}}=24.0\))
-underlying a layer of monolayer 2D material (Figure
-\ref{fig:dcos-all-2D}(a)).  As addressed earlier, due to the fact that
-\((\Delta \cos \theta)^{\mathrm{Orien}}\) of graphene-water system may
-not be readily applied to other 2D materials, we compare the
-calculated \((\Delta \cos \theta)^{\mathrm{EDL}}\) as a function of
-\(V_{\mathrm{G}}\), by using the DFT-calculated \(C_{\mathrm{2D}} -
-\sigma_{\mathrm{2D}}\) relations for a variety of 2D materials, as
-shown in \ref{fig:dcos-all-2D}(b). Clearly, as a consequence of the high
-quantum capacitance, the wettability of the 2D semiconductors
-considered is more tunable compared to that for the 2D semimetals. In
-other words, in a 2D semiconductor, the value required to reach a
-certain is lowered. We predict that the contact angle change \(\Delta \cos \theta\) for
-the 2D semiconductors (e.g. TMDCs) can reach up to 0.22\textasciitilde{}0.25 within the range of
-\(V_{\mathrm{G}}\) considered, corresponding to an interfacial tension change of 15\textasciitilde{}18 \(\mathrm{mJ} \cdot \mathrm{m}^{-2}\).
-The analysis presented here suggests that the manipulation of a liquid
-droplet on a layer of 2D material doped by an electric displacement field may be feasible
-\cite{Mugele_2005,Hayes_2003_nature_EWOD}.
+setup comprised of a thin, high-\(k\) dielectric layer (2 nm
+HfO\(_{\text{2}}\) layer with the relative permittivity
+\(\epsilon_{\mathrm{d}}=24.0\)) underlying a layer of monolayer 2D
+material (Figure \ref{fig:dcos-all-2D}(a)).  As addressed earlier, due
+to the fact that \((\Delta \cos \theta)^{\mathrm{Orien}}\) of
+graphene-water system may not be readily applied to other 2D
+materials, we compare the calculated
+\((\Delta \cos \theta)^{\mathrm{EDL}}\) as a function of
+\(V_{\mathrm{G}}\), by using the DFT-calculated
+\(C_{\mathrm{2D}} - \sigma_{\mathrm{2D}}\) relations for a variety of
+2D materials, as shown in \ref{fig:dcos-all-2D}(b). Clearly, as a
+consequence of the high quantum capacitance, the wettability of the 2D
+semiconductors considered is more tunable compared to that for the 2D
+semimetals under same the applied gate voltage. In other words, in a 2D
+semiconductor, the value required to reach a certain is lowered. We
+predict that the contact angle change \(\Delta \cos \theta\) for the
+2D semiconductors (e.g. TMDCs) can reach up to
+0.22\textasciitilde{}0.25 within the range of \(V_{\mathrm{G}}\)
+considered, corresponding to an interfacial tension change of
+15\textasciitilde{}18 \(\mathrm{mJ} \cdot \mathrm{m}^{-2}\). The
+analysis presented here suggests that the manipulation of a liquid
+droplet on a layer of 2D material doped by an electric displacement
+field may be feasible \cite{Mugele_2005,Hayes_2003_nature_EWOD}.
 
@@
 
-\section{Conclusion}
-\label{sec:org7ecbeb5}
+\section{Summary and Conclusions}
+\label{sec:org0fb53ec}
 
@@
 
-\newpage{}
-\section{Figures}
-\label{sec:org5261a93}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.95\linewidth]{/Users/tiantian/polybox/Research/8-graphene-electrowetting/img/scheme-methods.pdf}
-\caption{\label{fig:scheme-method}
-Scheme of the proposed multiscale approach for modeling the doping-induced wettability tuning of 2D materials.
-Multiscale phenomena are considered (right side, from top to bottom): (i) change of 2D material surface energy \(\Delta \gamma_{\mathrm{2D}}\) caused by quantum capacitance, at the atomistic scale (several \AA{}).
-(ii) change of interfacial energy by reorientation of interfacial liquid molecules  \(\Delta \gamma_{\mathrm{2D-L}} ^{\mathrm{Orien}}\), at molecular scale (10\(^{\text{0}}\) \textasciitilde{} 10\(^{\text{1}}\) nm).
-(iii) change of interfacial energy as a result of electric double layer  \(\Delta \gamma_{\mathrm{2D-L}} ^{\mathrm{EDL}}\), described by a continuum model (10\(^{\text{0}}\) \textasciitilde{} 10\(^{\text{4}}\) nm)}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.75\linewidth]{../img/dgamma-sigma.pdf}
-\caption{\label{fig:dgamma-sigma}
-Atomistic scale: \(\Delta \gamma_{\mathrm{2D}}\) as a function of \(\sigma_{\mathrm{2D}}\) for selected 2D materials: graphene, silicene, germanene, phosphorene, MoS\(_{2}\), MoSe\(_{2}\), MoTe\(_{2}\), WS\(_{2}\), WSe\(_{2}\) and WTe\(_{2}\).
-The 2D semimetals (graphene, silicene and germanene) with low high quantum capcitances show larger decrease of \(\gamma_{\mathrm{2D}}\) upon doping, compared with the 2D semiconductors (TMDCs, phosphorene).}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.9\linewidth]{../img/fig-pot-dens.pdf}
-\caption{\label{fig:MD-res}
-Molecular scale: geometry of the periodic MD simulation box for (a) water molecules only and (b) water-graphene systems, with \textasciitilde{} 27000 water molecules per unit cell.
-(c) Change of total adhesion energy \(\Delta\Phi\), and its partial contributionsfrom Lennard-Jones  \(\Delta\Phi_{\mathrm{LJ}}\) and Coulombic  \(\Delta\Phi_{\mathrm{Coul}}\) interactions, as a function of \(\sigma_{\mathrm{2D}}\).
-The filled regions indicate the error margin of calculation.
-\(10^{-3}\) \textit{e}/atom corresponds to a charge density of \(3.80 \times 10^{12}\ e \cdot \mathrm{cm}^{-2}\).
-(d) and (e) are the local density \(\rho_{\mathrm{L}}\) and local charge density \(\delta_{\mathrm{L}}\) of water molecules as a function of distance \(z\) from graphene surface, respectively.}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.5\linewidth]{../img/2d-ph-dependency+MD.pdf}
-\caption{\label{fig:res-EDL}
-The continuum model: (a) Scheme of the interface between the 2D material and the aqueous phase.
-(b) \((\Delta\cos\theta)^{\mathrm{EDL}}\) as a function of \(\sigma_{\mathrm{2D}}\) with varied solute concentrations.
-The concentration \(c_{0}\) varies from \(10^{0}\) to \(10^{-7}\) mol\(\cdot\mathrm{L}^{-1}\) (c) Overall change of contact angle \((\Delta \cos \theta)^{\mathrm{Orien+EDL}}\) combining the orientation and EDL effects, with varied solute concentrations as in (b).}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.95\linewidth]{../img/plot-fitting.pdf}
-\caption{\label{fig:f-nc-exp}
-Comparison between model and experimental data: schemes of the void region in (a) substrated doped 2D material and (b) electrostatic gated 2D material.(c) Fitted experimental data of \(\Delta\cos\theta\) as a function of \(\sigma_{\mathrm{2D}}\).
-The electrowetting data are extracted from Ref.
-\citenum{hong_mechanism_2016}; the ESEM data are extracted from Ref.
-\citenum{ashraf_doping-induced_2016}.}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.65\linewidth]{../img/dcos-all-2D.pdf}
-\caption{\label{fig:dcos-all-2D}
-Electrostatic tunability of 2D material wettability: (a) Schematic illustration of the 2D-material-based electrowetting device, where the 2D material is electostatically doped.
-(b) \((\Delta\cos\theta)^{\mathrm{EDL}}\) as a function of \(V_{\mathrm{G}}\) for selected 2D materials.}
-\end{figure}
 \end{document}

### 2018-10-05 submission/Langmuir/20171017/writing/dcos_sigma.py

@@ -1,0 +1,169 @@
+import matplotlib
+from matplotlib import patches
+from pubfigure.FigureCollection import FigureCollection
+import numpy
+import scipy
+import scipy.constants as const
+import pycse.orgmode as org
+
+eps_w = 80 * const.epsilon_0
+d_H = 0.3 * 10**-9                # Helmholtz plane
+n_L = numpy.linspace(-4, 4, 100)
+sigma_L = n_L * const.e * 10**13 * 10**4
+T = 298
+C_H = eps_w / d_H
+gamma_w = 63.6e-3               # surface tension in SI
+f_MD = scipy.poly1d([0.2157, -0.691, -3.71973, 0])/1000 #In mJ/m^2!!
+
+
+# def f_MD(x):
+#     f_n = lambda x_: -0.074 * (x_)**3 - 1.842 * \
+#         (x_)**2 - 2.249 * x_ + 2.48 * (-x_)**0.54
+#     f_p = lambda x_: - 1.279 * x_ + 1.525 * (x_)**0.99 + 11.950 * \
+#         (scipy.exp(-1.043 * x_) - 1) 
+#     xn = x[x < 0]
+#     xp = x[x >= 0]
+#     # print(xn, xp)
+#     yn = f_n(xn)/1000
+#     yp = f_p(xp)/1000
+
+#     return numpy.hstack([yn, yp])
+
+
+def cal_2D(c0, sigma_, what="Delta_cos", z=1, add_MD=False):
+    # c0 should use mol/m^3
+    sigma = -sigma_
+    psi_L = -2 * const.k * T / z / const.e * scipy.arcsinh(
+        sigma / scipy.sqrt(8 * c0 * const.N_A * eps_w * const.k * T))
+    psi_2D = psi_L - sigma / C_H
+    A = scipy.sqrt(2 * z**2 * const.e**2 * eps_w *
+                   c0 * const.N_A / const.k / T)
+    B = z * const.e * psi_L / (2 * const.k * T)
+    C_L = A * scipy.cosh(B)
+    l_D = scipy.sqrt(eps_w * const.k * T /
+                     (2 * z**2 * const.e**2 * c0 * const.N_A))
+    Delta_Phi_el = -sigma**2 / (2 * C_H) - sigma**2 / (C_L + eps_w / l_D)
+    if add_MD is True:
+        n = sigma_ / (const.e * 10**13 * 10**4)
+        Delta_Phi_MD = f_MD(n)
[…]

### 2018-10-05 submission/Langmuir/20171017/writing/fit_program.py

@@ -1,0 +1,174 @@
+esem=[["NAME", "CA", "CA-err", "WF", "WF-err"], ["PSS", 73.97, 3.92, 4.98, 0.092], ["PAA", 75.0, 2.96, 4.96, 0.096], ["SiO2", 80.88, 2.95, 4.6, 0.026], ["PAH", 75.01, 4.02, 4.16, 0.05], ["PLL", 74.03, 1.98, 4.12, 0.09]]
+elw=[["V", "CA"], [-100, 78], [0, 88], [100, 60]]
+import scipy
+import scipy.constants as const
+import matplotlib
+matplotlib.use("Agg")
+import matplotlib.pyplot as plt
+from scipy.integrate import cumtrapz
+import numpy
+from dcos_sigma import cal_2D
+import pycse.orgmode as org
+
+v_f = 1.1e6
+eps_sio2 = 3.9
+
+
+
+def e_cm2_to_SI(n):
+    return n*const.e*10**4
+
+def SI_to_e_cm2(sigma):
+    return sigma/const.e/10**4
+
+def EF_gr_from_sigma(sigma):
+    A = scipy.sign(sigma)*const.hbar*v_f/const.e
+    B = scipy.sqrt(scipy.pi*scipy.absolute(sigma)/const.e)
+    return A*B
+
+def sigma_from_EF(EF):
+    return scipy.sign(EF)*EF**2*const.e**3/const.pi/const.hbar**2/v_f**2
+
+def sigma_from_sio2(V_M, sigma0=0, t=280e-9):
+    Cox = const.epsilon_0*eps_sio2 / t
+    # VM to be voltage applied to 2D surface
+    return Cox*V_M + sigma0
+
+
+EF_plt = numpy.linspace(-0.8, 0.8, 200)
+sigma_plt = sigma_from_EF(EF_plt)
+n_plt = SI_to_e_cm2(sigma_plt)/10**13
+
+c0 = 10**-7*1000
+
+dcos_plt = cal_2D(c0, sigma_plt, add_MD=True)
+
+# Data for the ESEM
+data_esem = []
+sigma_esem = []
+sigma_err_esem = []
+dcos_esem = []
+dcos_err_esem = []
+
+esem_label = []
+
+theta0_esem = 81.0
+dcos0_esem = scipy.cos(theta0_esem/180*scipy.pi)
+for line in esem[1:]:
+    esem_label.append(line[0])
[…]

### 2018-10-05 submission/Langmuir/20171017/writing/plot_density.py

@@ -1,0 +1,83 @@
+import numpy, matplotlib
+matplotlib.use("Agg")
+import matplotlib.pyplot as plt
+import scipy.constants as const
+import scipy
+import pycse.orgmode as org
+from scipy.interpolate import interp1d
+
+charge_per_atom = [-12, -6, 0, 6, 12]
+name = ["neg0.012", "neg0.006", "0.000", "0.006", "0.012"]
+label_name = ["-0.012", "-0.006", "0", "0.006", "0.012"]
+
+c_atom_to_sigma = lambda x: x*2/(2.465e-8**2*scipy.sin(scipy.pi/3))
+z_gr = 1.980
+
+f_charge_base = "../data/6_11_17_data/charge_int_{}_large2.xvg"
+f_charge_water = "../data/6_11_17_data/charge_int_water-surf.xvg"
+
+f_dens_base = "../data/6_11_17_data/density_int_{}_large2.xvg"
+f_dens_water = "../data/6_11_17_data/density_int_water-surf.xvg"
+
+charge_per_atom.sort()
+
+c_water = numpy.genfromtxt(f_charge_water, delimiter=(12, 17), skip_header=19)
+d_water = numpy.genfromtxt(f_dens_water, delimiter=(12, 17), skip_header=19)
+
+# ax1.plot(c_water[:, 0] - z_gr, c_water[:, 1], label="Water Only")
+
+def plot_den(fig, what="mass"):
+    ax = fig.add_subplot(111)
+    if what is "mass":
+        for index, c in enumerate(charge_per_atom):
+            d_sys = numpy.genfromtxt(f_dens_base.format(name[index]),
+                                     delimiter=(12, 17), skip_header=19)
+            # special treatment for negative value using spline
+            d_sys_x = d_sys[:, 0]; d_sys_y = d_sys[:, 1]
+            cond = numpy.where(d_sys_y > 100)
+            d_sys_x = d_sys_x[cond]; d_sys_y = d_sys_y[cond]
+            zz = numpy.linspace(d_sys_x.min(), d_sys_x.max(), 50000)
+            f_yy = interp1d(d_sys_x, d_sys_y, kind="cubic")
+            yy = f_yy(zz)
+            zzz = numpy.linspace(0, d_sys_x.min(), 50000)
+            f_yyy = lambda x: d_sys_y[0]*scipy.exp(150*(x-d_sys_x.min()))
[…]
